### 2023-06-05 README.Rmd
add readme file new try 230605 _ v11

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# validateHOT &#127919;

<!-- badges: start -->
<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation task (also known as holdout task). A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores. At the moment, validateHOT provides the following functions:

<ul>
<li>
`createHOT`: creates the validation/holdout task for you. For example, in a *CBC* the total utilities are calculated by the sum of each attribute level. You have to specify the attribute levels for each alternative in the validation/holdout task and it will calculate the total utility for each alternative in the validation/holdout task.
</li>
<li>
`accuracy`: generates the number of correct predicted choice or no-choice divided by the total number of predictions. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
`f1`: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
`f1`: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>

## Installation

You can install the development version of validateHOT from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JoshSchramm94/validateHOT")
```

## Example

This is a basic example which shows you how to solve a common problem:

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

### 2023-06-05 README.Rmd
new try ... 230605

@@
 <li>
-`createHOT`: creates the validation/holdout task for you.
+<code>createHOT</code>: creates the validation/holdout task for you.
 For example, in a *CBC* the total utilities are calculated by the sum of each attribute level.
@@
 <li>
-`accuracy`: generates the number of correct predicted choice or no-choice divided by the total number of predictions. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
+<code>accuracy</code>: generates the number of correct predicted choice or no-choice divided by the total number of predictions.
+Only possible for a binary output, e.g., buy vs.
+no-buy correctly predicted.
 </li>
 <li>
-`f1`: generates the F1-Score.
+<code>f1</code>: generates the F1-Score.
 F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$.
@@
 </li>
-<li>
-`f1`: generates the F1-Score.
-F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$.
-Only possible for a binary output, e.g., buy vs.
-no-buy correctly predicted.
-</li>
+</ul>
 

### 2023-06-08 README.Rmd
update v01 230608

@@
 output: github_document
+bibliography: references.bib
 ---
@@
 A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores.
-At the moment, validateHOT provides the following functions:
+At the moment, <code>validateHOT</code>
+provides functions for 3 key areas:
+
+<ul>
+<li>validation metrics mainly reported in preference measurement
+studies</li>
+
+<li>metrics that are usually reported in machine learning (i.e.,
+confusion matrix)</li>
+
+<li>simulation methods, for example, to determine optimal product
+combinations</li>
+
+</ul>
+
+For all 3 key areas, the <code>createHOT</code> function is essential.
+This function creates the total utilities for each alternative in the
+validation/holdout task and also in the simulation method, respectively.
+@rao2014a [p. 82] mentions the additive utility model stating that the
+total utility of a profile or conjoint model is the sum of its attribute
+levels. <code>createHOT</code> will do exactly this for you.
+
+### Classical validation metrics
+
+<ul> <li><code>hitrate</code>: </li>
+
+<li><code>mhp</code>: </li>
+
+<li><code>kl</code>: </li>
+
+<li><code>mae</code>: </li>
+
+<li><code>medae</code>: </li>
+
+<li><code>mhp</code>: </li>
+
+<li><code>rmse</code>: </li>
+
+</ul>
+
+### Confusion Matrix
+
+<ul>
+
+<li><code>accuracy</code>: </li>
+
+<li><code>f1</code>: </li>
+
+<li><code>precision</code>: </li>
+
+<li><code>recall</code>: </li>
+
+<li><code>specificity</code>: </li>
+
+</ul>
+
+### Simulation Methods
+
+<ul>
+
+<li><code>freqassort</code>: </li>
+
+<li><code>reach</code>: </li>
+
+<li><code>shareofpref</code>: </li>
+
+</ul>
+
+### Data Frames provided by <code>validateHOT</code>
+
+<ul>
+
+<li><code>ACBC_interpolate</code>: </li>
+
+<li><code>ACBC</code>: </li>
+
+<li><code>CBC_lin</code>: </li>
+
+<li><code>CBC</code>: </li>
+
+<li><code>MaxDiff</code>: </li>
+
+</ul>
 
@@
 
-This is a basic example which shows you how to solve a common problem:
-
-What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:
-
-You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.
-`devtools::build_readme()` is handy for this.
-You could also use GitHub Actions to re-render `README.Rmd` every time you push.
-An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
+## References

### 2023-06-09 README.Rmd
update 230609_v01a

@@
 bibliography: references.bib
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-# validateHOT &#127919;
+# validateHOT 🎯
 
 <!-- badges: start -->
+
 <!-- badges: end -->
 
-The goal of validateHOT is to validate the results of your validation task (also known as holdout task).
-A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores.
-At the moment, <code>validateHOT</code>
+The goal of validateHOT is to validate the results of your validation
+task (also known as holdout task). A validation task is essential to
+make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are
+valid and can also predict outside task that were **not** included in
+estimating your utility scores. Although commercial studies often do not
+include a validation/holdout task [@yang2018], it is highly recommended
+to do so [@Orme.2015; @rao2014a]. This validation/ holdout task does not
+only help to check whether everything went right during data collection
+but also to determine your final model. <code>validatHOT</code> provides
+some of the relevant metrics to test the performance of your data in
+predicting a holdout task. In [Sawtooth
+Software's](https://sawtoothsoftware.com/) *CBC* a fixed validation/
+holdout task is automatically implemented. If you conduct a *MaxDiff* or
+*ACBC* study these have to be programmed by yourself.
+
+👉🏾 <u>What you need to provide</u>: <br> After collecting your data, and
+running your initial *Hierarchical Bayes* models, you can turn to
+<code>validateHOT</code> and test how good your model predicts choices
+in the validation/ holdout task. Herefore, you only have to insert your
+**raw** utility scores as well as the actual choice of your validation/
+holdout task. You can use the <code>merge()</code> provided by
+<code>base</code> package [@base]. Afterward, you can read in your data
+file and enjoy <code>validateHOT</code>.
+
+👈🏾 <u>What you get</u>:<br> At the moment, <code>validateHOT</code>
 provides functions for 3 key areas:
@@
 <ul>
+
 <li>validation metrics mainly reported in preference measurement
@@
 
-<ul> <li><code>hitrate</code>: </li>
+<ul>
 
-<li><code>mhp</code>: </li>
+<li><code>hitrate</code>: creates the *Hit Rate* (correctly predicted
+choices) of your validation task. The output will contain the chance
+level in your validation task ($\frac{1}{alternatives}$) in percentage.
+The number of correctly predicted partcipants' choices as well as the
+percentage of how many choices were correctly predicted. If you specify
+an optional <code>Group</code> argument the output is split by
+groups.</li>
 
-<li><code>kl</code>: </li>
+<li><code>kl</code>: Kullback-Leibler-Divergence ?????? [@ding2011]. If
+you specify an optional <code>Group</code> argument the output is split
+by groups.</li>
 
-<li><code>mae</code>: </li>
+<li><code>mhp</code>: averaged hit probability of participant's actual
+choice in the validation/ holdout task. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
-<li><code>medae</code>: </li>
+<li><code>mae</code>: average absolute error, i.e., deviation between
+predicted and stated choice share. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
-<li><code>mhp</code>: </li>
+<li><code>medae</code>: since the averaged absolute error can be highly
+influenced by the If you specify an optional <code>Group</code> argument
+the output is split by groups.</li>
 
-<li><code>rmse</code>: </li>
+<li><code>mhp</code>:</li>
+
+<li><code>rmse</code>:</li>
 
@@
 
-<li><code>accuracy</code>: </li>
+<li><code>accuracy</code>:</li>
 
-<li><code>f1</code>: </li>
+<li><code>f1</code>:</li>
 
-<li><code>precision</code>: </li>
+<li><code>precision</code>:</li>
 
-<li><code>recall</code>: </li>
+<li><code>recall</code>:</li>
 
-<li><code>specificity</code>: </li>
+<li><code>specificity</code>:</li>
 
@@
 
-<li><code>freqassort</code>: </li>
+<li><code>freqassort</code>:</li>
 
-<li><code>reach</code>: </li>
+<li><code>reach</code>:</li>
 
-<li><code>shareofpref</code>: </li>
+<li><code>shareofpref</code>:</li>
 
@@
 
-<li><code>ACBC_interpolate</code>: </li>
+<li><code>ACBC_interpolate</code>:</li>
 
-<li><code>ACBC</code>: </li>
+<li><code>ACBC</code>:</li>
 
-<li><code>CBC_lin</code>: </li>
+<li><code>CBC_lin</code>:</li>
 
-<li><code>CBC</code>: </li>
+<li><code>CBC</code>:</li>
 
-<li><code>MaxDiff</code>: </li>
+<li><code>MaxDiff</code>:</li>
 
@@
 <ul>
-<li>
-<code>createHOT</code>: creates the validation/holdout task for you.
-For example, in a *CBC* the total utilities are calculated by the sum of each attribute level.
-You have to specify the attribute levels for each alternative in the validation/holdout task and it will calculate the total utility for each alternative in the validation/holdout task.
-</li>
-<li>
-<code>accuracy</code>: generates the number of correct predicted choice or no-choice divided by the total number of predictions.
-Only possible for a binary output, e.g., buy vs.
-no-buy correctly predicted.
-</li>
-<li>
-<code>f1</code>: generates the F1-Score.
-F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$.
-Only possible for a binary output, e.g., buy vs.
-no-buy correctly predicted.
-</li>
+
+<li><code>createHOT</code>: creates the validation/holdout task for you.
+For example, in a *CBC* the total utilities are calculated by the sum of
+each attribute level. You have to specify the attribute levels for each
+alternative in the validation/holdout task and it will calculate the
+total utility for each alternative in the validation/holdout task.</li>
+
+<li><code>accuracy</code>: generates the number of correct predicted
+choice or no-choice divided by the total number of predictions. Only
+possible for a binary output, e.g., buy vs. no-buy correctly
+predicted.</li>
+
+<li><code>f1</code>: generates the F1-Score. F1-Score is calculated by
+the following formula
+$\frac{2 * precision * recall}{precision + recall}$. Only possible for a
+binary output, e.g., buy vs. no-buy correctly predicted.</li>
+
 </ul>
+
+## Why <code>validateHOT</code>
+
+comparison to Metrics
+
+studi seminar für preference measurement techniques --\> often not
+getting in touch with *R* before, so wanted to make it easier for them.
+this
 
@@
 
-You can install the development version of validateHOT from [GitHub](https://github.com/) with:
+You can install the development version of validateHOT from
+[GitHub](https://github.com/) with:
 

### 2023-06-09 R/Accuracy.R

@@ -52,7 +52,7 @@
 #' @examples
 #' library(validateHOT)
 #' data("MaxDiff")
-#' createHOT(
+#' validateHOT::createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,

### 2023-06-10 README.Rmd
230610_v01

@@
 
-👉🏾 <u>What you need to provide</u>: <br> After collecting your data, and
-running your initial *Hierarchical Bayes* models, you can turn to
+👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
+and running your initial *Hierarchical Bayes* models, you can turn to
 <code>validateHOT</code> and test how good your model predicts choices
@@
 
-👈🏾 <u>What you get</u>:<br> At the moment, <code>validateHOT</code>
+👈🏾 <u>**What you get**</u>:<br> At the moment, <code>validateHOT</code>
 provides functions for 3 key areas:
@@
 
-<li><code>kl</code>: Kullback-Leibler-Divergence ?????? [@ding2011]. If
+<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
+divergence between the actual choice distribution and the predicted
+choice distribution [@ding2011; @philentropy]. Output provides both
+divergence between *predicted* from *observed* and *observed* from
+*predicted* due to the asymmetry of the Kullback-Leibler divergence. If
 you specify an optional <code>Group</code> argument the output is split
 by groups.</li>
-
-<li><code>mhp</code>: averaged hit probability of participant's actual
-choice in the validation/ holdout task. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
 
@@
 
-<li><code>mhp</code>:</li>
+<li><code>mhp</code>: averaged hit probability of participant's actual
+choice in the validation/ holdout task. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
-<li><code>rmse</code>:</li>
+<li><code>rmse</code>: provides the root-mean-squared error of deviation between predicted and stated choice share.
+If you specify an optional <code>Group</code> argument the output is split by groups.</li>
 
@@
 
-<li><code>freqassort</code>:</li>
+<li><code>freqassort</code>: Inspired by the former [*turfR*](https://github.com/cran/turfR) package, <code>freqassort</code> will give you the averaged frequency, how many products the participants will choose from your in the function determined potential assortment.
+For the <code>method</code> argument you can decide between <code>method = "threshold"</code> (if utility of product is larger than the utility of *none*, it is marked as potential purchase option) and <code>method = "First Choice"</code> (only product with highest utility is considered.
+If its utility is above the utility of *none*, it is marked as potential purchase option).
+If you specify an optional <code>Group</code> argument the output is split by groups.</li>
 
-<li><code>reach</code>:</li>
+<li><code>reach</code>: Inspired by the former [*turfR*](https://github.com/cran/turfR) package, <code>reach</code> will give you the averaged percentage of how many participants you can reach (buy *at least* one of the products) with your in the function determined potential assortment.
+or the <code>method</code> argument you can decide between <code>method = "threshold"</code> (if utility of product is larger than the utility of *none*, it is marked as potential purchase option) and <code>method = "First Choice"</code> (only product with highest utility is considered.
+If its utility is above the utility of *none*, it is marked as potential purchase option).
+If you specify an optional <code>Group</code> argument the output is split by groups.</li>
 
-<li><code>shareofpref</code>:</li>
+<li><code>shareofpref</code>: provides you the aggregated share of preference, including the lower and upper confidence interval, which is calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$.
+If you specify an optional <code>Group</code> argument the output is split by groups and provided in a <code>list</code> element.
+</li>
 
@@
 
-<li><code>ACBC_interpolate</code>:</li>
+<li><code>ACBC</code>: Example data set with raw utilities of an *ACBC* study conducted in Sawtooth. Price was linear-coded while the other attributes were coded as part-worths.</li>
 
-<li><code>ACBC</code>:</li>
+<li><code>ACBC_interpolate</code>: Example data set with raw utilities of an *ACBC* study conducted in Sawtooth.
+Price was piecewise-coded, another attribute was linear-coded while the other attributes were coded as part-worths.
+</li>
 
-<li><code>CBC_lin</code>:</li>
+<li><code>CBC</code>: Example data set with raw utilities of an *CBC* study conducted in Sawtooth. All attributes were coded as part-worth.</li>
 
-<li><code>CBC</code>:</li>
+<li><code>CBC_lin</code>: Example data set with raw utilities of an *CBC* study conducted in Sawtooth. One attribute was linear coded while the other attributes are part-worth coded.</li>
 
-<li><code>MaxDiff</code>:</li>
+<li><code>MaxDiff</code>: Example data set with raw utilities of an *MaxDiff* study conducted in Sawtooth.</li>
 
@@
 <ul>
-
-<li><code>createHOT</code>: creates the validation/holdout task for you.
-For example, in a *CBC* the total utilities are calculated by the sum of
-each attribute level. You have to specify the attribute levels for each
-alternative in the validation/holdout task and it will calculate the
-total utility for each alternative in the validation/holdout task.</li>
 

### 2023-06-10 README.Rmd
230610_v03

--- 2023-06-09 README.Rmd
@@
 task (also known as holdout task). A validation task is essential to
-make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are
-valid and can also predict outside task that were **not** included in
+make sure that your collected data of a MaxDiff, CBC, or ACBC are
+valid and can also predict outside task that were not included in
 estimating your utility scores. Although commercial studies often do not
@@
 predicting a holdout task. In [Sawtooth
-Software's](https://sawtoothsoftware.com/) *CBC* a fixed validation/
-holdout task is automatically implemented. If you conduct a *MaxDiff* or
-*ACBC* study these have to be programmed by yourself.
+Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
+holdout task is automatically implemented. If you conduct a MaxDiff or
+ACBC study these have to be programmed by yourself.
 
-👉🏾 <u>What you need to provide</u>: <br> After collecting your data, and
-running your initial *Hierarchical Bayes* models, you can turn to
+👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
+and running your initial Hierarchical Bayes models, you can turn to
 <code>validateHOT</code> and test how good your model predicts choices
 in the validation/ holdout task. Herefore, you only have to insert your
-**raw** utility scores as well as the actual choice of your validation/
+raw utility scores as well as the actual choice of your validation/
 holdout task. You can use the <code>merge()</code> provided by
@@
 
-<li><code>hitrate</code>: creates the *Hit Rate* (correctly predicted
+<li><code>hitrate</code>: creates the Hit Rate (correctly predicted
 choices) of your validation task. The output will contain the chance
 level in your validation task ($\frac{1}{alternatives}$) in percentage.
-The number of correctly predicted partcipants' choices as well as the
+The number of correctly predicted participants' choices as well as the
 percentage of how many choices were correctly predicted. If you specify
@@
 
-<li><code>kl</code>: Kullback-Leibler-Divergence ?????? [@ding2011]. If
+<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
+divergence between the actual choice distribution and the predicted
+choice distribution [@ding2011; @philentropy]. Output provides both
+divergence between predicted from observed and observed from
+predicted due to the asymmetry of the Kullback-Leibler divergence. If
 you specify an optional <code>Group</code> argument the output is split
 by groups.</li>
-
-<li><code>mhp</code>: averaged hit probability of participant's actual
-choice in the validation/ holdout task. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
 
@@
 
-<li><code>mhp</code>:</li>
+<li><code>mhp</code>: averaged hit probability of participant's actual
+choice in the validation/ holdout task. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
-<li><code>rmse</code>:</li>
+<li><code>rmse</code>: provides the root-mean-squared error of deviation
+between predicted and stated choice share. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
@@
 
+We also include metrics from machine learning, i.e., the confusion matrix (e.g., @Burger2018).
+For all of the 5 provided functions, you currently have to have a **none** option in your data.
+We currently predict, e.g., whether a buy or no-buy was correctly predicted.
+Information could be used for overestimating and underestimating, respectively, of product purchases.
+
 <ul>
 
-<li><code>accuracy</code>:</li>
+<li><code>accuracy</code>: $\frac{2 * precision * recall}{precision + recall}$</li>
 
-<li><code>f1</code>:</li>
+<li><code>f1</code>: </li>
 
-<li><code>precision</code>:</li>
+<li><code>precision</code>: </li>
 
-<li><code>recall</code>:</li>
+<li><code>recall</code>: </li>
 
-<li><code>specificity</code>:</li>
+<li><code>specificity</code>: </li>
 
@@
 
-<li><code>freqassort</code>:</li>
+<li><code>freqassort</code>: Inspired by the former
+[turfR](https://github.com/cran/turfR) package,
+<code>freqassort</code> will give you the averaged frequency, how many
+products the participants will choose from your in the function
+determined potential assortment. For the <code>method</code> argument
+you can decide between <code>method = "threshold"</code> (if utility of
+product is larger than the utility of <code>None</code>, it is marked as potential
+purchase option) and <code>method = "First Choice"</code> (only product
+with highest utility is considered. If its utility is above the utility
+of <code>None</code>, it is marked as potential purchase option). If you specify an
+optional <code>Group</code> argument the output is split by groups.</li>
 
-<li><code>reach</code>:</li>
+<li><code>reach</code>: Inspired by the former
+[turfR](https://github.com/cran/turfR) package, <code>reach</code>
+will give you the averaged percentage of how many participants you can
+reach (buy at least one of the products) with your in the function
+determined potential assortment. or the <code>method</code> argument you
+can decide between <code>method = "threshold"</code> (if utility of
+product is larger than the utility of <code>None</code>, it is marked as potential
+purchase option) and <code>method = "First Choice"</code> (only product
+with highest utility is considered. If its utility is above the utility
+of <code>None</code>, it is marked as potential purchase option). If you specify an
+optional <code>Group</code> argument the output is split by groups.</li>
 
-<li><code>shareofpref</code>:</li>
+<li><code>shareofpref</code>: provides you the aggregated share of
+preference, including the lower and upper confidence interval, which is
+calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$. If
+you specify an optional <code>Group</code> argument the output is split
+by groups and provided in a list element.</li>
 
@@
 
-<li><code>ACBC_interpolate</code>:</li>
+<li><code>ACBC</code>: Example data set with raw utilities of an ACBC
+study conducted in Sawtooth. Price was linear-coded while the other
+attributes were coded as part-worths.</li>
 
-<li><code>ACBC</code>:</li>
+<li><code>ACBC_interpolate</code>: Example data set with raw utilities
+of an ACBC study conducted in Sawtooth. Price was piecewise-coded,
+another attribute was linear-coded while the other attributes were coded
+as part-worths.</li>
 
-<li><code>CBC_lin</code>:</li>
+<li><code>CBC</code>: Example data set with raw utilities of an CBC
+study conducted in Sawtooth. All attributes were coded as
+part-worth.</li>
 
-<li><code>CBC</code>:</li>
+<li><code>CBC_lin</code>: Example data set with raw utilities of an
+CBC study conducted in Sawtooth. One attribute was linear coded while
+the other attributes are part-worth coded.</li>
 
-<li><code>MaxDiff</code>:</li>
+<li><code>MaxDiff</code>: Example data set with raw utilities of an
+MaxDiff study conducted in Sawtooth.</li>
 

### 2023-06-10 README.Rmd
230610_v05

@@
 task (also known as holdout task). A validation task is essential to
-make sure that your collected data of a MaxDiff, CBC, or ACBC are
-valid and can also predict outside task that were not included in
-estimating your utility scores. Although commercial studies often do not
-include a validation/holdout task [@yang2018], it is highly recommended
-to do so [@Orme.2015; @rao2014a]. This validation/ holdout task does not
-only help to check whether everything went right during data collection
-but also to determine your final model. <code>validatHOT</code> provides
+make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
+and can also predict outside task that were not included in estimating
+your utility scores. Although commercial studies often do not include a
+validation/holdout task [@yang2018], it is highly recommended to do so
+[@Orme.2015; @rao2014a]. This validation/ holdout task does not only
+help to check whether everything went right during data collection but
+also to determine your final model. <code>validatHOT</code> provides
 some of the relevant metrics to test the performance of your data in
@@
 choice distribution [@ding2011; @philentropy]. Output provides both
-divergence between predicted from observed and observed from
-predicted due to the asymmetry of the Kullback-Leibler divergence. If
-you specify an optional <code>Group</code> argument the output is split
-by groups.</li>
+divergence between predicted from observed and observed from predicted
+due to the asymmetry of the Kullback-Leibler divergence. If you specify
+an optional <code>Group</code> argument the output is split by
+groups.</li>
 
@@
 
-We also include metrics from machine learning, i.e., the confusion matrix (e.g., @Burger2018).
-For all of the 5 provided functions, you currently have to have a **none** option in your data.
-We currently predict, e.g., whether a buy or no-buy was correctly predicted.
-Information could be used for overestimating and underestimating, respectively, of product purchases.
+We also include metrics from machine learning, i.e., the confusion
+matrix (e.g., @Burger2018). For all of the 5 provided functions, you
+currently have to have a **none** option in your data. We currently
+predict, e.g., whether a buy or no-buy was correctly predicted.
+Information could be used for overestimating and underestimating,
+respectively, of product purchases. In the following <code>TP</code>
+stands for true positives, <code>FP</code> for false positives,
+<code>TN</code> for true negatives, and <code>FN</code> for false
+negatives.
 
@@
 
-<li><code>accuracy</code>: $\frac{2 * precision * recall}{precision + recall}$</li>
+<li><code>accuracy</code>: defined as
+$\frac{TP + TN}{TP + FP + TN + FN}$. If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
 
-<li><code>f1</code>: </li>
+<li><code>f1</code>: defined as
+$\frac{2 * precision * recall}{precision + recall}$ or stated
+differently by Burger [-@Burger2018] $\frac{2TP}{2TP + FP + FN}$. If you
+specify an optional <code>Group</code> argument the output is split by
+groups.</li>
 
-<li><code>precision</code>: </li>
+<li><code>precision</code>: defined as $\frac{TP}{TP + FP}$. If you
+specify an optional <code>Group</code> argument the output is split by
+groups.</li>
 
-<li><code>recall</code>: </li>
+<li><code>recall</code>: defined as $\frac{TP}{TP + FN}$. If you specify
+an optional <code>Group</code> argument the output is split by
+groups.</li>
 
-<li><code>specificity</code>: </li>
+<li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$. If you
+specify an optional <code>Group</code> argument the output is split by
+groups.</li>
 
@@
 <li><code>freqassort</code>: Inspired by the former
-[turfR](https://github.com/cran/turfR) package,
-<code>freqassort</code> will give you the averaged frequency, how many
-products the participants will choose from your in the function
-determined potential assortment. For the <code>method</code> argument
-you can decide between <code>method = "threshold"</code> (if utility of
-product is larger than the utility of <code>None</code>, it is marked as potential
+[turfR](https://github.com/cran/turfR) package, <code>freqassort</code>
+will give you the averaged frequency, how many products the participants
+will choose from your in the function determined potential assortment.
+For the <code>method</code> argument you can decide between <code>method
+= "threshold"</code> (if utility of product is larger than the utility
+of <code>None</code>, it is marked as potential purchase option) and
+<code>method = "First Choice"</code> (only product with highest utility
+is considered. If its utility is above the utility of <code>None</code>,
+it is marked as potential purchase option). If you specify an optional
+<code>Group</code> argument the output is split by groups.</li>
+
+<li><code>reach</code>: Inspired by the former
+[turfR](https://github.com/cran/turfR) package, <code>reach</code> will
+give you the averaged percentage of how many participants you can reach
+(buy at least one of the products) with your in the function determined
+potential assortment. or the <code>method</code> argument you can decide
+between <code>method = "threshold"</code> (if utility of product is
+larger than the utility of <code>None</code>, it is marked as potential
 purchase option) and <code>method = "First Choice"</code> (only product
 with highest utility is considered. If its utility is above the utility
-of <code>None</code>, it is marked as potential purchase option). If you specify an
-optional <code>Group</code> argument the output is split by groups.</li>
-
-<li><code>reach</code>: Inspired by the former
-[turfR](https://github.com/cran/turfR) package, <code>reach</code>
-will give you the averaged percentage of how many participants you can
-reach (buy at least one of the products) with your in the function
-determined potential assortment. or the <code>method</code> argument you
-can decide between <code>method = "threshold"</code> (if utility of
-product is larger than the utility of <code>None</code>, it is marked as potential
-purchase option) and <code>method = "First Choice"</code> (only product
-with highest utility is considered. If its utility is above the utility
-of <code>None</code>, it is marked as potential purchase option). If you specify an
-optional <code>Group</code> argument the output is split by groups.</li>
+of <code>None</code>, it is marked as potential purchase option). If you
+specify an optional <code>Group</code> argument the output is split by
+groups.</li>
 
@@
 
-<li><code>CBC_lin</code>: Example data set with raw utilities of an
-CBC study conducted in Sawtooth. One attribute was linear coded while
-the other attributes are part-worth coded.</li>
+<li><code>CBC_lin</code>: Example data set with raw utilities of an CBC
+study conducted in Sawtooth. One attribute was linear coded while the
+other attributes are part-worth coded.</li>
 
@@
 
-<ul>
-
-<li><code>accuracy</code>: generates the number of correct predicted
-choice or no-choice divided by the total number of predictions. Only
-possible for a binary output, e.g., buy vs. no-buy correctly
-predicted.</li>
-
-<li><code>f1</code>: generates the F1-Score. F1-Score is calculated by
-the following formula
-$\frac{2 * precision * recall}{precision + recall}$. Only possible for a
-binary output, e.g., buy vs. no-buy correctly predicted.</li>
-
-</ul>
-
 ## Why <code>validateHOT</code>
 
-comparison to Metrics
+We are teaching a preference measurement seminar for students. Often
+these students did not have experience with *R* before or only sparsely.
+We teach them to also validate their results and wanted to give them an
+easy way on how to do this in *R*. Of course, there are other great
+packages which are even faster in running (i.e., @Metrics), however,
+these packages need some more data wrangling in order to use the
+appropriate functions, which might be a burden or barrier for the one or
+the other.
 
-studi seminar für preference measurement techniques --\> often not
-getting in touch with *R* before, so wanted to make it easier for them.
-this
+Moreover, as @yang2018 also report, often commercial studies do not use
+any validation task. Some market research companies (as far as we have
+realized) are not that familiar with *R* yet. Since these functions are
+not always implemented in other softwares, this might be one reason why
+they do not include one simply because they do not know how to use it
+correctly. Having a package to evaluate the validation/ holdout task can
+also be beneficial for those companies.
 
@@
 
+First, we load the package.
+
+```{r}
+library("validateHOT")
+```
+
+### Example I - CBC
+
+Since *CBC's* are most commonly used between *CBC*, *ACBC*, and
+*MaxDiff*, we will provide an example with a *CBC*. Let us begin with a
+*CBC* where all of the variables are coded as part-worth, so we need no
+interpolation. Let us load the <code>CBC</code> data frame for this
+example.
+
+```{r}
+data("CBC")
+```
+
+The data frame has a total of `r nrow(CBC)` participants and `r ncol(CBC)` columns.
+
+Now imagine you included a validation/ holdout task with three
+alternatives as well as an no-buy option.
+We specify the <code>data</code> argument and the column index of <code>id</code>.
+Since we also have a *no-buy* alternative in our validation task, we next specify the <code>None</code> argument, otherwise we would have left it empty.
+Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>.
+If we look back at the data frame, we can see that the first alternative in the holdout task <code>c(4, 9, 19)</code> is composed of the following attribute levels <code>Att1_Lev1</code>, <code>Att2_Lev1</code>, and <code>Att3_Lev5</code>.
+
+As mentioned above, all the attributes are part-worth coded, therefore, we set <code>coding = c(0, 0, 0)</code>.
+Finally, we specify the method of prefernce measurement technique, which is <code>method = "CBC"</code> in our case and the column index of the actual participant's choice (<code>choice</code>).
+If you run the code, a data frame called <code>HOT</code> (short form of **H**old**o**ut **t**ask) will be returned to the global environment.
+
+> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this.
+However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>.
+For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
+
+```{r}
+createHOT(
+  data = CBC,
+  id = 1,
+  None = 21,
+  prod = 3,
+  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
+  coding = c(0, 0, 0),
+  method = "CBC",
+  choice = 22
+)
+```
+
+Let us take a glimpse at the output, which shows the total raw utilities for each of the function included in the validation/ holdout task.
+
+```{r}
+head(HOT)
+```
+
+In the next step, we would like to see how well our model (from which we took the raw utilities) predict the choices in the validation/ holdout task.
+First, we will test the <code>hitrate()</code> function.
+We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice.
+We can see that the hitrate of our example is `r round(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 1], digits  = 3)`.
+
+```{r}
+hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)
+```
+
+Let us also check the magnitude of the mean absolute error by running the <code>mae()</code> function.
+
+```{r}
+mae(data = HOT, id = 1, opts = c(2:5), choice = 6)
+```
+To cover also one example on how to use the metrics of the confusion matrix, we could test whether our model overestimates the purchase behavior (our model predicts a *buy* although participant opts for a *no* buy) or underestimates it (i.e., model predicts *no-buy* but participant opts for a *buy*).
+We will test the accuracy of the model by running the <code>accuracy()</code> function.
+
+```{r}
+accuracy(data = HOT, id = 1, opts = c(2:5), None = 5, choice = 6)
+```
+Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers.
+We will use the <code>reach()</code> function and use the threshold approach.
+To specify the bundles we are offering we use the <code>bundles</code> argument in our function.
+
+```{r}
+reach(data = HOT, id = 1, bundles = c(2:4), None = 5, method = "threshold")
+```
+
+### Example II - CBC with linear coding
+
 ## References

### 2023-06-10 R/Reach.R

@@ -5,10 +5,10 @@
 #'
 #' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
 #' @param id column index
+#' @param bundles column indexes of the bundles included that should be included in the assortment
 #' @param Group optional grouping variable to get accuracy by group
 #' @param None column index
 #' @param method which method should be used, can be either \code{"First choice"} (only the bundle with highest utility is marked as purchase option if its above \code{"None"} utility) or \code{"threshold"} (all bundles with utility above \code{"None"} utility are marked as purchase option)
-#' @param bundles column indexes of the bundles included that should be included in the assortment
 #'
 #' @importFrom dplyr group_by summarise
 #' @importFrom magrittr "%>%"

### 2023-06-10 R/freqAssort.R

@@ -9,9 +9,10 @@
 #' @param data data frame including alternatives in the validation task and actual \code{"choice"}. \code{"None"} alternative needs to be included.
 #' @param id column index of \code{"id"}
 #' @param Group optional grouping variable to get results by group
+#' @param bundles column indexes of the bundles that should be included in the assortment
 #' @param None column index of None alternative
 #' @param method either \code{"First choice"} or \code{"threshold"}, please see Details
-#' @param bundles column indexes of the bundles that should be included in the assortment
+
 #'
 #' @details
 #' Please specify the method you are using. The method can be either set

### 2023-06-10 README.Rmd
230610_v123

@@
 > &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this.
-However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>.
+However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package [@base].
 For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
@@
 
+In a second example, we again use a *CBC*, however, this time we show how to use <code>validateHOT</code> if one of the variables are linear coded. All other examples are provided in the Vignette.
+
+We are using the data frame <code>CBC_lin</code> which is also provided by the <code>validateHOT</code> package. We first load the data frame.
+
+```{r}
+data("CBC_lin")
+```
+
+Next, we create the validation/ holdout task to evaluate it in the next step.
+We use a validation/ holdout task with three alternatives plus the *no-buy* option, just as we did in the previous example.
+The only difference to the previous example is that we coded the third attribute (<code>Att3_Lin</code>) as linear.
+
+Again, we first define <code>data</code>.
+The <code>id</code> is saved in the first column.
+The utilities for the <code>None</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative).
+Next, we define the <code>prod.levels</code> for each alternative.
+For example, we can see that the second see that the second alternative is composed of <code>Att1_Lev5</code>, <code>Att2_Lev4</code>, and <code>60</code> which is the value that should be interpolated.
+We can see that this value is the one that needs to be interpolated if we take a closer look at the <code>coding</code> argument.
+This tells us that the first two attributes (<code>Att1_Lev5</code>, <code>Att2_Lev4</code> in the case of alternative 2) are part-worth coded (<code>0</code>) while the third attribute is linear coded (<code>1</code>).
+
+To interpolate the value, we have to provide <code>validateHOT</code> the <code>interpolate.levels</code>.
+These **need** to be the same as provided to, e.g., Sawtooth as levels.
+Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of <code>interpolate.levels</code>.
+In our case, we had 7 levels that range from 10 to 70.
+The value we want to interpolate for the second alternative is 40, which of course lies within 10 and 70.
+
+Next, we define the column index of the linear coded variable (<code>lin.p</code>) and specify the <code>coding</code> we talked about above.
+Again, we are running a *CBC* specified by the <code>method</code> argument.
+This time, we would like to keep some of the variables to the data frame, which we specify in <code>varskeep</code>.
+We only keep one further variable, however, you can specify as many as you want.
+This could be relevant if you would like to display results per group.
+Finally, we just tell <code>validateHOT</code> the column index of the final choice (<code>choice</code>) and we are good to go.
+
+```{r}
+CBC <- createHOT(
+  data = CBC_lin,
+  id = 1,
+  None = 15,
+  prod = 3,
+  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)),
+  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
+  lin.p = 14,
+  coding = c(0, 0, 1),
+  method = "CBC",
+  varskeep = 17,
+  choice = 16
+)
+```
+
+The next steps are the same as above.
+However, let us take a look at some examples in which we display the results per group.
+Let us again begin with the <code>hitrate()</code> function.
+To do so, we specify the column index of the grouping variable in the <code>Group</code> argument.
+
+```{r}
+hitrate(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
+```
+
+In this case, the Grouping variable is just an integer.
+However, the output is different if it is a factor or if it is labelled data.
+To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by @base.
+
+```{r}
+CBC$Group <- base::factor(CBC$Group,
+                          levels = c(1:3),
+                          labels = paste0("Group_", c(1:3)))
+```
+
+Afterward, we display the *mean hit probability* by running the <code>mhp()</code> function.
+
+```{r}
+mhp(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
+```
+
+For more examples, please see the accompanied vignette.
+
 ## References

### 2023-06-12 README.Rmd
nfbfhsodfjjhr

@@
 output: github_document
-bibliography: references.bib
 editor_options: 
@@
 your utility scores. Although commercial studies often do not include a
-validation/holdout task [@yang2018], it is highly recommended to do so
-[@Orme.2015; @rao2014a]. This validation/ holdout task does not only
+validation/holdout task (Yang et al., 2018), it is highly recommended to do so
+(Orme, 2015; Rao, 2014). This validation/ holdout task does not only
 help to check whether everything went right during data collection but
@@
 holdout task. You can use the <code>merge()</code> provided by
-<code>base</code> package [@base]. Afterward, you can read in your data
+<code>base</code> package (R Core Team, 2023). Afterward, you can read in your data
 file and enjoy <code>validateHOT</code>.
@@
 validation/holdout task and also in the simulation method, respectively.
-@rao2014a [p. 82] mentions the additive utility model stating that the
+Rao (2014, p. 82) mentions the additive utility model stating that the
 total utility of a profile or conjoint model is the sum of its attribute
@@
 divergence between the actual choice distribution and the predicted
-choice distribution [@ding2011; @philentropy]. Output provides both
+choice distribution (Ding et al., 2011; Drost, 2018). Output provides both
 divergence between predicted from observed and observed from predicted
@@
 We also include metrics from machine learning, i.e., the confusion
-matrix (e.g., @Burger2018). For all of the 5 provided functions, you
+matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
 currently have to have a **none** option in your data. We currently
@@
 $\frac{2 * precision * recall}{precision + recall}$ or stated
-differently by Burger [-@Burger2018] $\frac{2TP}{2TP + FP + FN}$. If you
+differently by Burger (2018) $\frac{2TP}{2TP + FP + FN}$. If you
 specify an optional <code>Group</code> argument the output is split by
@@
 
-<li><code>freqassort</code>: Inspired by the former
-[turfR](https://github.com/cran/turfR) package, <code>freqassort</code>
+<li><code>freqassort</code>: Inspired by the former <a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>freqassort</code>
 will give you the averaged frequency, how many products the participants
@@
 <li><code>reach</code>: Inspired by the former
-[turfR](https://github.com/cran/turfR) package, <code>reach</code> will
+<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
 give you the averaged percentage of how many participants you can reach
@@
 easy way on how to do this in *R*. Of course, there are other great
-packages which are even faster in running (i.e., @Metrics), however,
+packages which are even faster in running (i.e., Hamner & Frasco, 2018), however,
 these packages need some more data wrangling in order to use the
@@
 
-Moreover, as @yang2018 also report, often commercial studies do not use
+Moreover, as Yang et al. (2018) also report, often commercial studies do not use
 any validation task. Some market research companies (as far as we have
@@
 > &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this.
-However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package [@base].
+However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package (R Core Team, 2023).
 For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
@@
 However, the output is different if it is a factor or if it is labelled data.
-To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by @base.
+To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by R Core Team (2023).
 
@@
 ## References
+
+Burger, Scott V. 2018. <em>Introduction to Machine Learning with R: Rigorous Mathematical Analysis</em>. O'Reilly.
+
+Ding, Min, John R.
+Hauser, Songting Dong, Daria Dzyabura, Zhilin Yang, SU Chenting, and Steven P.
+Gaskin.
+2011.
+“Unstructured Direct Elicitation of Decision Rules.” <em>Journal of Marketing Research 48</em>(1): 116-27.
+[https://doi.org/10.1509/jmkr.48.1.116](https://doi.org/10.1509/jmkr.48.1.116)
+
+Drost, Hajk-Georg.
+2018.
+“Philentropy: Information Theory and Distance Quantification with R” <em>Journal of Open Source Software 3</em>(26), 765, [https://joss.theoj.org/papers/10.21105/joss.00765](https://joss.theoj.org/papers/10.21105/joss.00765).
+
+Hamner, Ben, and Michael Frasco. 2018. “Metrics: Evaluation Metrics for Machine Learning.” [https://CRAN.R-project.org/package=Metrics](https://CRAN.R-project.org/package=Metrics).
+
+Orme, Bryan K.
+2015.
+“Including Holdout Choice Tasks in Conjoint Studies.” [https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies](https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies).
+
+R Core Team. 2023. “R: A Language and Environment for Statistical Computing.” [https://www.R-project.org/](https://www.R-project.org/).
+
+Rao, Vithala R. 2014. <em>Applied Conjoint Analysis.</em> Springer Berlin Heidelberg. [https://doi.org/10.1007/978-3-540-87753-0](https://doi.org/10.1007/978-3-540-87753-0).
+
+Yang, Liu (Cathy), Olivier Toubia, and Martijn G.
+de Jong.
+2018.
+“Attention, Information Processing, and Choice in Incentive-Aligned Choice Experiments.” <em>Journal of Marketing Research 55</em>(6): 783–800.
+[https://doi.org/10.1177/0022243718817004](https://doi.org/10.1177/0022243718817004).

### 2023-06-12 R/Precision.R

@@ -1,19 +1,66 @@
 #' Precision
 #'
-#' @description test
+#' @description precision is one of the 5 metrics of the confusion matrix
+#' and is defined as \eqn{\frac{TP}{TP + FP}}, where TP =
+#' True Positives, FP = False Positives (see, e.g., Burger, 2018).
 #'
-#' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
-#' @param id column index
-#' @param Group optional grouping variable to get accuracy by group
-#' @param opts column indexes of the options included in the holdout task
-#' @param choice column index of the actual choice
-#' @param None column index
+#' @param data data frame with all relevant variables.
+#' @param id vector of column index of unique identifier in \code{data}.
+#' @param Group optional vector of column number to specify grouping variable
+#' to get \code{"precision"} by group
+#' @param opts vector of column indexes of the alternatives included in the
+#' validation/holdout task.
+#' @param choice vector of column index of the actual choice.
+#' @param None vector of column index of None alternative.
 #'
 #' @importFrom dplyr group_by summarise
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
 #'
+#' @details
+#' The current logic of \code{"precision"} is to provide whether a binary coded event is correctly predicted.
+#' To use the function a \code{"None"} alternative needs to be in the script.
+#' One potential usage is, for example, whether a buy or a no-buy condition
+#' was predicted correctly. For example, you have three alternatives plus
+#' a \code{"None"} alternative and you want to check whether a buy or no-buy was
+#' correctly predicted. This function can be helpful when you test whether or
+#' not your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#'
+#' \code{data} needs to be a data frame including the alternatives shown in
+#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#'
+#' \code{id} needs to be the column index of the id (unique for each participant)
+#' in \code{data}.
+#'
+#' \code{Group} optional Grouping variable, if results should be display by different conditions.
+#' Input of \code{Group} needs to be a vector of the column index of \code{Group}.
+#'
+#' \code{opts} is needed to specify the different alternatives in the validation/holdout
+#' task (also includes the None option).
[…]

### 2023-06-12 R/Specificity.R

@@ -1,6 +1,24 @@
 #' Specificity
 #'
-#' @description test
+#' @description specificity is one of the 5 metrics of the confusion matrix
+#' and is defined as \eqn{\frac{TN}{TN + FP}}, where TN =
+#' True Negatives, FP = False Positives (see, e.g., Burger, 2018).
+#'
+#' @param data data frame with all relevant variables.
+#' @param id vector of column index of unique identifier in \code{data}.
+#' @param Group optional vector of column number to specify grouping variable
+#' to get \code{"specificity"} by group
+#' @param opts vector of column indexes of the alternatives included in the
+#' validation/holdout task.
+#' @param choice vector of column index of the actual choice.
+#' @param None vector of column index of None alternative.
+#'
+#' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
+#' @param id column index
+#' @param Group optional grouping variable to get accuracy by group
+#' @param opts column indexes of the options included in the holdout task
+#' @param choice column index of the actual choice
+#' @param None column index
 #'
 #' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
 #' @param id column index
@@ -13,7 +31,49 @@
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
 #'
+#' @details
+#' The current logic of \code{"specificity"} is to provide whether a binary coded event is correctly predicted.
+#' To use the function a \code{"None"} alternative needs to be in the script.
+#' One potential usage is, for example, whether a buy or a no-buy condition
+#' was predicted correctly. For example, you have three alternatives plus
+#' a \code{"None"} alternative and you want to check whether a buy or no-buy was
+#' correctly predicted. This function can be helpful when you test whether or
+#' not your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#'
+#' \code{data} needs to be a data frame including the alternatives shown in
+#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#'
+#' \code{id} needs to be the column index of the id (unique for each participant)
+#' in \code{data}.
+#'
+#' \code{Group} optional Grouping variable, if results should be display by different conditions.
+#' Input of \code{Group} needs to be a vector of the column index of \code{Group}.
+#'
[…]

### 2023-06-13 README.Rmd
230613_v0234sdfsfwrwer

@@
 give you the averaged percentage of how many participants you can reach
-(buy at least one of the products) with your in the function determined
+(at least one of the products resemble a purchase option) with your in the function determined
 potential assortment. or the <code>method</code> argument you can decide

### 2023-06-13 R/Reach.R

@@ -1,18 +1,57 @@
 #' Percentage of participants that are reached by assortment
 #'
 #' @description
-#' test
+#' Reach function of TURF analysis to measure the number of  the averaged percentage of how many participants you can reach
+#' (at least one of the products resemble a purchase option) is reached with a specific product bundle assortment. Can either be calculated
+#' using 'First Choice' or 'threshold' rule. See Details section for more
+#' information and specifying the data in the correct way.
 #'
-#' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
-#' @param id column index
-#' @param bundles column indexes of the bundles included that should be included in the assortment
-#' @param Group optional grouping variable to get accuracy by group
-#' @param None column index
-#' @param method which method should be used, can be either \code{"First choice"} (only the bundle with highest utility is marked as purchase option if its above \code{"None"} utility) or \code{"threshold"} (all bundles with utility above \code{"None"} utility are marked as purchase option)
+#' @param data data data frame with all relevant variables.
+#' @param id vector of column index of unique identifier in \code{data}.
+#' @param Group optional vector of column number to specify grouping variable
+#' to get \code{"reach"} by group.
+#' @param bundles vector of column indexes of the bundles that should be included in the assortment.
+#' @param None vector of column index of None alternative.
+#' @param method character variable that needs to be specified to either \code{"First choice"} or \code{"threshold"}, please see Details.
 #'
 #' @importFrom dplyr group_by summarise
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
+#'
+#' #' @details
+#' Reach measures the averaged percentage of how many participants you can reach (at least one of the products resemble a purchase option)
+#' product assortment you are testing. The current logic of \code{reach()}
+#' is that it needs to exceed a threshold. In the case of \code{reach()}
+#' this threshold is referred to the \code{None} argument in \code{data}.
+#'
+#' \code{reach()} currently provides two methods:
+#' \itemize{
+#' \item \code{"First Choice"}: Only the alternative with the highest utility is considered,
+#' if its utility is above the utility of \code{None}, it is marked as potential purchase option.
+#' \item \code{"threshold"}: All alternatives are considered. if utility of alternative is
+#' larger than the utility of \code{None}, it is marked as potential purchase option.
+#' }
+#'
+#'
[…]

### 2023-06-15 README.Rmd
230615_001

@@
 ```{r}
-createHOT(
+HOT <- createHOT(
   data = CBC,
@@
   levels = c(1:3),
-                          labels = paste0("Group_", c(1:3)))
+  labels = paste0("Group_", c(1:3))
+)
 ```

### 2023-06-15 R/F1.R

@@ -64,8 +64,8 @@
 #' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -76,10 +76,11 @@
 #' )
 #'
 #' f1(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)
+#' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -91,7 +92,7 @@
 #' )
 #'
 #' f1(data = HOT, id = 1, Group = 10, opts = c(2:9), choice = 11, None = 9)
-#'
+#' }
 #' @export
 
 

### 2023-06-15 R/KL.R

@@ -56,8 +56,8 @@
 #'
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -68,9 +68,11 @@
 #' )
 #'
 #' kl(data = HOT, id = 1, opts = c(2:9), choice = 10)
+#' }
 #'
-#' library(validateHOT)
-#' createHOT(
+#' @examples
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -82,6 +84,7 @@
 #' )
 #'
 #' kl(data = HOT, id = 1, opts = c(2:9), choice = 11, Group = 10)
+#' }
 #'
 #' @export
 

### 2023-06-15 R/MedAE.R

@@ -41,8 +41,8 @@
 #'
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -53,10 +53,11 @@
 #' )
 #'
 #' medae(data = HOT, id = 1, opts = c(2:9), choice = 10)
+#' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -68,6 +69,7 @@
 #' )
 #'
 #' medae(data = HOT, id = 1, opts = c(2:9), choice = 11, Group = 10)
+#' }
 #'
 #' @export
 

### 2023-06-15 R/ShareOfPref.R

@@ -45,8 +45,8 @@
 #' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -57,10 +57,11 @@
 #' )
 #'
 #' shareofpref(data = HOT, id = 1, opts = c(2:9))
+#' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -72,6 +73,7 @@
 #' )
 #'
 #' shareofpref(data = HOT, id = 1, opts = c(2:9), Group = 10)
+#' }
 #'
 #' @export
 

### 2023-06-15 R/hitrate.R

@@ -38,8 +38,8 @@
 #'
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -50,10 +50,11 @@
 #' )
 #'
 #' hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)
+#' }
 #'
 #' @examples
-#' library(validateHOT)
-#' createHOT(
+#' \dontrun{
+#' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
 #'   None = 19,
@@ -65,6 +66,7 @@
 #' )
 #'
 #' hitrate(data = HOT, id = 1, opts = c(2:9), choice = 11, Group = 10)
+#' }
 #'
 #' @return a data frame
 #' @importFrom dplyr group_by summarise mutate

### 2023-06-15 tests/testthat/test-Accuracy.R

@@ -2,7 +2,7 @@ library(validateHOT)
 data(MaxDiff)
 
 ####################### Test wo Grouping variable ########################################
-createHOT(
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
@@ -83,7 +83,7 @@ test_that("accuracy() also working with data.frame not created with createHOT()"
 
 ####################### Test with Grouping variable ########################################
 
-createHOT(
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),

### 2023-06-15 tests/testthat/test-Specificity.R

@@ -1,8 +1,7 @@
 library(validateHOT)
-data(MaxDiff)
-
 ####################### Test wo Grouping variable ########################################
-createHOT(
+
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
@@ -76,7 +75,7 @@ test_that("specificity() also working with data.frame not created with createHOT
 
 ####################### Test with Grouping variable ########################################
 
-createHOT(
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),

### 2023-06-15 tests/testthat/test-freqAssort.R

@@ -1,8 +1,7 @@
 library(validateHOT)
-data(MaxDiff)
 
 ####################### Test wo Grouping variable ########################################
-createHOT(
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
@@ -96,7 +95,7 @@ test_that("freqassort() also working with data.frame not created with createHOT(
 
 ####################### Test with Grouping variable ########################################
 
-createHOT(
+HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
@@ -274,3 +273,4 @@ test_that("Right labels of 'Group' variable", {
   expect_true(Results$Group[3] == lev[2])
   expect_true(Results$Group[4] == lev[3])
 })
+

### 2023-06-16 R/MAE.R
230616_001

@@ -167,7 +167,7 @@ mae <- function(data, id, Group = NULL, opts, choice) {
 
     MeanAbsErr <- base::as.data.frame(base::sum(base::abs(MAE$Share - MAE$Pred)) / base::length(opts))
 
-    colnames(MeanAbsErr) <- "MAE"
+    base::colnames(MeanAbsErr) <- "MAE"
     return(MeanAbsErr)
   }
 

### 2023-06-16 R/MHP.R

@@ -142,7 +142,7 @@ mhp <- function(data, id, Group = NULL, opts, choice) {
 
     MeanHIT <- base::as.data.frame(base::mean(HOT$MHP))
 
-    colnames(MeanHIT) <- "MeanHitProb"
+    base::colnames(MeanHIT) <- "MeanHitProb"
     return(MeanHIT)
   }
 

### 2023-06-16 R/Reach.R

@@ -91,20 +91,20 @@
 
 reach <- function(data, id, Group = NULL, None, method, bundles) {
   if (method != "threshold" & method != "First Choice") {
-    stop("Error: ", method, " is not valid. Please specify whether to use 'threshold' or 'First Choice'")
+    base::stop("Error: ", method, " is not valid. Please specify whether to use 'threshold' or 'First Choice'")
   }
 
   varCheck <- c(bundles, None)
 
   for (i in 1:base::length(varCheck)) {
     if (!base::is.integer(data[[varCheck[i]]]) & !base::is.numeric(data[[varCheck[i]]])) {
-      stop("Error: ", colnames(data[varCheck[i]]), " needs to be numeric!")
+      base::stop("Error: ", base::colnames(data[varCheck[i]]), " needs to be numeric!")
     }
   }
 
   for (i in 1:base::length(varCheck)) {
     if (base::anyNA(data[varCheck[i]])) {
-      stop("Error: ", colnames(data[[varCheck[i]]]), " has missing values!")
+      base::stop("Error: ", base::colnames(data[[varCheck[i]]]), " has missing values!")
     }
   }
 
@@ -141,7 +141,7 @@ reach <- function(data, id, Group = NULL, None, method, bundles) {
 
       Reach <- base::as.data.frame(base::mean(base::ifelse(base::rowSums(WS_new[, c(2:base::ncol(WS_new))]) > 0, 1, 0)) * 100)
 
-      colnames(Reach) <- "reach"
+      base::colnames(Reach) <- "reach"
 
       return(Reach)
     }
@@ -171,7 +171,7 @@ reach <- function(data, id, Group = NULL, None, method, bundles) {
         }
       }
 
-      WS_new$reach <- ifelse(rowSums(WS_new[, c(3:ncol(WS_new))]) > 0, 1, 0)
+      WS_new$reach <- base::ifelse(base::rowSums(WS_new[, c(3:base::ncol(WS_new))]) > 0, 1, 0)
 
       Reach <- base::rbind(
         WS_new %>%
@@ -262,7 +262,7 @@ reach <- function(data, id, Group = NULL, None, method, bundles) {
 
       Reach <- base::as.data.frame(base::mean(base::ifelse(base::rowSums(WS_new[, c(2:base::ncol(WS_new))]) > 0, 1, 0)) * 100)
 
-      colnames(Reach) <- "reach"
+      base::colnames(Reach) <- "reach"
 
       return(Reach)
     }

### 2023-06-16 R/hitrate.R

@@ -143,7 +143,7 @@ hitrate <- function(data, id, Group = NULL, opts, choice) {
 
 
     HR <- base::as.data.frame(rbind(
-      (1 / length(opts) * 100),
+      (1 / base::length(opts) * 100),
       base::sum(base::as.integer(HOT$choice == HOT$pred)),
       (base::sum(base::as.integer(HOT$choice == HOT$pred)) / base::nrow(HOT) * 100)
     ))

### 2023-06-26 README.Rmd
updated version 230626

@@
 an optional <code>Group</code> argument the output is split by
-groups.</li>
+groups. Currently, you can choose between \eqn{log{_2}} and \eqn{log} as logarithm base.</li>
 
@@
 We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice.
-We can see that the hitrate of our example is `r round(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 1], digits  = 3)`.
+We can see that the hitrate of our example is `r round(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 2]), digits  = 3)`.
 

### 2023-06-26 R/Accuracy.R

@@ -46,6 +46,7 @@
 #' @importFrom dplyr group_by summarise
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
+#' @importFrom tibble tibble
 #'
 #' @return a data frame
 #'
@@ -104,146 +105,50 @@ accuracy <- function(data, id, Group = NULL, opts, choice, None) {
   }
 
   if (!base::is.null(Group) & base::anyNA(data[Group])) {
-    base::warning("Warning: Grouping variable contains NAs.")
+    base::warning("Warning: Grouping variable contains NAs!")
+  }
+
+  if (base::anyNA(data[,opts])) {
+    base::stop("Error: opts contains NAs!")
   }
 
   WS <- data[, c(id, Group, choice, opts)]
 
-  buy <- NULL
-  pred_buy <- NULL
-
   if (base::is.null(Group)) {
-    Options <- c()
+    base::colnames(WS) <- c("id", "choice", paste0("Option_", c(1:base::length(opts))))
+    WS$pred <- base::max.col(WS[,c(base::which(colnames(WS) == "Option_1"):
+                                     base::which(colnames(WS) == paste0("Option_", base::length(opts))))])
 
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Option_", k)
-      Options <- c(Options, name)
-    }
+    WS$buy <- base::ifelse(WS$choice != base::match(None, opts), 1, 2)
+    WS$pred_buy <- base::ifelse(WS$pred != base::match(None, opts), 1, 2)
 
-    newNames <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Opt_", k)
-      newNames <- c(newNames, name)
-    }
-
-    Perc <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Perc_", k)
-      Perc <- c(Perc, name)
-    }
-
-    base::colnames(WS) <- c("id", "choice", Options)
-
-    for (i in 1:base::length(newNames)) {
-      WS[, base::ncol(WS) + 1] <- 0
-      base::colnames(WS)[ncol(WS)] <- newNames[i]
-    }
-
-    for (i in 3:(base::ncol(WS) - base::length(opts))) {
-      WS[, (base::length(opts) + i)] <- base::exp(WS[i])
-    }
-
-    for (i in 1:base::length(Perc)) {
[…]

### 2023-06-26 R/F1.R

@@ -43,7 +43,7 @@
 #' validation/holdout task. Needs to be specified for \code{f1()}.
 #'
 #'
-#' @importFrom dplyr group_by summarise
+#' @importFrom dplyr group_by summarise as_tibble
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
 #'
@@ -106,148 +106,53 @@ f1 <- function(data, id, Group = NULL, opts, choice, None) {
   }
 
   if (!base::is.null(Group) & base::anyNA(data[Group])) {
-    base::warning("Warning: Grouping variable contains NAs.")
+    base::warning("Warning: Grouping variable contains NAs!")
+  }
+
+  if (base::anyNA(data[,opts])) {
+    base::stop("Error: opts contains NAs!")
   }
 
   WS <- data[, c(id, Group, choice, opts)]
 
-  buy <- NULL
-  pred_buy <- NULL
-
   if (base::is.null(Group)) {
-    Options <- c()
+    base::colnames(WS) <- c("id", "choice", paste0("Option_", c(1:base::length(opts))))
+    WS$pred <- base::max.col(WS[,c(base::which(colnames(WS) == "Option_1"):
+                                     base::which(colnames(WS) == paste0("Option_", base::length(opts))))])
 
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Option_", k)
-      Options <- c(Options, name)
-    }
+    WS$buy <- base::ifelse(WS$choice != base::match(None, opts), 1, 2)
+    WS$pred_buy <- base::ifelse(WS$pred != base::match(None, opts), 1, 2)
 
-    newNames <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Opt_", k)
-      newNames <- c(newNames, name)
-    }
-
-    Perc <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Perc_", k)
-      Perc <- c(Perc, name)
-    }
-
-    base::colnames(WS) <- c("id", "choice", Options)
-
-    for (i in 1:base::length(newNames)) {
-      WS[, base::ncol(WS) + 1] <- 0
-      base::colnames(WS)[base::ncol(WS)] <- newNames[i]
-    }
-
[…]

### 2023-06-26 R/Precision.R

@@ -13,7 +13,7 @@
 #' @param choice vector of column index of the actual choice.
 #' @param None vector of column index of None alternative.
 #'
-#' @importFrom dplyr group_by summarise
+#' @importFrom dplyr group_by summarise as_tibble
 #' @importFrom magrittr "%>%"
 #' @importFrom labelled is.labelled val_labels
 #'
@@ -101,147 +101,57 @@ precision <- function(data, id, Group = NULL, opts, choice, None) {
     base::stop("Error: Choice must be numeric!")
   }
 
+  if (!base::is.integer(data[[None]]) & !base::is.numeric(data[[None]])) {
+    base::stop("Error: None must be numeric!")
+  }
+
   if (!base::is.null(Group) & base::anyNA(data[Group])) {
-    base::warning("Warning: Grouping variable contains NAs.")
+    base::warning("Warning: Grouping variable contains NAs!")
+  }
+
+  if (base::anyNA(data[,opts])) {
+    base::stop("Error: opts contains NAs!")
   }
 
   WS <- data[, c(id, Group, choice, opts)]
 
-  buy <- pred_buy <- NULL
-
   if (base::is.null(Group)) {
-    Options <- c()
+      base::colnames(WS) <- c("id", "choice", paste0("Option_", c(1:base::length(opts))))
+      WS$pred <- base::max.col(WS[,c(base::which(colnames(WS) == "Option_1"):
+                                       base::which(colnames(WS) == paste0("Option_", base::length(opts))))])
 
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Option_", k)
-      Options <- c(Options, name)
-    }
+      WS$buy <- base::ifelse(WS$choice != base::match(None, opts), 1, 2)
+      WS$pred_buy <- base::ifelse(WS$pred != base::match(None, opts), 1, 2)
 
-    newNames <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Opt_", k)
-      newNames <- c(newNames, name)
-    }
-
-    Perc <- c()
-    for (k in 1:base::length(opts)) {
-      name <- base::paste0("Perc_", k)
-      Perc <- c(Perc, name)
-    }
-
-    base::colnames(WS) <- c("id", "choice", Options)
-
[…]

### 2023-06-26 tests/testthat/test-Accuracy.R

@@ -1,6 +1,3 @@
-library(validateHOT)
-data(MaxDiff)
-
 ####################### Test wo Grouping variable ########################################
 HOT <- createHOT(
   data = MaxDiff, None = 19,
@@ -28,7 +25,7 @@ test_that("Test plausability of results", {
 })
 
 test_that("Make sure test data is correct", {
-  expect_equal(accuracy(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1], 70)
+  expect_equal(as.numeric(accuracy(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1]), 70)
 })
 
 test_that("Wrong format Choice", {
@@ -235,3 +232,4 @@ test_that("Right labels of 'Group' variable", {
   expect_true(Results$Group[3] == lev[2])
   expect_true(Results$Group[4] == lev[3])
 })
+

### 2023-06-26 tests/testthat/test-MAE.R

@@ -1,4 +1,3 @@
-library(validateHOT)
 ####################### Test wo Grouping variable ########################################
 
 HOT <- createHOT(
@@ -22,7 +21,7 @@ test_that("Labeling correct", {
 })
 
 test_that("Count of correct predicted people", {
-  expect_equal(base::round(mae(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 1], digits = 3), 4.933)
+  expect_equal(base::round(as.numeric(mae(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 1]), digits = 3), 4.933)
 })
 
 test_that("Wrong format Choice", {
@@ -71,7 +70,6 @@ test_that("mae() also working with data.frame not created with createHOT()", {
 
 
 ####################### Test with Grouping variable ########################################
-
 HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,

### 2023-06-26 tests/testthat/test-Precision.R

@@ -1,4 +1,3 @@
-library(validateHOT)
 ####################### Test wo Grouping variable ########################################
 HOT <- createHOT(
   data = MaxDiff, None = 19,
@@ -26,7 +25,7 @@ test_that("Test plausability of results", {
 })
 
 test_that("Make sure test data is correct", {
-  expect_equal(precision(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1], 70.69)
+  expect_equal(round(as.numeric(precision(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1]), digits = 2), 70.69)
 })
 
 test_that("Wrong format Choice", {
@@ -71,7 +70,6 @@ test_that("precision() also working with data.frame not created with createHOT()
 })
 
 ####################### Test with Grouping variable ########################################
-
 HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
@@ -216,3 +214,4 @@ test_that("Right labels of 'Group' variable", {
   expect_true(Results$Group[3] == lev[2])
   expect_true(Results$Group[4] == lev[3])
 })
+

### 2023-06-26 tests/testthat/test-Reach.R

@@ -1,6 +1,4 @@
-library(validateHOT)
 ####################### Test wo Grouping variable ########################################
-
 HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
@@ -48,8 +46,8 @@ test_that("Independent of method, results should remain same", {
 })
 
 test_that("Make sure test data is correct", {
-  expect_equal(base::round(reach(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")[1, 1], digits = 3), 70.000)
-  expect_equal(base::round(reach(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")[1, 1], digits = 3), 70.000)
+  expect_equal(base::round(as.numeric(reach(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")[1, 1]), digits = 3), 70.000)
+  expect_equal(base::round(as.numeric(reach(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")[1, 1]), digits = 3), 70.000)
 })
 
 
@@ -98,7 +96,6 @@ test_that("reach() also working with data.frame not created with createHOT()", {
 })
 
 ####################### Test with Grouping variable ########################################
-
 HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,

### 2023-06-26 tests/testthat/test-Recall.R

@@ -1,5 +1,3 @@
-library(validateHOT)
-
 ####################### Test wo Grouping variable ########################################
 HOT <- createHOT(
   data = MaxDiff, None = 19,
@@ -27,7 +25,7 @@ test_that("Test plausability of results", {
 })
 
 test_that("Make sure test data is correct", {
-  expect_equal(recall(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1], 91.11)
+  expect_equal(round(as.numeric(recall(data = HOT, id = 1, opts = c(2:9), choice = 10, None = 9)[1, 1]), digits = 2), 91.11)
 })
 
 test_that("Wrong format Choice", {
@@ -216,3 +214,4 @@ test_that("Right labels of 'Group' variable", {
   expect_true(Results$Group[3] == lev[2])
   expect_true(Results$Group[4] == lev[3])
 })
+

### 2023-06-26 tests/testthat/test-ShareofPref.R

@@ -1,6 +1,4 @@
-library(validateHOT)
 ####################### Test wo Grouping variable ########################################
-
 HOT <- createHOT(
   data = MaxDiff, None = 19,
   id = 1, prod = 7,
@@ -22,11 +20,11 @@ test_that("Structure of Output", {
 test_that("Structure of Output", {
   expect_equal(base::nrow(shareofpref(data = HOT, id = 1, opts = c(2:9))), 8)
 
-  expect_equal(base::ncol(shareofpref(data = HOT, id = 1, opts = c(2:9))), 4)
+  expect_equal(base::ncol(shareofpref(data = HOT, id = 1, opts = c(2:9))), 5)
 })
 
 test_that("Labeling correct", {
-  expect_equal(colnames(shareofpref(data = HOT, id = 1, opts = c(2:9))), c("Options", "Mean", "Lower CI", "Upper CI"))
+  expect_equal(colnames(shareofpref(data = HOT, id = 1, opts = c(2:9))), c("Options", "Mean", "se", "Lower CI", "Upper CI"))
 })
 
 
@@ -35,18 +33,18 @@ test_that("Test plausability of results", {
 
   for (i in 1:nrow(Results)) {
     expect_true(Results[i, 2] <= 100)
-    expect_true(Results[i, 3] < Results[i, 4] & Results[i, 3] < Results[i, 2])
-    expect_true(Results[i, 4] > Results[i, 3])
+    expect_true(Results[i, 4] < Results[i, 5] & Results[i, 4] < Results[i, 2])
+    expect_true(Results[i, 5] > Results[i, 4])
   }
 
-  expect_equal(base::sum(Results[, 2]), 100)
+  expect_equal(as.numeric(base::sum(Results[, 2])), 100)
 })
 
 
 test_that("Make sure test data is correct", {
-  expect_equal(base::round(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 2], digits = 3), 18.268)
-  expect_equal(base::round(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 3], digits = 3), 10.189)
-  expect_equal(base::round(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 4], digits = 3), 26.346)
+  expect_equal(base::round(as.numeric(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 2]), digits = 3), 18.268)
[…]

### 2023-08-02 README.Rmd
230802_changes

--- 2023-06-15 README.Rmd
@@
 your utility scores. Although commercial studies often do not include a
-validation/holdout task (Yang et al., 2018), it is highly recommended to do so
+validation/ holdout task (Yang et al., 2018), it is highly recommended to do so
 (Orme, 2015; Rao, 2014). This validation/ holdout task does not only
@@
 This function creates the total utilities for each alternative in the
-validation/holdout task and also in the simulation method, respectively.
+validation/ holdout task and also in the simulation method, respectively.
 Rao (2014, p. 82) mentions the additive utility model stating that the
@@
 percentage of how many choices were correctly predicted. If you specify
-an optional <code>Group</code> argument the output is split by
+an optional <code>group</code> argument the output is split by
 groups.</li>
@@
 due to the asymmetry of the Kullback-Leibler divergence. If you specify
-an optional <code>Group</code> argument the output is split by
-groups.</li>
+an optional <code>group</code> argument the output is split by
+groups. Currently, you can choose between \eqn{log{_2}} and \eqn{log} as logarithm base.</li>
 
@@
 predicted and stated choice share. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
+<code>group</code> argument the output is split by groups.</li>
 
 <li><code>medae</code>: since the averaged absolute error can be highly
-influenced by the If you specify an optional <code>Group</code> argument
+influenced by the If you specify an optional <code>group</code> argument
 the output is split by groups.</li>
@@
 choice in the validation/ holdout task. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
+<code>group</code> argument the output is split by groups.</li>
 
@@
 between predicted and stated choice share. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
+<code>group</code> argument the output is split by groups.</li>
 
@@
 $\frac{TP + TN}{TP + FP + TN + FN}$. If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
+<code>group</code> argument the output is split by groups.</li>
 
@@
 differently by Burger (2018) $\frac{2TP}{2TP + FP + FN}$. If you
-specify an optional <code>Group</code> argument the output is split by
+specify an optional <code>group</code> argument the output is split by
 groups.</li>
@@
 <li><code>precision</code>: defined as $\frac{TP}{TP + FP}$. If you
-specify an optional <code>Group</code> argument the output is split by
+specify an optional <code>group</code> argument the output is split by
 groups.</li>
@@
 <li><code>recall</code>: defined as $\frac{TP}{TP + FN}$. If you specify
-an optional <code>Group</code> argument the output is split by
+an optional <code>group</code> argument the output is split by
 groups.</li>
@@
 <li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$. If you
-specify an optional <code>Group</code> argument the output is split by
+specify an optional <code>group</code> argument the output is split by
 groups.</li>
@@
 will choose from your in the function determined potential assortment.
-For the <code>method</code> argument you can decide between <code>method
-= "threshold"</code> (if utility of product is larger than the utility
-of <code>None</code>, it is marked as potential purchase option) and
-<code>method = "First Choice"</code> (only product with highest utility
-is considered. If its utility is above the utility of <code>None</code>,
-it is marked as potential purchase option). If you specify an optional
-<code>Group</code> argument the output is split by groups.</li>
+Again, you have to define a `none` alternative. `freqassort` uses the *threshold* approach,
+meaning if the utility of one product is above the utility of `none`,
+it is marked as potential purchase option. If you specify an optional
+<code>group</code> argument the output is split by groups.</li>
 
@@
 (at least one of the products resemble a purchase option) with your in the function determined
-potential assortment. or the <code>method</code> argument you can decide
-between <code>method = "threshold"</code> (if utility of product is
-larger than the utility of <code>None</code>, it is marked as potential
-purchase option) and <code>method = "First Choice"</code> (only product
-with highest utility is considered. If its utility is above the utility
-of <code>None</code>, it is marked as potential purchase option). If you
-specify an optional <code>Group</code> argument the output is split by
-groups.</li>
+potential assortment. `reach` also uses the *threshold* approach (see above).</li>
 
@@
 calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$. If
-you specify an optional <code>Group</code> argument the output is split
+you specify an optional <code>group</code> argument the output is split
 by groups and provided in a list element.</li>
@@
 easy way on how to do this in *R*. Of course, there are other great
-packages which are even faster in running (i.e., Hamner & Frasco, 2018), however,
+packages which are faster in running (i.e., Hamner & Frasco, 2018), however,
 these packages need some more data wrangling in order to use the
@@
 As mentioned above, all the attributes are part-worth coded, therefore, we set <code>coding = c(0, 0, 0)</code>.
-Finally, we specify the method of prefernce measurement technique, which is <code>method = "CBC"</code> in our case and the column index of the actual participant's choice (<code>choice</code>).
+Finally, we specify the method of preference measurement technique, which is <code>method = "CBC"</code> in our case and the column index of the actual participant's choice (<code>choice</code>).
 If you run the code, a data frame called <code>HOT</code> (short form of **H**old**o**ut **t**ask) will be returned to the global environment.
 
-> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this.
+> &#10071; <code>createHOT</code> is currently just taking indexes instead of column names, please be aware of this.
 However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package (R Core Team, 2023).
@@
 First, we will test the <code>hitrate()</code> function.
-We specify the <code>data</code>, the column index of <code>id</code>, the column index of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the column index of the choice.
-We can see that the hitrate of our example is `r round(hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)[3, 1], digits  = 3)`.
+We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the choice.
+We can see that the hitrate of our example is `r round(as.numeric(hitrate(data = HOT, opts = c(2:5), choice = choice)[3, 2]), digits  = 3)`.
 
 ```{r}
-hitrate(data = HOT, id = 1, opts = c(2:5), choice = 6)
+hitrate(data = HOT, opts = c(2:5), choice = choice)
 ```
@@
 ```{r}
-mae(data = HOT, id = 1, opts = c(2:5), choice = 6)
+mae(data = HOT, opts = c(2:5), choice = choice)
 ```
@@
 ```{r}
-accuracy(data = HOT, id = 1, opts = c(2:5), None = 5, choice = 6)
+accuracy(data = HOT, opts = c(2:5), choice = choice, none = None)
 ```
@@
 We will use the <code>reach()</code> function and use the threshold approach.
-To specify the bundles we are offering we use the <code>bundles</code> argument in our function.
+To specify the bundles we are offering we use the <code>opts</code> argument in our function.
 
 ```{r}
-reach(data = HOT, id = 1, bundles = c(2:4), None = 5, method = "threshold")
+reach(data = HOT, opts = c(Option_1:Option_3), none = None)
 ```
@@
 Let us again begin with the <code>hitrate()</code> function.
-To do so, we specify the column index of the grouping variable in the <code>Group</code> argument.
+To do so, we specify the column name of the grouping variable in the <code>group</code> argument.
 
 ```{r}
-hitrate(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
+hitrate(data = CBC, opts = c(Option_1:None), choice = choice, group = Group)
 ```
@@
 However, the output is different if it is a factor or if it is labelled data.
-To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by R Core Team (2023).
+To proof this we just quickly change <code>group</code> in a factor by using the <code>factor()</code> function provided by R Core Team (2023).
 
@@
 ```{r}
-mhp(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
+mhp(data = CBC, opts = c(Option_1:None), choice = choice, group = Group)
 ```

### 2023-08-02 R/F1.R

@@ -5,49 +5,43 @@
 #' differently by Burger (2018) \eqn{\frac{2TP}{2TP + FP + FN}}, where TP =
 #' True Positives, FP = False Positives, and FN = False Negatives.
 #'
-#' @param data data frame with all relevant variables.
-#' @param id vector of column index of unique identifier in \code{data}.
-#' @param Group optional vector of column number to specify grouping variable
-#' to get \code{"f1"} by group
-#' @param opts vector of column indexes of the alternatives included in the
-#' validation/holdout task.
-#' @param choice vector of column index of the actual choice.
-#' @param None vector of column index of None alternative.
+#' @param data data frame with all relevant variables
+#' @param group optional column name(s) to specify grouping variable(s)
+#' to get \code{"f1"} by group(s)
+#' @param opts column names of the alternatives included in the
+#' validation/holdout task
+#' @param choice column name of the actual choice
+#' @param none column name of none alternative
 #'
 #' @details
 #' The current logic of \code{"f1"} is to provide whether a binary coded event is correctly predicted.
-#' To use the function a \code{"None"} alternative needs to be in the script.
+#' To use the function a \code{"none"} alternative needs to be in the script.
 #' One potential usage is, for example, whether a buy or a no-buy condition
 #' was predicted correctly. For example, you have three alternatives plus
-#' a \code{"None"} alternative and you want to check whether a buy or no-buy was
+#' a \code{"none"} alternative and you want to check whether a buy or no-buy was
 #' correctly predicted. This function can be helpful when you test whether or
 #' not your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#' This function was programmed to predict demand for a MaxDiff, CBC, or ACBC.
 #'
 #' \code{data} needs to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
[…]

### 2023-08-02 R/MHP.R

@@ -5,20 +5,12 @@
 #' holdout task. Calculates the hit/ choice probability of the actual choice
 #' in the validation/ holdout task.
 #'
-#' @param data a data frame
-#' @param id vector of column index of unique identifier in \code{data}.
-#' @param Group optional vector of column number to specify grouping variable
-#' to get \code{"mhp"} by group.
-#' @param opts vector of column indexes of the alternatives included in the
-#' validation/ holdout task.
-#' @param choice vector of column index of the actual choice.
-#'
-#' @return a data frame
-#' @importFrom dplyr group_by summarise mutate
-#' @importFrom magrittr "%>%"
-#' @importFrom labelled is.labelled val_labels
-#' @importFrom tibble tibble
-#'
+#' @param data data frame with all relevant variables
+#' @param group optional column name(s) to specify grouping variable(s)
+#' to get \code{"mhp"} by group(s)
+#' @param opts column names of the alternatives included in the
+#' validation/holdout task
+#' @param choice column name of the actual choice
 #'
 #' @details
 #' Mean hit probability (MHP) measures the averaged hit probability of participants actual
@@ -27,34 +19,19 @@
 #' \code{data} needs to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
-#' \code{id} needs to be the column index of the id (unique for each participant)
-#' in \code{data}.
+#' \code{group} optional Grouping variable, if results should be display by different groups.
+#' Needs to be column name of variables in \code{data}.
 #'
-#' \code{Group} optional Grouping variable, if results should be display by different conditions.
-#' Input of \code{Group} needs to be a vector of the column index of \code{Group}.
+#' \code{opts} is needed to specify the different alternatives in the validation/holdout
+#' task (also includes the \code{none} alternative).
+#' Input of \code{opts} needs to be column names of variables in \code{data}.
 #'
[…]

### 2023-08-02 R/Recall.R

@@ -4,55 +4,44 @@
 #' and is defined as \eqn{\frac{TP}{TP + FN}}, where TP =
 #' True Positives, FN = False Negatives (see, e.g., Burger, 2018).
 #'
-#' @param data data frame with all relevant variables.
-#' @param id vector of column index of unique identifier in \code{data}.
-#' @param Group optional vector of column number to specify grouping variable
-#' to get \code{"recall"} by group
-#' @param opts vector of column indexes of the alternatives included in the
-#' validation/holdout task.
-#' @param choice vector of column index of the actual choice.
-#' @param None vector of column index of None alternative.
-#'
-#' @param data data frame including Holdout Options and actual \code{"choice"} and \code{"Group"} if optional argument is defined
-#' @param id column index
-#' @param Group optional grouping variable to get accuracy by group
-#' @param opts column indexes of the options included in the holdout task
-#' @param choice column index of the actual choice
-#' @param None column index
-#'
-#' @importFrom dplyr group_by summarise as_tibble
-#' @importFrom magrittr "%>%"
-#' @importFrom labelled is.labelled val_labels
+#' @param data data frame with all relevant variables
+#' @param group optional column name(s) to specify grouping variable(s)
+#' to get \code{"recall"} by group(s)
+#' @param opts column names of the alternatives included in the
+#' validation/holdout task
+#' @param choice column name of the actual choice
+#' @param none column name of none alternative
 #'
 #' @details
 #' The current logic of \code{"recall"} is to provide whether a binary coded event is correctly predicted.
-#' To use the function a \code{"None"} alternative needs to be in the script.
+#' To use the function a \code{"none"} alternative needs to be in the script.
 #' One potential usage is, for example, whether a buy or a no-buy condition
 #' was predicted correctly. For example, you have three alternatives plus
-#' a \code{"None"} alternative and you want to check whether a buy or no-buy was
+#' a \code{"none"} alternative and you want to check whether a buy or no-buy was
[…]

### 2023-08-02 R/hitrate.R

@@ -1,56 +1,41 @@
 #' Hit Rate
 #'
 #' @description \code{hitrate} measures number of times a choice was correctly predicted in a validation task.
-#' @param data frame with all relevant variables.
-#' @param id vector of column index of unique identifier in \code{data}.
-#' @param Group optional vector of column number to specify grouping variable
-#' to get \code{"hitrate"} by group.
-#' @param opts vector of column indexes of the alternatives included in the
-#' validation/holdout task.
-#' @param choice vector of column index of the actual choice.
+#'
+#' @param data data frame with all relevant variables
+#' @param group optional column name(s) to specify grouping variable(s)
+#' to get \code{"hitrate"} by group(s)
+#' @param opts column names of the alternatives included in the
+#' validation/holdout task
+#' @param choice column name of the actual choice
 #'
 #' @details
 #' \code{hitrate} measures number of times a participant's choice was correctly
 #' predicted by our model.
-#' Output contains the following 3 metrics:
+#' Output contains the following 4 metrics:
 #' \itemize{
 #' \item \code{"chance"} chance level (\eqn{\frac{1}{number of alternatives}}) in percentage
 #' \item \code{"no."} absolute value of correctly predicted choices
 #' \item \code{"\%"} correctly predicted choices in percentage
+#' \item \code{"n"} total number of choices
 #' }
 #'
 #' \code{data} needs to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
-#' \code{id} needs to be the column index of the id (unique for each participant)
-#' in \code{data}.
-#'
-#' \code{Group} optional Grouping variable, if results should be display by different conditions.
-#' Input of \code{Group} needs to be a vector of the column index of \code{Group}.
+#' \code{group} optional Grouping variable, if results should be display by different groups.
+#' Needs to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the validation/holdout
-#' task (also includes the None option).
[…]

### 2023-08-02 tests/testthat/test-HitRate.R

@@ -1,92 +1,3 @@
-####################### Test wo Grouping variable ########################################
-HOT <- createHOT(
-  data = MaxDiff, None = 19,
-  id = 1, prod = 7,
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-  choice = 20, method = "MaxDiff"
-)
-
-test_that("Structure of Output", {
-  expect_true(base::is.data.frame(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)))
-})
-
-test_that("Structure of Output", {
-  expect_equal(base::nrow(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)), 3)
-  expect_equal(base::ncol(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)), 2)
-})
-
-test_that("Labeling correct", {
-  expect_equal(base::colnames(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)), c("name", "stats"))
-})
-
-
-
-test_that("Chance Level correct", {
-  expect_equal(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 2]), (1 / 8 * 100))
-})
-
-test_that("Count of correct predicted people", {
-  expect_equal(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[2, 2]), 39)
-})
-
-test_that("Test plausability of results", {
-  expect_true(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 2]) <= 100 & as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 2]) >= 0)
-  expect_true(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[2, 2]) <= base::nrow(HOT))
-  expect_true(as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[3, 2]) <= 100 & as.numeric(hitrate(data = HOT, id = 1, opts = c(2:9), choice = 10)[3, 2]) >= 0)
-})
-
-test_that("Hit Rate % correct", {
[…]

### 2023-08-02 tests/testthat/test-MedAE.R

@@ -1,76 +1,3 @@
-####################### Test wo Grouping variable ########################################
-HOT <- createHOT(
-  data = MaxDiff, None = 19,
-  id = 1, prod = 7,
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-  choice = 20, method = "MaxDiff"
-)
-
-test_that("Structure of Output", {
-  expect_true(base::is.data.frame(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)))
-})
-
-test_that("Structure of Output", {
-  expect_equal(base::nrow(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)), 1)
-  expect_equal(base::ncol(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)), 1)
-})
-
-
-test_that("Labeling correct", {
-  expect_equal(base::colnames(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)), "MedAE")
-})
-
-test_that("Count of correct predicted people", {
-  expect_equal(base::round(as.numeric(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 1]), digits = 3), 1.988)
-})
-
-test_that("Wrong format Choice", {
-  HOT2 <- HOT
-  HOT2$choice <- base::as.character(HOT2$choice)
-  expect_error(medae(data = HOT2, id = 1, opts = c(2:9), choice = 10))
-})
-
-test_that("Wrong format Option", {
-  HOT2 <- HOT
-  HOT2$Option_2 <- base::as.character(HOT2$Option_2)
-  expect_error(medae(data = HOT2, id = 1, opts = c(2:9), choice = 10))
-})
-
-
-test_that("Test plausability of results", {
-  expect_true(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)[1, 1] >= 0)
-})
-
-test_that("Missings", {
-  HOT2 <- HOT
-  HOT2[1, 5] <- NA
-  expect_error(medae(data = HOT2, id = 1, opts = c(2:9), choice = 10))
-})
-
-test_that("No missings in output", {
-  expect_false(base::anyNA(medae(data = HOT, id = 1, opts = c(2:9), choice = 10)))
-})
-
-
-test_that("medae() also working with data.frame not created with createHOT()", {
-  newHOT <- base::data.frame(
-    ID = c(1:10),
-    Option_1 = stats::runif(10, min = -5, max = 5),
[…]

### 2023-08-02 tests/testthat/test-ShareofPref.R

@@ -1,88 +1,3 @@
-####################### Test wo Grouping variable ########################################
-HOT <- createHOT(
-  data = MaxDiff, None = 19,
-  id = 1, prod = 7,
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-  choice = 20, method = "MaxDiff"
-)
-
-test_that("Columns needs to be numeric", {
-  HOT2 <- HOT
-  HOT2$Option_2 <- as.character(HOT2$Option_2)
-  expect_error(shareofpref(data = HOT2, id = 1, opts = c(2:9)))
-})
-
-test_that("Structure of Output", {
-  expect_true(base::is.data.frame(shareofpref(data = HOT, id = 1, opts = c(2:9))))
-})
-
-
-test_that("Structure of Output", {
-  expect_equal(base::nrow(shareofpref(data = HOT, id = 1, opts = c(2:9))), 8)
-
-  expect_equal(base::ncol(shareofpref(data = HOT, id = 1, opts = c(2:9))), 5)
-})
-
-test_that("Labeling correct", {
-  expect_equal(colnames(shareofpref(data = HOT, id = 1, opts = c(2:9))), c("Options", "Mean", "se", "Lower CI", "Upper CI"))
-})
-
-
-test_that("Test plausability of results", {
-  Results <- shareofpref(data = HOT, id = 1, opts = c(2:9))
-
-  for (i in 1:nrow(Results)) {
-    expect_true(Results[i, 2] <= 100)
-    expect_true(Results[i, 4] < Results[i, 5] & Results[i, 4] < Results[i, 2])
-    expect_true(Results[i, 5] > Results[i, 4])
-  }
-
-  expect_equal(as.numeric(base::sum(Results[, 2])), 100)
-})
-
-
-test_that("Make sure test data is correct", {
-  expect_equal(base::round(as.numeric(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 2]), digits = 3), 18.268)
-  expect_equal(base::round(as.numeric(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 4]), digits = 3), 10.189)
-  expect_equal(base::round(as.numeric(shareofpref(data = HOT, id = 1, opts = c(2:9))[1, 5]), digits = 3), 26.346)
-})
-
-
-test_that("Wrong format Option", {
-  names <- base::colnames(HOT)[c(2:9)]
-
[…]

### 2023-08-02 tests/testthat/test-freqAssort.R

@@ -1,98 +1,3 @@
-####################### Test wo Grouping variable ########################################
-HOT <- createHOT(
-  data = MaxDiff, None = 19,
-  id = 1, prod = 7,
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-  choice = 20, method = "MaxDiff"
-)
-
-test_that("Columns needs to be numeric", {
-  HOT2 <- HOT
-  HOT2$Option_2 <- as.character(HOT2$Option_2)
-  expect_error(freqassort(data = HOT2, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold"))
-  expect_error(freqassort(data = HOT2, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold"))
-})
-
-test_that("Structure of Output", {
-  expect_true(base::is.data.frame(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")))
-  expect_true(base::is.data.frame(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")))
-})
-
-test_that("Right method", {
-  expect_error(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "test"))
-})
-
-test_that("Structure of Output", {
-  expect_equal(base::nrow(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")), 1)
-  expect_equal(base::ncol(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")), 1)
-
-  expect_equal(base::nrow(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")), 1)
-  expect_equal(base::ncol(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")), 1)
-})
-
-test_that("Labeling correct", {
-  expect_equal(base::colnames(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "threshold")), "Frequency")
-  expect_equal(base::colnames(freqassort(data = HOT, id = 1, bundles = c(2, 3, 7), None = 9, method = "First Choice")), "Frequency")
-})
-
-
-test_that("Test plausability of results", {
[…]

### 2023-08-21 R/Recall.R
update01_230821

@@ -13,27 +13,26 @@
 #' @param none column name of none alternative
 #'
 #' @details
-#' The current logic of \code{"recall"} is to provide whether a binary coded event is correctly predicted.
-#' To use the function a \code{"none"} alternative needs to be in the script.
+#' The current logic of \code{"recall"} is to determine whether a binary coded is correctly predicted by the model.
+#' To use the function a \code{"none"} alternative has to be included in the validation/holdout task.
 #' One potential usage is, for example, whether a buy or a no-buy condition
 #' was predicted correctly. For example, you have three alternatives plus
 #' a \code{"none"} alternative and you want to check whether a buy or no-buy was
-#' correctly predicted. This function can be helpful when you test whether or
-#' not your model significantly overestimates or underestimates, for example, a purchase likelihood.
-#' This function was programmed to predict demand for a MaxDiff, CBC, or ACBC.
+#' correctly predicted. This function can be helpful when you test, for example, if
+#' your model significantly overestimates or underestimates, for example, a purchase likelihood.
 #'
-#' \code{data} needs to be a data frame including the alternatives shown in
+#' \code{data} has to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
 #' \code{group} optional Grouping variable, if results should be display by different conditions.
-#' Needs to be column name of variables in \code{data}.
+#' Has to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the validation/holdout
 #' task (also includes the \code{none} alternative).
-#' Input of \code{opts} needs to be column names of variables in \code{data}.
+#' Input of \code{opts} has to be column names of variables in \code{data}.
 #'
 #' \code{choice} to specify column of actual choice.
-#' Input of opts \code{choice} needs to be column name of actual choice.
+#' Input of opts \code{choice} has to be column name of actual choice.
 #'
 #' \code{none} to specify column name of the \code{none} alternative in the
 #' validation/holdout task.
@@ -94,7 +93,7 @@ recall <- function(data, group, opts, choice, none) {
 
   if (!(data %>% dplyr::select(., {{ none }}) %>% base::colnames()) %in%
     (data %>% dplyr::select(., {{ opts }}) %>% base::colnames())) {
[…]

### 2023-08-22 R/F1.R
update_230822_v01

@@ -26,7 +26,7 @@
 #' \code{data} has to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
-#' \code{group} optional Grouping variable, if results should be display by different conditions.
+#' \code{group} optional grouping variable, if results should be displayed by different conditions.
 #' Has to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the validation/holdout
@@ -139,16 +139,16 @@ f1 <- function(data, group, opts, choice, none) {
 
   return(data %>%
     dplyr::mutate(
-      pred = base::max.col(dplyr::pick({{ opts }})),
+      pred = base::max.col(dplyr::pick({{ opts }})), # store column index with highest utility
       buy = base::ifelse({{ choice }} != base::match(
         data %>% dplyr::select(., {{ none }}) %>% colnames(),
         data %>% dplyr::select(., {{ opts }}) %>% colnames()
-      ), 1, 2),
+      ), 1, 2), # dichotomies actual choice (1 = prod, 2 = none)
       pred = base::ifelse(pred != base::match(
         data %>% dplyr::select(., {{ none }}) %>% colnames(),
         data %>% dplyr::select(., {{ opts }}) %>% colnames()
       ), 1, 2)
-    ) %>%
+    ) %>% # dichotomies pred choice (1 = prod, 2 = none)
     dplyr::group_by(pick({{ group }})) %>%
     dplyr::summarise(
       f1 = 100 * ((2 * (base::sum(buy == 1 & pred == 1))) / (((2 * (base::sum(buy == 1 & pred == 1))) + base::sum(buy == 2 & pred == 1) + base::sum(buy == 1 & pred == 2)))

### 2023-08-22 R/Reach.R

@@ -1,7 +1,7 @@
 #' Percentage of participants that are reached by assortment
 #'
 #' @description
-#' Reach function of TURF analysis to measure the number of  the averaged percentage of how many participants you can reach
+#' Reach function of **T**(otal) **U**(nduplicated) **R**(Reach) and **F**(requency) analysis to measure the number of  the averaged percentage of how many participants you can reach
 #' (at least one of the products resemble a purchase option) is reached with a specific product bundle assortment.
 #'
 #' @param data data frame with all relevant variables
@@ -13,18 +13,18 @@
 #' @details
 #' \code{"reach"} calculates the the percentage of consumers that would be reached with the
 #' product assortment you are testing. The current logic of \code{reach()}
-#' is that it needs to exceed a threshold. In the case of \code{reach()}
+#' is that the utility of an alternative has to exceed a threshold. In the case of \code{reach()}
 #' this threshold is referred to the \code{none} argument in \code{data}.
 #'
 #'
-#' \code{data} needs to be a data frame including the alternatives that should be tested
+#' \code{data} has to be a data frame including the alternatives that should be tested
 #'
-#' \code{group} optional Grouping variable, if results should be display by different conditions.
-#' Needs to be column name of variables in \code{data}.
+#' \code{group} optional Grouping variable, if results should be displayed by different conditions.
+#' Has to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the
 #' product assortment that should be considered.
-#' Input of \code{opts} needs to be column names of variables in \code{data}.
+#' Input of \code{opts} has to be column names of variables in \code{data}.
 #'
 #' \code{none} to specify column name of the \code{none} alternative in the
 #' validation/holdout task.
@@ -52,14 +52,12 @@
 #'
 #' # reach grouped
 #' reach(data = HOT, opts = c(Option_1, Option_2, Option_6), none = None, group = Group)
-#'
 #' }
 
 #'
 #' @export
 
 reach <- function(data, group, none, opts) {
-
   # check for wrong / missing input
   if (base::length(data %>% dplyr::select(., {{ none }})) == 0) {
     stop("Error: argument 'none' is missing!")
[…]

### 2023-08-22 R/ShareOfPref.R

@@ -1,7 +1,7 @@
 #' Share of Preferences of Options included in HOT
 #'
 #' @description
-#' Function to measure the share of preferences of each option in the validation task
+#' Function to measure the share of preferences of each option in a validation/holdout task
 #'
 #' @param data data frame with all relevant variables
 #' @param group optional column name(s) to specify grouping variable(s)
@@ -16,20 +16,20 @@
 #' @importFrom tibble as_tibble
 #'
 #' @details
-#' Share of Preference provides the aggrgated share of each alternative in the
-#' validation/ holdout task as well as the lower and upper confidence interval
+#' Share of Preference provides the aggregated share of each alternative in the
+#' validation/holdout task as well as the lower and upper confidence interval
 #' of each alternative which is calculated according to the following formula
 #' \eqn{mean +/- 1.96 x \frac{sd}{\sqrt(n)}} (Orme, 2020, p. 94).
 #'
-#' \code{data} needs to be a data frame including the alternatives shown in
+#' \code{data} has to be a data frame including the alternatives shown in
 #' the validation/holdout task. Can be created using the \code{createHOT()} function.
 #'
-#' \code{group} optional Grouping variable, if results should be display by different groups.
-#' Needs to be column name of variables in \code{data}.
+#' \code{group} optional grouping variable, if results should be displyed by different groups.
+#' Has to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the simulation
-#' task (also includes the \code{none} alternative).
-#' Input of \code{opts} needs to be column names of variables in \code{data}.
+#' task.
+#' Input of \code{opts} has to be column names of variables in \code{data}.
 #'
 #' @references {
 #'
@@ -62,7 +62,6 @@
 #' @export
 
 shareofpref <- function(data, group, opts) {
-
   if (base::length(data %>% dplyr::select(., {{ opts }})) == 0) {
     stop("Error: argument 'opts' is missing!")
   }
@@ -86,7 +85,7 @@ shareofpref <- function(data, group, opts) {
   ## check whether variable is numeric
[…]

### 2023-08-22 tests/testthat/test-Accuracy.R

@@ -22,7 +22,6 @@ test_that("Error if none is not part of opts", {
 })
 
 test_that("Warning if group contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Group[34] <- NA
@@ -31,7 +30,6 @@ test_that("Warning if group contains NA ", {
 })
 
 test_that("Error if alternatives contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Option_2[34] <- NA
@@ -40,16 +38,14 @@ test_that("Error if alternatives contains NA ", {
 })
 
 test_that("Error if alternatives is not numeric ", {
-
   HOT2 <- HOT
 
-  HOT2$Option_2 <-base::as.character(HOT2$Option_2)
+  HOT2$Option_2 <- base::as.character(HOT2$Option_2)
 
   expect_error(accuracy(data = HOT2, opts = c(Option_1:None), choice = choice, none = None, group = Group))
 })
 
 test_that("Error if choice contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$choice[34] <- NA
@@ -58,7 +54,6 @@ test_that("Error if choice contains NA ", {
 })
 
 test_that("Error if choice is not numeric ", {
-
   HOT2 <- HOT
 
   HOT2$choice <- base::as.character(HOT2$choice)
@@ -107,7 +102,7 @@ test_that("group output equals group input - character input ", {
 test_that("group output equals group input - labelled input ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                     labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_true(labelled::is.labelled(accuracy(data = HOT, opts = c(Option_1:None), choice = choice, none = None, group = Group2)[[1]]))
 })
@@ -115,7 +110,7 @@ test_that("group output equals group input - labelled input ", {
 test_that("group output equals group input - multiple grouping variables ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                                   labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_equal(utils::str(accuracy(data = HOT, opts = c(Option_1:None), choice = choice, none = None, group = c(Group, Group2))[[1]]), utils::str(HOT$Group))
[…]

### 2023-08-22 tests/testthat/test-F1.R

@@ -22,7 +22,6 @@ test_that("Error if none is not part of opts", {
 })
 
 test_that("Warning if group contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Group[34] <- NA
@@ -31,7 +30,6 @@ test_that("Warning if group contains NA ", {
 })
 
 test_that("Error if alternatives contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Option_2[34] <- NA
@@ -40,16 +38,14 @@ test_that("Error if alternatives contains NA ", {
 })
 
 test_that("Error if alternatives is not numeric ", {
-
   HOT2 <- HOT
 
-  HOT2$Option_2 <-base::as.character(HOT2$Option_2)
+  HOT2$Option_2 <- base::as.character(HOT2$Option_2)
 
   expect_error(f1(data = HOT2, opts = c(Option_1:None), choice = choice, none = None, group = Group))
 })
 
 test_that("Error if choice contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$choice[34] <- NA
@@ -58,7 +54,6 @@ test_that("Error if choice contains NA ", {
 })
 
 test_that("Error if choice is not numeric ", {
-
   HOT2 <- HOT
 
   HOT2$choice <- base::as.character(HOT2$choice)
@@ -107,7 +102,7 @@ test_that("group output equals group input - character input ", {
 test_that("group output equals group input - labelled input ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                                   labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_true(labelled::is.labelled(f1(data = HOT, opts = c(Option_1:None), choice = choice, none = None, group = Group2)[[1]]))
 })
@@ -115,7 +110,7 @@ test_that("group output equals group input - labelled input ", {
 test_that("group output equals group input - multiple grouping variables ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                                   labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_equal(utils::str(f1(data = HOT, opts = c(Option_1:None), choice = choice, none = None, group = c(Group, Group2))[[1]]), utils::str(HOT$Group))
[…]

### 2023-08-22 tests/testthat/test-Reach.R

@@ -18,7 +18,6 @@ test_that("Error if none is part of opts", {
 })
 
 test_that("Warning if group contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Group[34] <- NA
@@ -27,7 +26,6 @@ test_that("Warning if group contains NA ", {
 })
 
 test_that("Error if alternatives contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$Option_2[34] <- NA
@@ -36,17 +34,15 @@ test_that("Error if alternatives contains NA ", {
 })
 
 test_that("Error if alternatives is not numeric ", {
-
   HOT2 <- HOT
 
-  HOT2$Option_2 <-base::as.character(HOT2$Option_2)
+  HOT2$Option_2 <- base::as.character(HOT2$Option_2)
 
   expect_error(reach(data = HOT2, opts = c(Option_1, Option_2, Option_6), none = None, group = Group))
 })
 
 
 test_that("Error if none contains NA ", {
-
   HOT2 <- HOT
 
   HOT2$None[34] <- NA
@@ -55,7 +51,6 @@ test_that("Error if none contains NA ", {
 })
 
 test_that("Error if none is not numeric ", {
-
   HOT2 <- HOT
 
   HOT2$None <- base::as.character(HOT2$None)
@@ -105,7 +100,7 @@ test_that("group output equals group input - character input ", {
 test_that("group output equals group input - labelled input ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                                   labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_true(labelled::is.labelled(reach(data = HOT, opts = c(Option_1, Option_2, Option_6), none = None, group = Group2)[[1]]))
 })
@@ -113,7 +108,7 @@ test_that("group output equals group input - labelled input ", {
 test_that("group output equals group input - multiple grouping variables ", {
   HOT$Group2 <- c(1:2)
   HOT$Group2 <- labelled::labelled(HOT$Group2,
-                                   labels = c("Group 1" = 1, "Group 2" = 2)
+    labels = c("Group 1" = 1, "Group 2" = 2)
   )
   expect_equal(utils::str(reach(data = HOT, opts = c(Option_1, Option_2, Option_6), none = None, group = c(Group, Group2))[[1]]), utils::str(HOT$Group))
[…]

### 2023-08-23 README.Rmd
update_230823_02

@@
 make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
-and can also predict outside task that were not included in estimating
+and can also predict outside tasks that were not included in estimating
 your utility scores. Although commercial studies often do not include a
-validation/ holdout task (Yang et al., 2018), it is highly recommended to do so
-(Orme, 2015; Rao, 2014). This validation/ holdout task does not only
+validation/holdout task (Yang et al., 2018), it is highly recommended to do so
+(Orme, 2015; Rao, 2014). This validation/holdout task does not only
 help to check whether everything went right during data collection but
@@
 holdout task is automatically implemented. If you conduct a MaxDiff or
-ACBC study these have to be programmed by yourself.
+ACBC study, you have to program these on your own.
 
@@
 <code>validateHOT</code> and test how good your model predicts choices
-in the validation/ holdout task. Herefore, you only have to insert your
+in the validation/holdout task. Herefore, you only have to read in your
 raw utility scores as well as the actual choice of your validation/
-holdout task. You can use the <code>merge()</code> provided by
+holdout task. You can use the <code>merge()</code> provided by the
 <code>base</code> package (R Core Team, 2023). Afterward, you can read in your data
-file and enjoy <code>validateHOT</code>.
+file and enjoy <code>validateHOT</code>. We provide a tutorial a short tutorial in the vignette.
 
@@
 This function creates the total utilities for each alternative in the
-validation/ holdout task and also in the simulation method, respectively.
+validation/holdout task and also in the simulation method, respectively.
 Rao (2014, p. 82) mentions the additive utility model stating that the
@@
 <li><code>hitrate</code>: creates the Hit Rate (correctly predicted
-choices) of your validation task. The output will contain the chance
-level in your validation task ($\frac{1}{alternatives}$) in percentage.
-The number of correctly predicted participants' choices as well as the
-percentage of how many choices were correctly predicted. If you specify
-an optional <code>group</code> argument the output is split by
-groups.</li>
+choices) of your validation task. The output will contain 
+the percentage of how many choices were correctly predicted, 
+the chance level in your validation task ($\frac{1}{alternatives}$) in percentage,
+the number of correctly predicted participants' choices as well as the number of observations. 
+</li>
 
-<li><code>kl</code>: Kullback-Leibler-Divergence which measures the
+<li><code>kl</code>: Kullback-Leibler-Divergence measures the
 divergence between the actual choice distribution and the predicted
@@
 an optional <code>group</code> argument the output is split by
-groups. Currently, you can choose between \eqn{log{_2}} and \eqn{log} as logarithm base.</li>
+groups. Currently, you can choose between \eqn{log} and \eqn{log{_2}} as logarithm base.
+The default is set to \eqn{log}.</li>
 
-<li><code>mae</code>: average absolute error, i.e., deviation between
-predicted and stated choice share. If you specify an optional
-<code>group</code> argument the output is split by groups.</li>
+<li><code>mae</code>: mean absolute error, i.e., deviation between
+predicted and stated choice share. </li>
 
-<li><code>medae</code>: since the averaged absolute error can be highly
-influenced by the If you specify an optional <code>group</code> argument
-the output is split by groups.</li>
+<li><code>medae</code>: median absolute error, which is less affected
+by outliers compared to the mean absolute error.</li>
 
 <li><code>mhp</code>: averaged hit probability of participant's actual
-choice in the validation/ holdout task. If you specify an optional
-<code>group</code> argument the output is split by groups.</li>
+choice in the validation/holdout task.</li>
 
-<li><code>rmse</code>: provides the root-mean-squared error of deviation
-between predicted and stated choice share. If you specify an optional
-<code>group</code> argument the output is split by groups.</li>
+<li><code>rmse</code>: provides the root-mean-square error of deviation
+between predicted and stated choice share.</li>
 
 </ul>
+
+All functions can be extended with the `group` argument to get output by group.
 
@@
 matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
-currently have to have a **none** option in your data. We currently
+currently have to include a **none** alternative in your validation/holdout task. We currently
 predict, e.g., whether a buy or no-buy was correctly predicted.
@@
 <code>TN</code> for true negatives, and <code>FN</code> for false
-negatives.
+negatives (Burger, 2018). 
+To translate this to the `validateHOT` logic, imagine you have a validation/holdout task
+with 5 alternatives plus the alternative not to buy any of those chosen. `validateHOT` now measures
+whether or not a buy (participant opts for one of the 5 alternatives) or a no-buy (participant opts
+for the no-buy alternative), respectively, is correctly predicted.
 
@@
 
-<li><code>accuracy</code>: defined as
-$\frac{TP + TN}{TP + FP + TN + FN}$. If you specify an optional
-<code>group</code> argument the output is split by groups.</li>
+<li><code>accuracy</code>: calculates the number of correctly predicted choices (buy or no-buy);
+$\frac{TP + TN}{TP + TN + FP + FN}$ (Burger, 2018). 
+</li>
 
@@
 $\frac{2 * precision * recall}{precision + recall}$ or stated
-differently by Burger (2018) $\frac{2TP}{2TP + FP + FN}$. If you
-specify an optional <code>group</code> argument the output is split by
-groups.</li>
+differently by Burger (2018) $\frac{2TP}{2TP + FP + FN}$.</li>
 
-<li><code>precision</code>: defined as $\frac{TP}{TP + FP}$. If you
-specify an optional <code>group</code> argument the output is split by
-groups.</li>
+<li><code>precision</code>: defined as $\frac{TP}{TP + FP}$ (Burger, 2018).</li>
 
-<li><code>recall</code>: defined as $\frac{TP}{TP + FN}$. If you specify
-an optional <code>group</code> argument the output is split by
-groups.</li>
+<li><code>recall</code>: defined as $\frac{TP}{TP + FN}$ (Burger, 2018).</li>
 
-<li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$. If you
-specify an optional <code>group</code> argument the output is split by
-groups.</li>
+<li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$ (Burger, 2018).</li>
 
 </ul>
+
+Again, all functions can be extended with the `group` argument to get output by group.
 
@@
 will choose from your in the function determined potential assortment.
-Again, you have to define a `none` alternative. `freqassort` uses the *threshold* approach,
+Again, you have to define a `none` alternative, because `freqassort` uses the *threshold* approach,
 meaning if the utility of one product is above the utility of `none`,
-it is marked as potential purchase option. If you specify an optional
-<code>group</code> argument the output is split by groups.</li>
+it is marked as potential purchase option.</li>
 
@@
 <li><code>shareofpref</code>: provides you the aggregated share of
-preference, including the lower and upper confidence interval, which is
-calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$. If
-you specify an optional <code>group</code> argument the output is split
-by groups and provided in a list element.</li>
+preference, including the standard error, as well as the lower and upper confidence interval, which is
+calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>
 
@@
 We are teaching a preference measurement seminar for students. Often
-these students did not have experience with *R* before or only sparsely.
-We teach them to also validate their results and wanted to give them an
-easy way on how to do this in *R*. Of course, there are other great
-packages which are faster in running (i.e., Hamner & Frasco, 2018), however,
-these packages need some more data wrangling in order to use the
-appropriate functions, which might be a burden or barrier for the one or
+these students did not have any prior experience (or only sparsely) with *R*.
+One of the chapters in this class is about model validating the results obtained and we teach this,
+of course, in *R*.
+Of course, there are other great packages which are faster in running (i.e., `Metrics` by Hamner & Frasco, 2018), 
+however, these packages need some more data wrangling in order to use the
+appropriate functions, which might be a burden or barrier for one or
 the other.
 
-Moreover, as Yang et al. (2018) also report, often commercial studies do not use
-any validation task. Some market research companies (as far as we have
-realized) are not that familiar with *R* yet. Since these functions are
-not always implemented in other softwares, this might be one reason why
+Moreover, as Yang et al. (2018) report, commercial studies often do not use
+any validation task. Again, the missing experience in *R* could be one explanation. 
+Since these functions are not always implemented in other softwares, this might be one reason why
 they do not include one simply because they do not know how to use it
-correctly. Having a package to evaluate the validation/ holdout task can
-also be beneficial for those companies.
+correctly. Having a package to evaluate the validation/holdout task can
+also be beneficial from this perspective.
 
@@
 However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package (R Core Team, 2023).
-For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
+For example, if you want to find out the column index of <code>ID</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
 
@@
 HOT <- createHOT(
-  data = CBC,
-  id = 1,
-  None = 21,
-  prod = 3,
-  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
-  coding = c(0, 0, 0),
-  method = "CBC",
-  choice = 22
+  data = CBC, # data frame
+  id = 1, # column index of the id
+  None = 21, # column index of none alternative
+  prod = 3, # number of alternatives in validation task (excluding none)
+  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each alternative
+  coding = c(0, 0, 0), # how the attributes were coded
+  method = "CBC", # method
+  choice = 22 # column index of choice
 )
@@
 
-Let us take a glimpse at the output, which shows the total raw utilities for each of the function included in the validation/ holdout task.
+Let us take a glimpse at the output, which shows the total raw utilities for each of the alternatives 
+included in the validation/holdout task.
 
@@
 
-In the next step, we would like to see how well our model (from which we took the raw utilities) predict the choices in the validation/ holdout task.
-First, we will test the <code>hitrate()</code> function.
-We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember we have three alternatives + the *no-buy* alternative), and finally the choice.
-We can see that the hitrate of our example is `r round(as.numeric(hitrate(data = HOT, opts = c(2:5), choice = choice)[3, 2]), digits  = 3)`.
+In the next step, we would like to see how well our model (from which we took the raw utilities) predict 
+the actual choices in the validation/holdout task. First, we will test the <code>hitrate()</code> function. 
+We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember 
+we have three alternatives + the *no-buy* alternative), and finally the actual choice.
 
 ```{r}
-hitrate(data = HOT, opts = c(2:5), choice = choice)
+hitrate(
+  data = HOT, # data frame
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice # column name of choice
+)
 ```
@@
 ```{r}
-mae(data = HOT, opts = c(2:5), choice = choice)
+mae(
+  data = HOT, # data frame
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice # column name of choice
+)
 ```
@@
 ```{r}
-accuracy(data = HOT, opts = c(2:5), choice = choice, none = None)
+accuracy(
+  data = HOT, # data frame
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice, # column name of choice
+  none = None # column name of none alternative
+)
 ```
@@
 ```{r}
-reach(data = HOT, opts = c(Option_1:Option_3), none = None)
+reach(
+  data = HOT, # data frame
+  opts = c(Option_1:Option_3), # products that should be considered
+  none = None # column name of none alternative
+)
 ```
@@
 
-In a second example, we again use a *CBC*, however, this time we show how to use <code>validateHOT</code> if one of the variables are linear coded. All other examples are provided in the Vignette.
+In a second example, we again use a *CBC*, however, this time we show how to use <code>validateHOT</code> if one of the variables are linear coded.
+All other examples are provided in the accompanied vignette.
 
@@
 
-Next, we create the validation/ holdout task to evaluate it in the next step.
-We use a validation/ holdout task with three alternatives plus the *no-buy* option, just as we did in the previous example.
-The only difference to the previous example is that we coded the third attribute (<code>Att3_Lin</code>) as linear.
+Next, we create the validation/holdout task to evaluate it in the next step.
+We use a validation/holdout task with three alternatives plus the *no-buy* alternative, just as we did in the previous example.
+The only difference to the previous example is that for our model estimation, the third attribute (<code>Att3_Lin</code>) was coded as linear.
 
@@
 To interpolate the value, we have to provide <code>validateHOT</code> the <code>interpolate.levels</code>.
-These **need** to be the same as provided to, e.g., Sawtooth as levels.
+These **need** to be the same as provided to Sawtooth as levels.
 Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of <code>interpolate.levels</code>.
 In our case, we had 7 levels that range from 10 to 70.
-The value we want to interpolate for the second alternative is 40, which of course lies within 10 and 70.
 
@@
 Again, we are running a *CBC* specified by the <code>method</code> argument.
-This time, we would like to keep some of the variables to the data frame, which we specify in <code>varskeep</code>.
+This time, we would like to keep some of the variables in the data frame, which we specify in <code>varskeep</code>.
 We only keep one further variable, however, you can specify as many as you want.
 This could be relevant if you would like to display results per group.
-Finally, we just tell <code>validateHOT</code> the column index of the final choice (<code>choice</code>) and we are good to go.
+Finally, we just tell <code>validateHOT</code> the column index of the final choice (<code>choice</code>) and we are all set.
 
@@
 CBC <- createHOT(
-  data = CBC_lin,
-  id = 1,
-  None = 15,
-  prod = 3,
-  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)),
-  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
-  lin.p = 14,
-  coding = c(0, 0, 1),
-  method = "CBC",
-  varskeep = 17,
-  choice = 16
+  data = CBC_lin, # data frame
+  id = 1, # column index of the id
+  None = 15, # column index of none alternative
+  prod = 3, # number of alternatives in validation task (excluding none)
+  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each alternative (for linear coded we specify value to be interpolated)
+  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
+  lin.p = 14, # column index of the linear coded variable
+  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
+  method = "CBC", # method
+  varskeep = 17, # column index of variables that should be kept in the dataframe
+  choice = 16 # column index of choice
 )
@@
 ```{r}
-hitrate(data = CBC, opts = c(Option_1:None), choice = choice, group = Group)
+hitrate(
+  data = CBC, # data frame
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice, # column name of choice
+  group = Group # column name of Grouping variable
+)
 ```
 
-In this case, the Grouping variable is just an integer.
-However, the output is different if it is a factor or if it is labelled data.
-To proof this we just quickly change <code>group</code> in a factor by using the <code>factor()</code> function provided by R Core Team (2023).
+In this case, the group assignment is stored in form of integers.
+However, the output is the same if it is a factor or if it is labelled data.
+To proof this we just quickly change <code>group</code> into a factor by using the <code>factor()</code> function provided by R Core Team (2023).
 
 ```{r}
-CBC$Group <- base::factor(CBC$Group,
+CBC$Group <- base::factor(
+  CBC$Group,
   levels = c(1:3),
@@
 ```{r}
-mhp(data = CBC, opts = c(Option_1:None), choice = choice, group = Group)
+mhp(
+  data = CBC, # data frame
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice, # column name of choice
+  group = Group # column name of Grouping variable
+)
 ```
@@
 
+Orme, B. K. (2020). <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.
+
 R Core Team. 2023. “R: A Language and Environment for Statistical Computing.” [https://www.R-project.org/](https://www.R-project.org/).

### 2023-08-23 R/Reach.R

@@ -121,10 +121,10 @@ reach <- function(data, group, none, opts) {
     dplyr::select(., {{ opts }}, {{ none }}, {{ group }}) %>% # select relevant variables
     dplyr::mutate(
       thres = {{ none }}, # store utility of threshold
-      dplyr::across({{ opts }}, ~ base::ifelse(.x > thres, 1, 0))
+      dplyr::across({{ opts }}, ~ base::ifelse(.x > thres, 1, 0)) # if value of alternatves above threshold --> reached
     ) %>%
     dplyr::rowwise() %>%
-    dplyr::mutate(reach = base::ifelse(sum({{ opts }}) > 0, 1, 0)) %>% # if sum of alternatves is above 0 --> reached
+    dplyr::mutate(reach = base::ifelse(sum({{ opts }}) > 0, 1, 0)) %>% # if sum of alternatves is at least once above 0 --> reached
     dplyr::group_by(dplyr::pick({{ group }})) %>%
     dplyr::summarise(reach = base::mean(reach) * 100))
 }

### 2023-08-29 README.Rmd
fin 230829

@@
 
-<li><code>freqassort</code>: Inspired by the former <a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>freqassort</code>
+<li><code>turf</code>: **T**(otal) **U**(nduplicated) **R**(each) and **F**(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
+29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option).
+<code>turf</code> currently provides both the threshold approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
+112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
+111).
+
+<li><code>freqassort</code>: Similar to <code>turf</code>, <code>freqassort</code>
 will give you the averaged frequency, how many products the participants
@@
 meaning if the utility of one product is above the utility of `none`,
-it is marked as potential purchase option.</li>
+it is marked as potential purchase option. While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>freqassort</code>.</li>
 
-<li><code>reach</code>: Inspired by the former
-<a href="https://github.com/cran/turfR" target="_blank">turfR</a> package, <code>reach</code> will
+<li><code>reach</code>: Similar to <code>turf</code>,, <code>reach</code> will
 give you the averaged percentage of how many participants you can reach
 (at least one of the products resemble a purchase option) with your in the function determined
-potential assortment. `reach` also uses the *threshold* approach (see above).</li>
+potential assortment.
+`reach` also uses the *threshold* approach (see above).
+While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>reach</code></li>
 
@@
 ```
+
 Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers.
@@
 
+Chrzan, K., & Orme, B. K. (2019). <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
+
 Ding, Min, John R.
@@
 Hamner, Ben, and Michael Frasco. 2018. “Metrics: Evaluation Metrics for Machine Learning.” [https://CRAN.R-project.org/package=Metrics](https://CRAN.R-project.org/package=Metrics).
+
+Miaoulis, G., Parsons, H., & Free, V. (1990). Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
 

### 2023-08-30 README.Rmd
fin 230829 v_02
230830 new stuff

@@
 
-<li><code>turf</code>: **T**(otal) **U**(nduplicated) **R**(each) and **F**(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
+<li><code>turf</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
 29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option).
@@
 112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
-111).
+111).</li>
 
@@
 will choose from your in the function determined potential assortment. 
-Again, you have to define a `none` alternative, because `freqassort` uses the *threshold* approach,
-meaning if the utility of one product is above the utility of `none`,
-it is marked as potential purchase option. While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>freqassort</code>.</li>
+Again, you have to define a <code>none</code> alternative, because <code>freqassort</code> uses the <i>threshold</i> approach,
+meaning if the utility of one product is above the utility of <code>none</code>,
+it is marked as potential purchase option.
+While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>freqassort</code>.</li>
 
-<li><code>reach</code>: Similar to <code>turf</code>,, <code>reach</code> will
+<li><code>reach</code>: Similar to <code>turf</code>, <code>reach</code> will
 give you the averaged percentage of how many participants you can reach
@@
 potential assortment.
-`reach` also uses the *threshold* approach (see above).
-While `turf` calculates the reach and frequency for **all** combinations, you specify the combination you are interested in <code>reach</code></li>
+<code>reach</code> also uses the <i>threshold</i> approach (see above).
+While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach</code></li>
 

### 2023-08-30 R/MedAE.R

@@ -51,15 +51,19 @@
 #' )
 #'
 #' # medae ungrouped
-#' medae(data = HOT,
-#'       opts = c(Option_1:None),
-#'       choice = choice)
+#' medae(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice
+#' )
 #'
 #' # medae grouped
-#' medae(data = HOT,
-#'       opts = c(Option_1:None),
-#'       choice = choice,
-#'       group = Group)
+#' medae(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice,
+#'   group = Group
+#' )
 #' }
 #'
 #' @export

### 2023-08-30 R/Reach.R

@@ -49,15 +49,19 @@
 #' )
 #'
 #' # reach ungrouped
-#' reach(data = HOT,
-#'       opts = c(Option_1, Option_2, Option_6),
-#'       none = None)
+#' reach(
+#'   data = HOT,
+#'   opts = c(Option_1, Option_2, Option_6),
+#'   none = None
+#' )
 #'
 #' # reach grouped
-#' reach(data = HOT,
-#'       opts = c(Option_1, Option_2, Option_6),
-#'       none = None,
-#'       group = Group)
+#' reach(
+#'   data = HOT,
+#'   opts = c(Option_1, Option_2, Option_6),
+#'   none = None,
+#'   group = Group
+#' )
 #' }
 #'
 #' @export

### 2023-08-30 R/ShareOfPref.R

@@ -53,13 +53,17 @@
 #' )
 #'
 #' # shareofpref ungrouped
-#' shareofpref(data = HOT,
-#'             opts = c(Option_1:None))
+#' shareofpref(
+#'   data = HOT,
+#'   opts = c(Option_1:None)
+#' )
 #'
 #' # shareofpref grouped
-#' shareofpref(data = HOT,
-#'             opts = c(Option_1:None),
-#'             group = Group)
+#' shareofpref(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   group = Group
+#' )
 #' }
 #'
 #' @export

### 2023-08-30 R/Specificity.R

@@ -69,17 +69,21 @@
 #' )
 #'
 #' # specificity ungrouped
-#' specificity(data = HOT,
-#'             opts = c(Option_1:None),
-#'             choice = choice,
-#'             none = None)
+#' specificity(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice,
+#'   none = None
+#' )
 #'
 #' # specificity by group
-#' specificity(data = HOT,
-#'             opts = c(Option_1:None),
-#'             choice = choice,
-#'             none = None,
-#'             group = Group)
+#' specificity(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice,
+#'   none = None,
+#'   group = Group
+#' )
 #' }
 #'
 #' @export

### 2023-08-30 R/hitrate.R

@@ -50,15 +50,19 @@
 #'   varskeep = 21
 #' )
 #' # hit rate ungrouped
-#' hitrate(data = HOT,
-#'         opts = c(Option_1:None),
-#'         choice = choice)
+#' hitrate(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice
+#' )
 #'
 #' # hit rate grouped
-#' hitrate(data = HOT,
-#'         opts = c(Option_1:None),
-#'         choice = choice,
-#'         group = Group)
+#' hitrate(
+#'   data = HOT,
+#'   opts = c(Option_1:None),
+#'   choice = choice,
+#'   group = Group
+#' )
 #' }
 #'
 #' @export

### 2023-08-30 tests/testthat/test-turf.R

@@ -10,11 +10,11 @@ HOT <- createHOT(
 
 # examples
 test_that("Example 1 should work ", {
-  expect_no_error(turf(data = HOT, opts = c(Option_1:Option_16),  none = None, size = 3, approach = "thres"))
+  expect_no_error(turf(data = HOT, opts = c(Option_1:Option_16), none = None, size = 3, approach = "thres"))
 })
 
 test_that("Example 2 should work ", {
-  expect_no_error(turf(data = HOT, opts = c(Option_1:Option_16),  none = None, size = 4, fixed = c("Option_1", "Option_5"), approach = "thres"))
+  expect_no_error(turf(data = HOT, opts = c(Option_1:Option_16), none = None, size = 4, fixed = c("Option_1", "Option_5"), approach = "thres"))
 })
 
 
@@ -76,7 +76,7 @@ test_that("Error if opts contains NA ", {
 
   HOT2$Option_2[34] <- NA
 
-  expect_error(turf(data = HOT2, opts = c(Option_1:Option_16),  none = None, size = 3, approach = "thres"))
+  expect_error(turf(data = HOT2, opts = c(Option_1:Option_16), none = None, size = 3, approach = "thres"))
 })
 
 
@@ -85,28 +85,30 @@ test_that("Error if opts is not numeric ", {
 
   HOT2$Option_2 <- base::as.character(HOT2$Option_2)
 
-  expect_error(turf(data = HOT2, opts = c(Option_1:Option_16),  none = None, size = 3, approach = "thres"))
+  expect_error(turf(data = HOT2, opts = c(Option_1:Option_16), none = None, size = 3, approach = "thres"))
 })
 
 
 # Output
 test_that("Data Frame as output ", {
-  expect_true(is.data.frame(turf(data = HOT, opts = c(Option_1:Option_16),  none = None, size = 3, approach = "thres")))
+  expect_true(is.data.frame(turf(data = HOT, opts = c(Option_1:Option_16), none = None, size = 3, approach = "thres")))
 })
 
 test_that("length of output should equal number of possible combinations ", {
-  expect_equal(base::nrow(turf(data = HOT, opts = c(Option_1:Option_16),  none = None, size = 3, approach = "thres")),
-               base::nrow(base::as.data.frame(base::t(utils::combn(base::length(HOT %>% select(Option_1:Option_16)), 3)))))
+  expect_equal(
[…]

### 2023-08-30 tests/testthat/test-createHOT.R
updated tests

@@ -996,3 +996,56 @@ test_that("Make sure varskeep is working ", {
     varskeep = 41
   ))
 })
+
+
+# Add missing tests
+test_that("piece.p only takes numeric values ", {
+  prod1 <- c(5, 5, 12, 14, 18, 22, 29, 31, 15.99)
+  prod2 <- c(6, 4, 12, 14, 20, 24, 28, 31, 12.99)
+  prod3 <- c(8, 6, 13, 16, 20, 21, 25, 31, 12.99)
+  prod4 <- c(7, 5, 11, 15, 19, 21, 25, 30, 9.99)
+  prod5 <- c(4, 9, 10, 14, 20, 24, 25, 31, 7.99)
+  prod6 <- c(5, 8, 11, 14, 20, 24, 26, 30, 9.99)
+
+  expect_error(createHOT(
+    data = ACBC_interpolate,
+    id = 1,
+    None = 39,
+    prod = 6,
+    prod.levels = list(prod1, prod2, prod3, prod4, prod5, prod6),
+    interpolate.levels = list(c(3, 5, 8, 10), c(1.99, 6.99, 9.99, 10.99, 12.99, 17.99, 25.99)),
+    piece.p = list(c("36", 37), c(35, 36), c(35, 36), c(33, 34), c(33, 34), c(33, 34)),
+    lin.p = 9,
+    coding = c(0, 1, 0, 0, 0, 0, 0, 0, 2),
+    method = "ACBC",
+    choice = 40,
+    varskeep = 41
+  ))
+})
+
+
+test_that("Variables in piece.p only have to be numeric ", {
+  prod1 <- c(5, 5, 12, 14, 18, 22, 29, 31, 15.99)
+  prod2 <- c(6, 4, 12, 14, 20, 24, 28, 31, 12.99)
+  prod3 <- c(8, 6, 13, 16, 20, 21, 25, 31, 12.99)
+  prod4 <- c(7, 5, 11, 15, 19, 21, 25, 30, 9.99)
+  prod5 <- c(4, 9, 10, 14, 20, 24, 25, 31, 7.99)
+  prod6 <- c(5, 8, 11, 14, 20, 24, 26, 30, 9.99)
+
+  ACBC_interpolate[3, 36] <- as.character(ACBC_interpolate[3, 36])
+
+  expect_error(createHOT(
+    data = ACBC_interpolate,
+    id = 1,
+    None = 39,
+    prod = 6,
[…]

### 2023-09-25 R/Accuracy.R
updated format 230925

@@ -1,8 +1,9 @@
 #' Accuracy
 #'
 #' @description accuracy is one of the 5 metrics of the confusion matrix
-#' and is defined as number of correctly predicted participants divided by the total number of predictions.
-#' See, for example, Burger (2018): \eqn{\frac{TP + TN}{TP + FP + TN + FN}}, where TP =
+#' and is defined as number of correctly predicted participants divided by
+#' the total number of predictions. See, for example, Burger (2018):
+#' \eqn{\frac{TP + TN}{TP + FP + TN + FN}}, where TP =
 #' True Positives, TN = True Negatives, FP = False Positives, and FN =
 #' False Negatives.
 #'
@@ -15,23 +16,26 @@
 #' @param none column name of none alternative
 #'
 #' @details
-#' The current logic of \code{"accuracy"} is to determine whether a binary coded is correctly predicted by the model.
-#' To use the function a \code{"none"} alternative has to be included in the validation/holdout task.
+#' The current logic of \code{"accuracy"} is to determine whether a binary coded
+#' is correctly predicted by the model. To use the function a \code{"none"}
+#' alternative has to be included in the validation/holdout task.
 #' One potential usage is, for example, whether a buy or a no-buy condition
 #' was predicted correctly. For example, assume you have three alternatives plus
 #' a \code{"none"} alternative and you want to check whether a buy or no-buy was
-#' correctly predicted. This function can be helpful when you test, for example, if
-#' your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#' correctly predicted. This function can be helpful when you test, for example,
+#' if your model significantly overestimates or underestimates, for
+#' example, a purchase likelihood.
 #'
 #'
 #' \code{data} has to be a data frame including the alternatives shown in
-#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#' the validation/holdout task. Can be created using the \code{createHOT()}
+#' function.
 #'
-#' \code{group} optional grouping variable(s), if results should be displayed by different groups.
-#' Has to be column name(s) of variables in \code{data}.
+#' \code{group} optional grouping variable(s), if results should be displayed by
+#' different groups. Has to be column name(s) of variables in \code{data}.
 #'
-#' \code{opts} is needed to specify the different alternatives in the validation/holdout
[…]

### 2023-09-25 R/Precision.R

@@ -13,23 +13,26 @@
 #' @param none column name of none alternative
 #'
 #' @details
-#' The current logic of \code{"precision"} is to determine whether a binary coded is correctly predicted by the model.
-#' To use the function a \code{"none"} alternative has to be included in the validation/holdout task.
-#' One potential usage is, for example, whether a buy or a no-buy condition
-#' was predicted correctly. For example, you have three alternatives plus
-#' a \code{"none"} alternative and you want to check whether a buy or no-buy was
-#' correctly predicted. This function can be helpful when you test, for example, if
-#' your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#' The current logic of \code{"precision"} is to determine whether a binary
+#' coded is correctly predicted by the model.
+#' To use the function a \code{"none"} alternative has to be included in the
+#' validation/holdout task. One potential usage is, for example, whether a
+#' buy or a no-buy condition was predicted correctly. For example,
+#' you have three alternatives plus a \code{"none"} alternative and you
+#' want to check whether a buy or no-buy was correctly predicted. This function
+#' can be helpful when you test, for example, if your model significantly
+#' overestimates or underestimates, for example, a purchase likelihood.
 #'
 #' \code{data} has to be a data frame including the alternatives shown in
-#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#' the validation/holdout task. Can be created using the \code{createHOT()}
+#' function.
 #'
-#' \code{group} optional Grouping variable, if results should be display by different conditions.
-#' Has to be column name of variables in \code{data}.
+#' \code{group} optional Grouping variable, if results should be display by
+#' different conditions. Has to be column name of variables in \code{data}.
 #'
-#' \code{opts} is needed to specify the different alternatives in the validation/holdout
-#' task.
-#' Input of \code{opts} has to be column names of variables in \code{data}.
+#' \code{opts} is needed to specify the different alternatives in the
+#' validation/holdout task. Input of \code{opts} has to be column names of
+#' variables in \code{data}.
 #'
 #' \code{choice} to specify column name of actual choice.
 #'
@@ -53,7 +56,8 @@
 #'
 #' @references {
 #'
[…]

### 2023-09-25 R/Recall.R

@@ -13,23 +13,27 @@
 #' @param none column name of none alternative
 #'
 #' @details
-#' The current logic of \code{"recall"} is to determine whether a binary coded is correctly predicted by the model.
-#' To use the function a \code{"none"} alternative has to be included in the validation/holdout task.
+#' The current logic of \code{"recall"} is to determine whether a binary coded
+#' is correctly predicted by the model.
+#' To use the function a \code{"none"} alternative has to be included in the
+#' validation/holdout task.
 #' One potential usage is, for example, whether a buy or a no-buy condition
 #' was predicted correctly. For example, you have three alternatives plus
 #' a \code{"none"} alternative and you want to check whether a buy or no-buy was
-#' correctly predicted. This function can be helpful when you test, for example, if
-#' your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#' correctly predicted. This function can be helpful when you test, for example,
+#' if your model significantly overestimates or underestimates, for
+#' example, a purchase likelihood.
 #'
 #' \code{data} has to be a data frame including the alternatives shown in
-#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#' the validation/holdout task. Can be created using the \code{createHOT()}
+#' function.
 #'
-#' \code{group} optional grouping variable, if results should be displayed by different conditions.
-#' Has to be column name of variables in \code{data}.
+#' \code{group} optional grouping variable, if results should be displayed by
+#' different conditions. Has to be column name of variables in \code{data}.
 #'
-#' \code{opts} is needed to specify the different alternatives in the validation/holdout
-#' task.
-#' Input of \code{opts} has to be column names of variables in \code{data}.
+#' \code{opts} is needed to specify the different alternatives in the
+#' validation/holdout task. Input of \code{opts} has to be column names of
+#' variables in \code{data}.
 #'
 #' \code{choice} to specify column of actual choice.
 #' Input of opts \code{choice} has to be column name of actual choice.
@@ -51,7 +55,8 @@
 #'
 #' @references {
 #'
-#' Burger, S. V. (2018). \emph{Introduction to Machine Learning with R: Rigorous Mathematical Analysis}. O'Reilly.
+#' Burger, S. V. (2018). \emph{Introduction to Machine Learning with R:
[…]

### 2023-09-25 R/Specificity.R

@@ -13,23 +13,26 @@
 #' @param none column name of none alternative
 #'
 #' @details
-#' The current logic of \code{"specificity"} is to determine whether a binary coded is correctly predicted by the model.
-#' To use the function a \code{"none"} alternative has to be included in the validation/holdout task.
-#' One potential usage is, for example, whether a buy or a no-buy condition
-#' was predicted correctly. For example, you have three alternatives plus
-#' a \code{"none"} alternative and you want to check whether a buy or no-buy was
-#' correctly predicted. This function can be helpful when you test, for example, if
-#' your model significantly overestimates or underestimates, for example, a purchase likelihood.
+#' The current logic of \code{"specificity"} is to determine whether a binary
+#' coded is correctly predicted by the model.To use the function
+#' a \code{"none"} alternative has to be included in the validation/holdout
+#' task. One potential usage is, for example, whether a buy or a no-buy
+#' condition was predicted correctly. For example, you have three alternatives
+#' plus a \code{"none"} alternative and you want to check whether a buy or
+#' no-buy was correctly predicted. This function can be helpful when you test,
+#' for example, if your model significantly overestimates or underestimates,
+#' for example, a purchase likelihood.
 #'
 #' \code{data} has to be a data frame including the alternatives shown in
-#' the validation/holdout task. Can be created using the \code{createHOT()} function.
+#' the validation/holdout task. Can be created using the \code{createHOT()}
+#' function.
 #'
-#' \code{group} optional grouping variable, if results should be displayed by different conditions.
-#' Has to be column name of variables in \code{data}.
+#' \code{group} optional grouping variable, if results should be displayed by
+#' different conditions. Has to be column name of variables in \code{data}.
 #'
-#' \code{opts} is needed to specify the different alternatives in the validation/holdout
-#' task.
-#' Input of \code{opts} has to be column names of variables in \code{data}.
+#' \code{opts} is needed to specify the different alternatives in the
+#' validation/holdout task. Input of \code{opts} has to be column names of
+#' variables in \code{data}.
 #'
 #' \code{choice} to specify column of actual choice.
 #' Input of opts \code{choice} has to be column name of actual choice.
@@ -51,7 +54,8 @@
 #'
[…]

### 2023-09-25 R/createHOT.R

@@ -4,77 +4,110 @@
 #'
 #' @param data data frame with all relevant variables.
 #' @param id vector of column index of unique identifier in \code{data}.
-#' @param None optional column index to specify \code{None} alternative in \code{data}.
-#' @param prod number of alternatives in the holdout/validation task (does not count the \code{None} alternative); input has to be numeric
-#' @param prod.levels a list to define the attribute levels of the alternatives (\code{prod})
-#' @param interpolate.levels a list of the levels of the variables that should be interpolated. These have to be the same as provided to Sawtooth Software. Please make sure to provide the whole list. Only has to be specified for the variables that are coded as '1' (linear) or '2' (piecewise)
-#' @param piece.p a list of the column indexes of the lower level and the upper level that should be used for interpolating
+#' @param None optional column index to specify \code{None}
+#' alternative in \code{data}.
+#' @param prod number of alternatives in the holdout/validation task
+#' (does not count the \code{None} alternative); input has to be numeric
+#' @param prod.levels a list to define the attribute levels of the
+#' alternatives (\code{prod})
+#' @param interpolate.levels a list of the levels of the variables that should
+#' be interpolated. These have to be the same as provided to Sawtooth Software.
+#' Please make sure to provide the whole list. Only has to be specified for the
+#' variables that are coded as '1' (linear) or '2' (piecewise)
+#' @param piece.p a list of the column indexes of the lower level and the upper
+#' level that should be used for interpolating
 #' @param lin.p vector of the column indexes of the linear variables
-#' @param coding vector of the coding of each attribute, '0' = part-worth coding, '1' = linear coding, '2' = piecewise coding; please make sure to code linear price of ACBC as piecewise since you have two values to interpolate
-#' @param method specify the \code{method} your study; has to be one of the following three: MaxDiff, CBC, or ACBC
-#' @param varskeep vector of column index(es) of variables that should be kept in the data frame
+#' @param coding vector of the coding of each attribute, '0' = part-worth
+#' coding,'1' = linear coding, '2' = piecewise coding; please make sure to code
+#' linear price of ACBC as piecewise since you have two values to interpolate
+#' @param method specify the \code{method} your study; has to be one of the
[…]

### 2023-09-25 R/freqAssort.R

@@ -1,11 +1,13 @@
-#' Averaged number of times a person is reached by a specific assortment of bundles
+#' Averaged number of times a person is reached by a specific assortment of
+#' bundles
 #'
 #' @description
 #' Frequency function of T(otal) U(nduplicated) R(each) and F(requency)
 #' analysis to measure the average time a consumer
-#' is reached with a specific product bundle assortment. \code{"freqassort"} calculates
-#' the frequency based on the 'threshold' approach, meaning each alternative that exceeds
-#' utility of \code{none} alternative is considered as, for example, purchase option.
+#' is reached with a specific product bundle assortment. \code{"freqassort"}
+#' calculates the frequency based on the 'threshold' approach, meaning
+#' each alternative that exceeds utility of \code{none} alternative is
+#' considered as, for example, purchase option.
 #'
 #' @param data data frame with all relevant variables
 #' @param group optional column name(s) to specify grouping variable(s)
@@ -16,15 +18,17 @@
 #' @details
 #' Frequency calculates the average times a consumer would be reached with the
 #' product assortment you are testing. The current logic of \code{freqassort()}
-#' is that the utility of an alternative has to exceed a threshold. In the case of \code{freqassort()}
+#' is that the utility of an alternative has to exceed a threshold. In the case
+#'  of \code{freqassort()}
 #' this threshold is referred to the \code{none} argument in \code{data}.
 #'
-#' \code{data} has to be a data frame including the alternatives that should be tested
+#' \code{data} has to be a data frame including the alternatives that should
+#' be tested
 #'
-#' \code{group} optional grouping variable, if results should be displayed by different conditions.
+#' \code{group} optional grouping variable, if results should be displayed
+#' by different conditions.
 #' Has to be column name of variables in \code{data}.
 #'
-#' \code{opts} is needed to specify the different alternatives in the
 #' product assortment that should be considered.
 #' Input of \code{opts} has to be column names of variables in \code{data}.
 #'
@@ -32,7 +36,8 @@
 #' validation/holdout task.
 #'
 #'
-#' @importFrom dplyr select mutate across rowwise c_across pick summarise group_by ungroup
+#' @importFrom dplyr select mutate across rowwise c_across pick summarise
+#' group_by ungroup
 #' @importFrom magrittr "%>%"
[…]

### 2023-09-25 R/turf.R

@@ -1,20 +1,25 @@
 #' Total Unduplicated Reach and Frequency
 #' @description
 #' T(otal) U(nduplicated) R(each) and F(requency) is
-#' a "product line extension model" (Miaoulis et al., 1990, p. 29). For each possible combinations,
-#' it looks for the reach and frequency of this combination. Participants are reached,
-#' if at least one of the alternatives in a combination has a higher utility than \code{none}. On the contrary,
-#' frequency calculates the averaged number of alternatives that have a higher utility than \code{none}.
+#' a "product line extension model" (Miaoulis et al., 1990, p. 29). For each
+#' possible combinations, it looks for the reach and frequency of this
+#' combination. Participants are reached, if at least one of the alternatives
+#' in a combination has a higher utility than \code{none}. On the contrary,
+#' frequency calculates the averaged number of alternatives that have a
+#' higher utility than \code{none}.
 #'
 #'
 #' @param data data frame with all relevant variables
 #' @param opts column names of the alternatives included in the assortment
 #' @param none column name of none / threshold alternative
 #' @param size numeric vector to determine size of the assortment
-#' @param fixed optional vector to determine alternatives that have to be included in the assortment
-#' @param approach character whether to run First Choice approach ('fc') or Threshold approach ('thres')
+#' @param fixed optional vector to determine alternatives that have to be
+#' included in the assortment
+#' @param approach character whether to run First Choice approach ('fc') or
+#' Threshold approach ('thres')
 #'
-#' \code{data} has to be a data frame including the alternatives that should be tested
+#' \code{data} has to be a data frame including the alternatives that should be
+#' tested
 #'
 #' \code{opts} is needed to specify the different alternatives in the
 #' product assortment that should be considered.
@@ -25,25 +30,33 @@
 #'
 #' \code{size} has to be a whole number determining the size of the assortment.
 #'
-#' \code{fixed} has to be a vector of variables that are fixed in the assortment, i.e., they
-#' have to be part of the assortment
+#' \code{fixed} has to be a vector of variables that are fixed in the
+#' assortment, i.e., they have to be part of the assortment
 #'
[…]

### 2023-10-02 README.Rmd
updated tests
worfklow added 230925
updated rmd - 231002

@@
 
+[![R-CMD-check](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml)
 <!-- badges: end -->
@@
 holdout task is automatically implemented. If you conduct a MaxDiff or
-ACBC study, you have to program these on your own.
+ACBC study, you have to program these on your own. Since the start of
 
@@
 We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember 
-we have three alternatives + the *no-buy* alternative), and finally the actual choice.
+there are three alternatives + the *no-buy* alternative), and finally the actual choice.
 

### 2023-10-06 README.Rmd
badges included - 231006

@@
 [![R-CMD-check](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml)
+
+[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
 <!-- badges: end -->
@@
 task (also known as holdout task). A validation task is essential to
-make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
+make sure that your collected data of a MaxDiff, CBC, or ACBC is valid
 and can also predict outside tasks that were not included in estimating
@@
 holdout task is automatically implemented. If you conduct a MaxDiff or
-ACBC study, you have to program these on your own. Since the start of
+ACBC study, you have to program these on your own.
+
+> Currently <code>validateHOT</code> only works with data from Sawtooth Software 
+due to the coding of price.
 

### 2023-10-09 README.Rmd
added first choice rule and changed shareofpref to marksim

@@
 
-<li><code>shareofpref</code>: provides you the aggregated share of
-preference, including the standard error, as well as the lower and upper confidence interval, which is
+<li><code>marksim</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
 calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>

### 2023-10-09 R/ShareOfPref.R

@@ -1,145 +1,0 @@
-#' Share of Preferences of Options included in HOT
-#'
-#' @description
-#' Function to measure the share of preferences of each option in a
-#' validation/holdout task
-#'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"shareofpref"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#'
-#' @return a tibble
-#' @importFrom dplyr select pick mutate across ungroup group_by summarise count
-#' @importFrom magrittr "%>%"
-#' @importFrom stats sd
-#' @importFrom tibble as_tibble
-#'
-#' @details
-#' Share of Preference provides the aggregated share of each alternative in the
-#' validation/holdout task as well as the lower and upper confidence interval
-#' of each alternative which is calculated according to the following formula
-#' \eqn{mean +/- 1.96 x \frac{sd}{\sqrt(n)}} (Orme, 2020, p. 94).
-#'
-#' \code{data} has to be a data frame including the alternatives shown in
-#' the validation/holdout task. Can be created using the \code{createHOT()}
-#' function.
-#'
-#' \code{group} optional grouping variable, if results should be displayed by
-#' different groups. Has to be column name of variables in \code{data}.
-#'
-#' \code{opts} is needed to specify the different alternatives in the simulation
-#' task.
-#' Input of \code{opts} has to be column names of variables in \code{data}.
-#'
-#' @references {
-#'
-#' Orme, B. K. (2020). \emph{Getting Started with Conjoint Analysis:
-#' Strategies for Product Design and Pricing Research}. 4th edition.
-#' Manhattan Beach, CA: Research Publishers LLC.
-#'
-#' }
-#'
-#' @examples
-#' \dontrun{
-#' HOT <- createHOT(
-#'   data = MaxDiff,
-#'   id = 1,
-#'   None = 19,
-#'   prod = 7,
-#'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-#'   method = "MaxDiff",
-#'   choice = 20,
-#'   varskeep = 21
-#' )
-#'
-#' # shareofpref ungrouped
-#' shareofpref(
-#'   data = HOT,
[…]

### 2023-10-09 tests/testthat/test-ShareofPref.R

@@ -1,140 +1,0 @@
-HOT <- createHOT(
-  data = MaxDiff, None = 19,
-  id = 1, prod = 7,
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-  choice = 20, method = "MaxDiff", varskeep = 21
-)
-
-test_that("Error if opts is missing", {
-  expect_error(shareofpref(data = HOT))
-})
-
-test_that("Error if opts has just length 1 ", {
-  expect_error(shareofpref(data = HOT, opts = Option_1))
-})
-
-test_that("Warning if group contains NA ", {
-  HOT2 <- HOT
-
-  HOT2$Group[34] <- NA
-
-  expect_warning(shareofpref(data = HOT2, opts = c(Option_1:None), group = Group))
-})
-
-test_that("Error if alternatives contains NA ", {
-  HOT2 <- HOT
-
-  HOT2$Option_2[34] <- NA
-
-  expect_error(shareofpref(data = HOT2, opts = c(Option_1:None), group = Group))
-})
-
-test_that("Error if alternatives is not numeric ", {
-  HOT2 <- HOT
-
-  HOT2$Option_2 <- base::as.character(HOT2$Option_2)
-
-  expect_error(shareofpref(data = HOT2, opts = c(Option_1:None), group = Group))
-})
-
-test_that("Structure of Output data.frame ", {
-  expect_true(base::is.data.frame(shareofpref(data = HOT, opts = c(Option_1:None))))
-})
-
-test_that("Structure of Output tibble ", {
-  expect_true(tibble::is_tibble(shareofpref(data = HOT, opts = c(Option_1:None))))
-})
-
-test_that("Length of output equals number of alternatives ", {
-  expect_equal(base::nrow(shareofpref(data = HOT, opts = c(Option_1:None))), base::length(HOT %>% dplyr::select(c(Option_1:None))))
-})
-
-test_that("Length of output equals number of groups - 1 group ", {
-  expect_equal(base::nrow(shareofpref(data = HOT, opts = c(Option_1:None), group = Group)), (base::length(base::unique(HOT$Group)) * base::length(HOT %>% dplyr::select(c(Option_1:None)))))
-})
-
-test_that("Length of output equals number of groups - 2 group ", {
-  HOT$Group2 <- c("Group 1", "Group 2")
[…]

### 2023-10-12 paper/paper.Rmd
added paper and attribue importance function - 231012

---
title: 'validateHOT - Validate your Holdout Task'
tags:
  - R
authors:
  - name: Joshua Schramm
    orcid: 0000-0001-5602-4632
    corresponding: True
    affiliation: 1
affiliations:
 - name: Chemnitz University of Technology, Germany
   index: 1
citation_author: Schramm, J.
date: 10 October 2023
year: 2023
bibliography: paper.bib
link-citations: true
output: rticles::joss_article
journal: JOSS
---

```{r include=FALSE}
library(validateHOT)
library(tidyverse)
```

# Summary
validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained a (adaptive) choice-based conjoint analysis and MaxDiff using [Sawtooth Software](https://sawtoothsoftware.com/). Having valid data is essential to predict future choice behavior.

dfsdfdjf

# Statement of need

# Overview and features

```{r}
data("MaxDiff")
HOT <- createHOT(
  data = MaxDiff, # data frame
  id = 1, # column index of unique identifier
  None = 19, # column index of none alternative
  prod = 7, # no of alternatives in HOT excluding none
  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # column index of alternatives
  method = "MaxDiff", # method applied
  choice = 20 # column index of choice alternative
)
```

```{r}
hitrate(
  data = HOT, # data frame
  opts = c(Option_1:None), # column names of alternatives
  choice = choice # column name of choice
) %>% 
  round(3)
```

```{r}
turf(
  data = MaxDiff,
  opts = c(Option_01:Option_16),
  none = none,
  size = 3,
  approach = "thres"
) %>% 
  head(., n = 5) %>% 
  mutate_if(is.numeric, round, 2)
```

# Availability
validateHOT is available on [Github](https://github.com/JoshSchramm94/validateHOT).

# References

### 2023-10-20 README.Rmd
updated tests and formatted function - 231020

@@
 We specify the <code>data</code> argument and the column index of <code>id</code>.
-Since we also have a *no-buy* alternative in our validation task, we next specify the <code>None</code> argument, otherwise we would have left it empty.
+Since we also have a *no-buy* alternative in our validation task, we next specify the <code>none</code> argument, otherwise we would have left it empty.
 Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>.
@@
   id = 1, # column index of the id
-  None = 21, # column index of none alternative
+  none = 21, # column index of none alternative
   prod = 3, # number of alternatives in validation task (excluding none)
@@
 The <code>id</code> is saved in the first column.
-The utilities for the <code>None</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative).
+The utilities for the <code>none</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative).
 Next, we define the <code>prod.levels</code> for each alternative.
@@
   id = 1, # column index of the id
-  None = 15, # column index of none alternative
+  none = 15, # column index of none alternative
   prod = 3, # number of alternatives in validation task (excluding none)

### 2023-10-20 R/ACBC_interpolate.R

@@ -5,49 +5,49 @@
 #'
 #'
 #' \itemize{
-#'   \item ID. \code{ID} of participants
+#'   \item ID. Participants' ID.
 #'   \item RLH. Root likelihood.
-#'   \item NumParameters. Number of parameters per respondent
-#'   \item Att1_Lev1. part-worth utility of Level 1 of Attribute 1
-#'   \item Att1_Lev2. part-worth utility of Level 2 of Attribute 1
-#'   \item Att1_Lev3. part-worth utility of Level 3 of Attribute 1
-#'   \item Att1_Lev4. part-worth utility of Level 4 of Attribute 1
-#'   \item Att1_Lev5. part-worth utility of Level 5 of Attribute 1
-#'   \item Att2_Lin. linear coefficient for linear-coded Attribute 2
-#'   \item Att3_Lev1. part-worth utility of Level 1 of Attribute 3
-#'   \item Att3_Lev2. part-worth utility of Level 2 of Attribute 3
-#'   \item Att3_Lev3. part-worth utility of Level 3 of Attribute 3
-#'   \item Att3_Lev4. part-worth utility of Level 4 of Attribute 3
-#'   \item Att4_Lev1. part-worth utility of Level 1 of Attribute 4
-#'   \item Att4_Lev2. part-worth utility of Level 2 of Attribute 4
-#'   \item Att4_Lev3. part-worth utility of Level 3 of Attribute 4
-#'   \item Att5_Lev1. part-worth utility of Level 1 of Attribute 5
-#'   \item Att5_Lev2. part-worth utility of Level 2 of Attribute 5
-#'   \item Att5_Lev3. part-worth utility of Level 3 of Attribute 5
-#'   \item Att5_Lev4. part-worth utility of Level 4 of Attribute 5
-#'   \item Att6_Lev1. part-worth utility of Level 1 of Attribute 6
-#'   \item Att6_Lev2. part-worth utility of Level 2 of Attribute 6
-#'   \item Att6_Lev3. part-worth utility of Level 3 of Attribute 6
-#'   \item Att6_Lev4. part-worth utility of Level 4 of Attribute 6
-#'   \item Att7_Lev1. part-worth utility of Level 1 of Attribute 7
-#'   \item Att7_Lev2. part-worth utility of Level 2 of Attribute 7
-#'   \item Att7_Lev3. part-worth utility of Level 3 of Attribute 7
-#'   \item Att7_Lev4. part-worth utility of Level 4 of Attribute 7
[…]

### 2023-10-20 R/Accuracy.R

@@ -1,19 +1,19 @@
 #' Accuracy
 #'
-#' @description accuracy is one of the 5 metrics of the confusion matrix
+#' @description \code{accuracy} is one of the 5 metrics of the confusion matrix
 #' and is defined as number of correctly predicted participants divided by
 #' the total number of predictions. See, for example, Burger (2018):
 #' \eqn{\frac{TP + TN}{TP + FP + TN + FN}}, where TP =
 #' True Positives, TN = True Negatives, FP = False Positives, and FN =
 #' False Negatives.
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"accuracy"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param choice column name of the actual choice
-#' @param none column name of none alternative
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"accuracy"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param choice Column name of the actual choice.
+#' @param none Column name of none alternative.
 #'
 #' @details
 #' The current logic of \code{"accuracy"} is to determine whether a binary coded
@@ -69,7 +69,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/MHP.R

@@ -5,12 +5,12 @@
 #' task. Calculates the hit/ choice probability of the actual choice
 #' in the validation/holdout task.
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"mhp"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param choice column name of the actual choice
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"mhp"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param choice Column name of the actual choice.
 #'
 #' @details
 #' Mean hit probability (MHP) measures the averaged hit probability of
@@ -44,7 +44,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/MarkSim.R

@@ -3,15 +3,15 @@
 #' @description
 #' Function to run market simulations with options in a validation/holdout task.
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"marksim"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param method name of the market simulation method that should be conducted.
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"marksim"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param method Name of the market simulation method that should be conducted.
 #' Either needs to be \code{method = "shareofpref"} to run share of preference
 #' as method or \code{method = "firstchoice"} to run first choice rule. Default
-#' set to \code{"shareofpref"}
+#' set to \code{"shareofpref"}.
 #'
 #' @return a tibble
 #' @importFrom dplyr select pick mutate across ungroup group_by summarise count
@@ -57,7 +57,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/MaxDiff.R

@@ -4,27 +4,27 @@
 #'
 #'
 #' \itemize{
-#'   \item ID. \code{ID} of participants
+#'   \item ID. Participants' ID.
 #'   \item RLH. Root likelihood.
-#'   \item Option_01. part-worth utility of MaxDiff object # 1
-#'   \item Option_02. part-worth utility of MaxDiff object # 2
-#'   \item Option_03. part-worth utility of MaxDiff object # 3
-#'   \item Option_04. part-worth utility of MaxDiff object # 4
-#'   \item Option_05. part-worth utility of MaxDiff object # 5
-#'   \item Option_06. part-worth utility of MaxDiff object # 6
-#'   \item Option_07. part-worth utility of MaxDiff object # 7
-#'   \item Option_08. part-worth utility of MaxDiff object # 8
-#'   \item Option_09. part-worth utility of MaxDiff object # 9
-#'   \item Option_10. part-worth utility of MaxDiff object # 10
-#'   \item Option_11. part-worth utility of MaxDiff object # 11
-#'   \item Option_12. part-worth utility of MaxDiff object # 12
-#'   \item Option_13. part-worth utility of MaxDiff object # 13
-#'   \item Option_14. part-worth utility of MaxDiff object # 14
-#'   \item Option_15. part-worth utility of MaxDiff object # 15
-#'   \item Option_16. part-worth utility of MaxDiff object # 16
-#'   \item none. part-worth utility of none parameter
-#'   \item HOT. actual choice in the Holdout task
-#'   \item Group. Grouping variable
+#'   \item Option_01. Part-worth utility of MaxDiff object # 1.
+#'   \item Option_02. Part-worth utility of MaxDiff object # 2.
+#'   \item Option_03. Part-worth utility of MaxDiff object # 3.
+#'   \item Option_04. Part-worth utility of MaxDiff object # 4.
+#'   \item Option_05. Part-worth utility of MaxDiff object # 5.
+#'   \item Option_06. Part-worth utility of MaxDiff object # 6.
+#'   \item Option_07. Part-worth utility of MaxDiff object # 7.
+#'   \item Option_08. Part-worth utility of MaxDiff object # 8.
+#'   \item Option_09. Part-worth utility of MaxDiff object # 9.
+#'   \item Option_10. Part-worth utility of MaxDiff object # 10.
+#'   \item Option_11. Part-worth utility of MaxDiff object # 11.
[…]

### 2023-10-20 R/Precision.R

@@ -4,13 +4,13 @@
 #' and is defined as \eqn{\frac{TP}{TP + FP}}, where TP =
 #' True Positives, FP = False Positives (see, e.g., Burger, 2018).
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"precision"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param choice column name of the actual choice
-#' @param none column name of none alternative
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"precision"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param choice Column name of the actual choice.
+#' @param none Column name of none alternative.
 #'
 #' @details
 #' The current logic of \code{"precision"} is to determine whether a binary
@@ -66,7 +66,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/Reach.R

@@ -6,11 +6,11 @@
 #' many participants you can reach (at least one of the products resemble
 #' a purchase option) is reached with a specific product bundle assortment.
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"reach"} by group(s)
-#' @param opts column names of the alternatives included in the assortment
-#' @param none column name of none / threshold alternative
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"reach"} by group(s).
+#' @param opts Column names of the alternatives included in the assortment.
+#' @param none Column name of none / threshold alternative.
 #'
 #' @details
 #' \code{"reach"} calculates the the percentage of consumers that would be
@@ -45,7 +45,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/Specificity.R

@@ -4,13 +4,13 @@
 #' and is defined as \eqn{\frac{TN}{TN + FP}}, where TN =
 #' True Negatives, FP = False Positives (see, e.g., Burger, 2018).
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"specificity"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param choice column name of the actual choice
-#' @param none column name of none alternative
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"specificity"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param choice Column name of the actual choice.
+#' @param none Column name of none alternative.
 #'
 #' @details
 #' The current logic of \code{"specificity"} is to determine whether a binary
@@ -64,7 +64,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/createHOT.R

@@ -2,29 +2,30 @@
 #'
 #' @description Function used to create utilities for validation task.
 #'
-#' @param data data frame with all relevant variables.
-#' @param id vector of column index of unique identifier in \code{data}.
-#' @param None optional column index to specify \code{None}
+#' @param data A data frame with all relevant variables.
+#' @param id A vector of column index of unique identifier in \code{data}.
+#' @param none An optional column index to specify \code{none}
 #' alternative in \code{data}.
-#' @param prod number of alternatives in the holdout/validation task
-#' (does not count the \code{None} alternative); input has to be numeric
-#' @param prod.levels a list to define the attribute levels of the
-#' alternatives (\code{prod})
-#' @param interpolate.levels a list of the levels of the variables that should
+#' @param prod A vector that specifies the number of alternatives in the
+#' holdout/validation task (does not count the \code{none} alternative). The
+#' input of \code{prod} has to be numeric.
+#' @param prod.levels A list to define the attribute levels of the
+#' alternatives (\code{prod}).
+#' @param interpolate.levels A list of the levels of the variables that should
 #' be interpolated. These have to be the same as provided to Sawtooth Software.
 #' Please make sure to provide the whole list. Only has to be specified for the
-#' variables that are coded as '1' (linear) or '2' (piecewise)
-#' @param piece.p a list of the column indexes of the lower level and the upper
-#' level that should be used for interpolating
-#' @param lin.p vector of the column indexes of the linear variables
-#' @param coding vector of the coding of each attribute, '0' = part-worth
+#' variables that are coded as '1' (linear) or '2' (piecewise).
+#' @param piece.p A list of the column indexes of the lower level and the upper
+#' level that should be used for interpolating.
+#' @param lin.p A vector of the column indexes of the linear variables.
+#' @param coding A vector of the coding of each attribute, '0' = part-worth
 #' coding,'1' = linear coding, '2' = piecewise coding; please make sure to code
-#' linear price of ACBC as piecewise since you have two values to interpolate
[…]

### 2023-10-20 R/hitrate.R

@@ -3,12 +3,12 @@
 #' @description \code{hitrate} measures number of times a choice was correctly
 #' predicted in a validation/holdout task.
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' to get \code{"hitrate"} by group(s)
-#' @param opts column names of the alternatives included in the
-#' validation/holdout task
-#' @param choice column name of the actual choice
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s)
+#' to get \code{"hitrate"} by group(s).
+#' @param opts Column names of the alternatives included in the
+#' validation/holdout task.
+#' @param choice Column name of the actual choice.
 #'
 #' @details
 #' \code{hitrate} measures number of times a participant's choice was correctly
@@ -48,7 +48,7 @@
 #' HOT <- createHOT(
 #'   data = MaxDiff,
 #'   id = 1,
-#'   None = 19,
+#'   none = 19,
 #'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",

### 2023-10-20 R/prob_scores.R

@@ -1,10 +1,10 @@
 #' Probability Scores for (anchored) MaxDiff
 #'
-#' @param data data frame with all relevant variables
-#' @param group optional column name(s) to specify grouping variable(s)
-#' @param items specifies the items
-#' @param set.size size of the choice sets
-#' @param anchor optional variable to specify anchor variable
+#' @param data A data frame with all relevant variables.
+#' @param group Optional column name(s) to specify grouping variable(s).
+#' @param items Vector that specifies the items.
+#' @param set.size A vector that specifies size of the choice set.
+#' @param anchor An optional variable to specify anchor variable.
 #'
 #' @return a tibble
 #'
@@ -108,11 +108,6 @@ prob_scores <- function(data, group = NULL, items, set.size, anchor = NULL) {
   ## check for missings
   if (base::anyNA(data %>% dplyr::select(., {{ items }}))) {
     base::stop("Error: 'items' contains NAs!")
-  }
-
-  # check set.size
-  if (base::is.null(set.size)) {
-    base::stop("Error: 'set.size' is missing!")
   }
 
   if (!base::is.numeric(set.size)) {

### 2023-10-20 README.Rmd
added citation - 231020

@@
 
-The goal of validateHOT is to validate the results of your validation
-task (also known as holdout task). A validation task is essential to
-make sure that your collected data of a MaxDiff, CBC, or ACBC is valid
-and can also predict outside tasks that were not included in estimating
-your utility scores. Although commercial studies often do not include a
+The goal of `validateHOT` is to validate the results of your validation
+task (also known as holdout task) as well as a tool for simulating markets with
+the results of your MaxDiff, CBC, and ACBC. 
+This package is especially relevant for the [Sawtooth Software](https://sawtoothsoftware.com/) community who would like to report their analysis in *R* for open science purposes. Of course,
+this package is also useful for practitioners, who would like to run the analyses
+in an open source software.
+The ultimate goal of these preference measurement techniques is to predict 
+future behavior (Green & Srinivasan, 1990). 
+A validation task is essential to ensure that your collected data of a MaxDiff, 
+CBC, or ACBC is valid and can also predict outside tasks that were not included in estimating
+your utility scores. The main goal  Although commercial studies often do not include a
 validation/holdout task (Yang et al., 2018), it is highly recommended to do so
@@
 
-Chrzan, K., & Orme, B. K. (2019). <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
+Chrzan, K., & Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
 
@@
 
+Green, Paul E.,  and Srinivasan, V.
+1990.
+"Conjoint Analysis in Marketing: New Developments with Implications for Research and Practice." <em>Journal of Marketing 54</em>(4): 3-19.[https://doi.org/10.1177/002224299005400402](https://doi.org/10.1177/002224299005400402).
+
 Hamner, Ben, and Michael Frasco. 2018. “Metrics: Evaluation Metrics for Machine Learning.” [https://CRAN.R-project.org/package=Metrics](https://CRAN.R-project.org/package=Metrics).
 
-Miaoulis, G., Parsons, H., & Free, V. (1990). Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
+Miaoulis, G., Parsons, H., & Free, V. 1990. Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
 

### 2023-10-21 README.Rmd
new readme file - 231021

@@
 The ultimate goal of these preference measurement techniques is to predict 
-future behavior (Green & Srinivasan, 1990). 
-A validation task is essential to ensure that your collected data of a MaxDiff, 
-CBC, or ACBC is valid and can also predict outside tasks that were not included in estimating
-your utility scores. The main goal  Although commercial studies often do not include a
-validation/holdout task (Yang et al., 2018), it is highly recommended to do so
+future behavior (Green & Srinivasan, 1990). Therefore, it is essential for 
+both academics and practitioners to ensure that the collected data is valid 
+and can also predict outside tasks that were not included in the estimation of 
+the utility scores.
+
+Although commercial studies often do not include a validation/holdout task (Yang et al., 2018), it is highly recommended to do so
 (Orme, 2015; Rao, 2014). This validation/holdout task does not only
 help to check whether everything went right during data collection but
-also to determine your final model. <code>validatHOT</code> provides
-some of the relevant metrics to test the performance of your data in
-predicting a holdout task. In [Sawtooth
-Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
-holdout task is automatically implemented. If you conduct a MaxDiff or
-ACBC study, you have to program these on your own.
+also to determine the final model. `validatHOT` provides
+some of the relevant metrics to test the performance of the data in
+predicting a validation/holdout task.
 
-> Currently <code>validateHOT</code> only works with data from Sawtooth Software 
-due to the coding of price.
+Moreover, another key goal of preference measurement techniques is to simulate 
+or predict markets (Gilbride, Lenk, & Brazell, 2008). `validateHOT` provides key functions for an easy implementation to simulate markets for both (A)CBC and MaxDiff.
+
+> `validateHOT` was developed to work with Sawtooth Software. Please be cautious about using it with different platforms (especially for linear and piecewise-coded variables).
 
@@
 and running your initial Hierarchical Bayes models, you can turn to
-<code>validateHOT</code> and test how good your model predicts choices
-in the validation/holdout task. Herefore, you only have to read in your
+`validateHOT` and test how good your model predicts choices
+in the validation/holdout task. Therefore, you only have to read in your
 raw utility scores as well as the actual choice of your validation/
-holdout task. You can use the <code>merge()</code> provided by the
-<code>base</code> package (R Core Team, 2023). Afterward, you can read in your data
-file and enjoy <code>validateHOT</code>. We provide a tutorial a short tutorial in the vignette.
+holdout task. You can use the `merge()` function provided by the *R* base package to do so (R Core Team, 2023). Afterward, you can read in your data
+file and enjoy `validateHOT`. We provide a short tutorial in the markdown, for a more detailed tutorial, please see the vignette that comes along with `validateHOT`.
 
-👈🏾 <u>**What you get**</u>:<br> At the moment, <code>validateHOT</code>
+👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT`
 provides functions for 3 key areas:
@@
 
-For all 3 key areas, the <code>createHOT</code> function is essential.
+For all 3 key areas, the `createHOT()` function is essential.
 This function creates the total utilities for each alternative in the
@@
 total utility of a profile or conjoint model is the sum of its attribute
-levels. <code>createHOT</code> will do exactly this for you.
+levels. `createHOT()` will calculate the total utility of each alternative you specify.
+
+> We are planning to expand the functions of the package by also providing functions to convert the raw utilities into scores that are easier to interpretate, for example, `prob_scores()` to calculate choice probabilities of both unanchored and anchored MaxDiff or `att_imp()` to calculate the importance of the attributes included in an ACBC or CBC.
 
@@
 
-<li><code>hitrate</code>: creates the Hit Rate (correctly predicted
-choices) of your validation task. The output will contain 
+<li><code>hitrate()</code>: creates the Hit Rate (correctly predicted
+choices) of your validation/holdout task. The output will contain 
 the percentage of how many choices were correctly predicted, 
@@
 
-<li><code>kl</code>: Kullback-Leibler-Divergence measures the
+<li><code>kl()</code>: Kullback-Leibler-Divergence measures the
 divergence between the actual choice distribution and the predicted
@@
 
-<li><code>mae</code>: mean absolute error, i.e., deviation between
+<li><code>mae()</code>: calculates the mean absolute error, i.e., deviation between
 predicted and stated choice share. </li>
 
-<li><code>medae</code>: median absolute error, which is less affected
+<li><code>medae()</code>: calculates the median absolute error, which is less affected
 by outliers compared to the mean absolute error.</li>
 
-<li><code>mhp</code>: averaged hit probability of participant's actual
+<li><code>mhp()</code>: calculates the averaged hit probability of participant's actual
 choice in the validation/holdout task.</li>
 
-<li><code>rmse</code>: provides the root-mean-square error of deviation
+<li><code>rmse()</code>: provides the root-mean-squared error of deviation
 between predicted and stated choice share.</li>
@@
 
-All functions can be extended with the `group` argument to get output by group.
+All functions can be extended with the `group` argument to get 
+output split by group(s).
 
@@
 matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
-currently have to include a **none** alternative in your validation/holdout task. We currently
-predict, e.g., whether a buy or no-buy was correctly predicted.
-Information could be used for overestimating and underestimating,
+currently have to include a **none** alternative in your validation/holdout 
+task. We currently predict, e.g., whether a buy or no-buy was correctly 
+predicted. Information could be used for overestimating and underestimating,
 respectively, of product purchases. In the following <code>TP</code>
@@
 negatives (Burger, 2018). 
-To translate this to the `validateHOT` logic, imagine you have a validation/holdout task
-with 5 alternatives plus the alternative not to buy any of those chosen. `validateHOT` now measures
-whether or not a buy (participant opts for one of the 5 alternatives) or a no-buy (participant opts
+To translate this to the `validateHOT` logic, imagine you have a 
+validation/holdout task with 5 alternatives plus the alternative not to buy 
+any of those chosen. `validateHOT` now measures whether or not a buy 
+(participant opts for one of the 5 alternatives) or a no-buy (participant opts
 for the no-buy alternative), respectively, is correctly predicted.
@@
 
-<li><code>accuracy</code>: calculates the number of correctly predicted choices (buy or no-buy);
+<li><code>accuracy()</code>: calculates the number of correctly predicted choices (buy or no-buy);
 $\frac{TP + TN}{TP + TN + FP + FN}$ (Burger, 2018). 
@@
 
-<li><code>f1</code>: defined as
+<li><code>f1()</code>: defined as
 $\frac{2 * precision * recall}{precision + recall}$ or stated
@@
 
-<li><code>precision</code>: defined as $\frac{TP}{TP + FP}$ (Burger, 2018).</li>
+<li><code>precision()</code>: defined as $\frac{TP}{TP + FP}$ (Burger, 2018).</li>
 
-<li><code>recall</code>: defined as $\frac{TP}{TP + FN}$ (Burger, 2018).</li>
+<li><code>recall()</code>: defined as $\frac{TP}{TP + FN}$ (Burger, 2018).</li>
 
-<li><code>specificity</code>: defined as $\frac{TN}{TN + FP}$ (Burger, 2018).</li>
+<li><code>specificity()</code>: defined as $\frac{TN}{TN + FP}$ (Burger, 2018).</li>
 
@@
 
-Again, all functions can be extended with the `group` argument to get output by group.
+Again, all functions can be extended with the `group` argument to get output 
+split by group(s).
 
@@
 
-<li><code>turf</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
-29) that helps to find the perfect product bundle based on the <code>reach</code> (e.g., how many participants consider buying at least one product of that assortment) and the <code>frequency</code> (how many products are on average a purchase option).
-<code>turf</code> currently provides both the threshold approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
-112) and the first choice approach (<code>approach = 'fc'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
+<li>`turf()`: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
+29) that helps to find the perfect product bundle based on the reach (e.g., how many participants consider buying at least one product of that assortment) and the frequency (how many products are on average a purchase option).
+`turf()` currently provides both the *threshold*  approach (`approach = 'thres'`; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
+112) and the *first choice* approach (`approach = 'fc'`; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
 111).</li>
 
-<li><code>freqassort</code>: Similar to <code>turf</code>, <code>freqassort</code>
+<li>`freqassort()`: Similar to `turf()`, `freqassort()`
 will give you the averaged frequency, how many products the participants
 will choose from your in the function determined potential assortment. 
-Again, you have to define a <code>none</code> alternative, because <code>freqassort</code> uses the <i>threshold</i> approach,
-meaning if the utility of one product is above the utility of <code>none</code>,
-it is marked as potential purchase option.
-While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>freqassort</code>.</li>
+Again, you have to define a `none` alternative, because `freqassort()` uses 
+the <i>threshold</i> approach, meaning if the utility of one product is above 
+the utility of `none`, it is marked as potential purchase option. 
+While `turf()` calculates the reach and frequency for <b>all</b> combinations, 
+you specify the combination you are interested in `freqassort()`.</li>
 
-<li><code>reach</code>: Similar to <code>turf</code>, <code>reach</code> will
+<li>`reach()`: Similar to `turf()`, `reach()` will
 give you the averaged percentage of how many participants you can reach
@@
 potential assortment.
-<code>reach</code> also uses the <i>threshold</i> approach (see above).
-While <code>turf</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach</code></li>
+`reach()` also uses the <i>threshold</i> approach (see above).
+While `turf()` calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in `reach()`.</li>
 
-<li><code>marksim</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
+<li>`marksim()`: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
 calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>
@@
 
+> <b>Important</b>: For both `reach()` and `freqassort()`, `none` does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.
+
 ### Data Frames provided by <code>validateHOT</code>
+
+`validaeHOT` provides 5 data sets that come with the package. These datasets 
+should help to better understand the way the data needs to be defined, 
+especially for the `createHOT()` function.
 
@@
 
-<li><code>ACBC</code>: Example data set with raw utilities of an ACBC
+<li>`ACBC`: Example data set with raw utilities of an ACBC
 study conducted in Sawtooth. Price was linear-coded while the other
-attributes were coded as part-worths.</li>
+attributes were coded as part-worths.
 
-<li><code>ACBC_interpolate</code>: Example data set with raw utilities
+<li>`ACBC_interpolate`: Example data set with raw utilities
 of an ACBC study conducted in Sawtooth. Price was piecewise-coded,
@@
 
-<li><code>CBC</code>: Example data set with raw utilities of an CBC
+<li>`CBC`: Example data set with raw utilities of a CBC
 study conducted in Sawtooth. All attributes were coded as
@@
 
-<li><code>CBC_lin</code>: Example data set with raw utilities of an CBC
+<li>`CBC_lin`: Example data set with raw utilities of a CBC
 study conducted in Sawtooth. One attribute was linear coded while the
@@
 
-<li><code>MaxDiff</code>: Example data set with raw utilities of an
+<li>`MaxDiff`: Example data set with raw utilities of a
 MaxDiff study conducted in Sawtooth.</li>
@@
 
-## Why <code>validateHOT</code>
+## Why `validateHOT`
 
@@
 One of the chapters in this class is about model validating the results obtained and we teach this,
-of course, in *R*.
-Of course, there are other great packages which are faster in running (i.e., `Metrics` by Hamner & Frasco, 2018), 
-however, these packages need some more data wrangling in order to use the
-appropriate functions, which might be a burden or barrier for one or
+of course, in *R*. We want to put a strong emphasis on open science and providing tools to run the analyses and provide the code afterwards is essential.
+
+Of course, there are other great packages which are faster in running (i.e., `Metrics` by Hamner & Frasco, 2018), however, these packages need some more data wrangling in order to use the
+appropriate functions with the raw utilities, which might be a burden or barrier for one or
 the other.
@@
 any validation task. Again, the missing experience in *R* could be one explanation. 
-Since these functions are not always implemented in other softwares, this might be one reason why
+Since these functions are not always implemented in other software, this might be one reason why
 they do not include one simply because they do not know how to use it
@@
 
-You can install the development version of validateHOT from
+You can install the development version of `validateHOT` from
 [GitHub](https://github.com/) with:
@@
 
-Since *CBC's* are most commonly used between *CBC*, *ACBC*, and
+Since *CBC's* are applied more commonly compared to *ACBC* and
 *MaxDiff*, we will provide an example with a *CBC*. Let us begin with a
-*CBC* where all of the variables are coded as part-worth, so we need no
-interpolation. Let us load the <code>CBC</code> data frame for this
+*CBC* where all of the attributes are part-worth coded, so we need no
+interpolation. Let us load the `CBC` data frame for this
 example.
@@
 
-Now imagine you included a validation/ holdout task with three
-alternatives as well as an no-buy option.
-We specify the <code>data</code> argument and the column index of <code>id</code>.
-Since we also have a *no-buy* alternative in our validation task, we next specify the <code>none</code> argument, otherwise we would have left it empty.
-Afterwards, we specify the number of products (<code>prod</code>) we include (excluding the *no-buy* alternative), which we define in the next step with the argument <code>prod.levels</code>.
-If we look back at the data frame, we can see that the first alternative in the holdout task <code>c(4, 9, 19)</code> is composed of the following attribute levels <code>Att1_Lev1</code>, <code>Att2_Lev1</code>, and <code>Att3_Lev5</code>.
+Now imagine you included a validation/holdout task with three
+alternatives plus a no-buy alternative.
+We specify the `data` argument and the column index of `id`.
+Since we also have a *no-buy* alternative in our validation task, we next specify the `none` argument, otherwise we would have left it empty.
+Afterwards, we specify the number of alternatives (`prod`) in our validation/holdout task (excluding the *no-buy* alternative).
+Next, we define each alternative with the argument `prod.levels`.
+If we look back at the data frame, we can see that the first alternative in the holdout task (`c(4, 9, 19)`) is composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and `Att3_Lev5`.
 
-As mentioned above, all the attributes are part-worth coded, therefore, we set <code>coding = c(0, 0, 0)</code>.
-Finally, we specify the method of preference measurement technique, which is <code>method = "CBC"</code> in our case and the column index of the actual participant's choice (<code>choice</code>).
-If you run the code, a data frame called <code>HOT</code> (short form of **H**old**o**ut **t**ask) will be returned to the global environment.
+As mentioned above, all the attributes are part-worth coded, therefore, we set `coding = c(0, 0, 0)`.
+Finally, we specify the method, which is `method = "CBC"` in our case, and define the column index of the actual participant's choice (`choice`).
+If you run the code, a data frame called `HOT` (short form of **H**old**o**ut **t**ask) will be returned to the global environment.
 
-> &#10071; <code>createHOT</code> is currently just taking indexes instead of column names, please be aware of this.
-However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package (R Core Team, 2023).
-For example, if you want to find out the column index of <code>ID</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.
+> &#10071; `createHOT()` is currently just taking indexes instead of column names, please be aware of this.
+However, you can easily find out the index by either using the `names()` function to see all names of the dataframe, or if you already know the name of the variable, you can use `which()` and `colnames()`, both functions are provided by the base package (R Core Team, 2023).
+For example, if you want to find out the column index of `ID`, you could run `which(colnames(CBC) == "ID")` to determine the column index of `ID`.
 
@@
   prod = 3, # number of alternatives in validation task (excluding none)
-  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each alternative
+  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each attribute
   coding = c(0, 0, 0), # how the attributes were coded
@@
 
-Let us take a glimpse at the output, which shows the total raw utilities for each of the alternatives 
-included in the validation/holdout task.
+Let us take a glimpse at the output, which shows the participants' total raw utilities for each of the 3 alternatives that were included in the validation/holdout task.
 
@@
 
-In the next step, we would like to see how well our model (from which we took the raw utilities) predict 
-the actual choices in the validation/holdout task. First, we will test the <code>hitrate()</code> function. 
-We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember 
-there are three alternatives + the *no-buy* alternative), and finally the actual choice.
+In the next step, we would like to see how well our model (from which we took the raw utilities) predicts 
+the actual choices in the validation/holdout task. First, we will run the `hitrate()` function. 
+We specify the `data`, the column names of the alternatives (`opts`; remember 
+there are three alternatives + the *no-buy* alternative), and finally the actual choice (`choice`).
 
@@
 
-Let us also check the magnitude of the mean absolute error by running the <code>mae()</code> function.
+Next, we look at the magnitude of the mean absolute error by running the `mae()` function. The arguments are the same as for the `hitrate()` function.
 
@@
 ```
-To cover also one example on how to use the metrics of the confusion matrix, we could test whether our model overestimates the purchase behavior (our model predicts a *buy* although participant opts for a *no* buy) or underestimates it (i.e., model predicts *no-buy* but participant opts for a *buy*).
-We will test the accuracy of the model by running the <code>accuracy()</code> function.
+
+To cover also one example on how to use the metrics of the confusion matrix, we could test whether our model overestimates the purchase behavior (our model predicts a *buy* although participant opts for a *no-buy*) or underestimates it (i.e., model predicts *no-buy* but participant opts for a *buy*).
+We will test the accuracy of the model by running the `accuracy()` function.
 
@@
 
-Finally, let us test, how many participants would at least buy one of the three products, assuming that this is one potential assortment we would like to offer to our consumers.
-We will use the <code>reach()</code> function and use the threshold approach.
-To specify the bundles we are offering we use the <code>opts</code> argument in our function.
+Finally, let us test, how many participants would at least buy one of the 3 products, assuming that this is one potential assortment we would like to offer to our consumers.
+We will use the `reach()` function.
+To specify the bundles we are offering we use the `opts` argument in our function.
 
@@
 
-In a second example, we again use a *CBC*, however, this time we show how to use <code>validateHOT</code> if one of the variables are linear coded.
-All other examples are provided in the accompanied vignette.
+In a second example, we again use a *CBC*, however, this time we show how to use `validateHOT` if one of the variables are linear coded. All other examples are provided in the accompanied vignette.
 
-We are using the data frame <code>CBC_lin</code> which is also provided by the <code>validateHOT</code> package. We first load the data frame.
+We are using the data frame `CBC_lin`. Again, we first load the data frame.
 
@@
 We use a validation/holdout task with three alternatives plus the *no-buy* alternative, just as we did in the previous example.
-The only difference to the previous example is that for our model estimation, the third attribute (<code>Att3_Lin</code>) was coded as linear.
+The only difference to the previous example is that for our model estimation, the third attribute (`Att3_Lin`) was coded as linear.
 
-Again, we first define <code>data</code>.
-The <code>id</code> is saved in the first column.
-The utilities for the <code>none</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative).
-Next, we define the <code>prod.levels</code> for each alternative.
-For example, we can see that the second see that the second alternative is composed of <code>Att1_Lev5</code>, <code>Att2_Lev4</code>, and <code>60</code> which is the value that should be interpolated.
-We can see that this value is the one that needs to be interpolated if we take a closer look at the <code>coding</code> argument.
-This tells us that the first two attributes (<code>Att1_Lev5</code>, <code>Att2_Lev4</code> in the case of alternative 2) are part-worth coded (<code>0</code>) while the third attribute is linear coded (<code>1</code>).
+Again, we first define data.
+The `id` is saved in the first column.
+The utilities for the `none` parameter are stored in the 15th column, and we again set `prod` to 3 (**excluding** the *no-buy* alternative).
+Next, we define the `prod.levels` for each alternative.
+For example, we can see that the second alternative is composed of `Att1_Lev5`, `Att2_Lev4`, and `60` which is the value that should be interpolated.
+We tell `createHOT()` that this value needs to be interpolated by specifying the `coding` argument.
+This tells us that the first two attributes (`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are part-worth coded (`0`) while the third attribute is linear coded (`1`).
 
-To interpolate the value, we have to provide <code>validateHOT</code> the <code>interpolate.levels</code>.
+To interpolate the value, we have to provide `createHOT()` the `interpolate.levels`.
 These **need** to be the same as provided to Sawtooth as levels.
-Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of <code>interpolate.levels</code>.
+Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of `interpolate.levels`.
 In our case, we had 7 levels that range from 10 to 70.
 
-Next, we define the column index of the linear coded variable (<code>lin.p</code>) and specify the <code>coding</code> we talked about above.
-Again, we are running a *CBC* specified by the <code>method</code> argument.
-This time, we would like to keep some of the variables in the data frame, which we specify in <code>varskeep</code>.
+Next, we define the column index of the linear coded variable (`lin.p`) and specify the `coding` we talked about above.
+Again, we are running a *CBC* specified by the `method` argument.
+This time, we would like to keep some of the variables in the data frame, which we specify in `varskeep`.
 We only keep one further variable, however, you can specify as many as you want.
 This could be relevant if you would like to display results per group.
-Finally, we just tell <code>validateHOT</code> the column index of the final choice (<code>choice</code>) and we are all set.
+Finally, we just tell `createHOT()` the column index of the final choice (`choice`) and we are all set.
 
@@
   prod = 3, # number of alternatives in validation task (excluding none)
-  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each alternative (for linear coded we specify value to be interpolated)
+  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each attribute (for linear coded we specify value to be interpolated)
   interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
@@
 However, let us take a look at some examples in which we display the results per group.
-Let us again begin with the <code>hitrate()</code> function.
-To do so, we specify the column name of the grouping variable in the <code>group</code> argument.
+Let us again begin with the `hitrate()` function.
+To do so, we specify the column name of the grouping variable in the `group` argument.
 
@@
 However, the output is the same if it is a factor or if it is labelled data.
-To proof this we just quickly change <code>group</code> into a factor by using the <code>factor()</code> function provided by R Core Team (2023).
+To proof this we just quickly change `group` into a factor by using the `factor()` function provided by the *R*  Core Team (2023).
 
@@
 
-Afterward, we display the *mean hit probability* by running the <code>mhp()</code> function.
+Afterward, we display the *mean hit probability* by running the `mhp()` function.
 
@@
 
+Gilbride, Timothy J., Lenk, Peter J., and Brazell, Jeff D.
+2008.
+"Market Share Constraints and the Loss Function in Choice-Based Conjoint Analysis." <em>Marketing Science 27</em>(6):995-1011.[https://doi.org/10.1287/mksc.1080.0369](https://doi.org/10.1287/mksc.1080.0369)
+
 Green, Paul E.,  and Srinivasan, V.

### 2023-10-21 README.Rmd
new readme file - 231021 v2

@@
 
-<li>`turf()`: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
+<li><code>turf()</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
 29) that helps to find the perfect product bundle based on the reach (e.g., how many participants consider buying at least one product of that assortment) and the frequency (how many products are on average a purchase option).
-`turf()` currently provides both the *threshold*  approach (`approach = 'thres'`; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
-112) and the *first choice* approach (`approach = 'fc'`; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
+<code>turf()</code> currently provides both the *threshold*  approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
+112) and the *first choice* approach (<code>approach = 'thres'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
 111).</li>
 
-<li>`freqassort()`: Similar to `turf()`, `freqassort()`
+<li><code>freqassort()</code>: Similar to <code>turf()</code>, <code>freqassort()</code>
 will give you the averaged frequency, how many products the participants
 will choose from your in the function determined potential assortment. 
-Again, you have to define a `none` alternative, because `freqassort()` uses 
+Again, you have to define a <code>none</code> alternative, because <code>freqassort()</code> uses 
 the <i>threshold</i> approach, meaning if the utility of one product is above 
-the utility of `none`, it is marked as potential purchase option. 
-While `turf()` calculates the reach and frequency for <b>all</b> combinations, 
-you specify the combination you are interested in `freqassort()`.</li>
+the utility of <code>none</code>, it is marked as potential purchase option. 
+While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, 
+you specify the combination you are interested in <code>freqassort()</code>.</li>
 
-<li>`reach()`: Similar to `turf()`, `reach()` will
+<li><code>reach()</code>: Similar to <code>turf()</code>, <code>reach()</code> will
 give you the averaged percentage of how many participants you can reach
@@
 potential assortment.
-`reach()` also uses the <i>threshold</i> approach (see above).
-While `turf()` calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in `reach()`.</li>
+<code>reach()</code> also uses the <i>threshold</i> approach (see above).
+While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach()</code>.</li>
 
-<li>`marksim()`: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
+<li><code>marksim()</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
 calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>
@@
 
-> <b>Important</b>: For both `reach()` and `freqassort()`, `none` does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.
+> <b>Important</b>: For both <code>reach()</code> and <code>freqassort()</code>, <code>noen</code> does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.
 
@@
 
-<li>`ACBC`: Example data set with raw utilities of an ACBC
+<li><code>ACBC</code>: Example data set with raw utilities of an ACBC
 study conducted in Sawtooth. Price was linear-coded while the other
-attributes were coded as part-worths.
+attributes were coded as part-worths.</li>
 
-<li>`ACBC_interpolate`: Example data set with raw utilities
+<li><code>ACBC_interpolate</code>: Example data set with raw utilities
 of an ACBC study conducted in Sawtooth. Price was piecewise-coded,
@@
 
-<li>`CBC`: Example data set with raw utilities of a CBC
+<li><code>CBC</code>: Example data set with raw utilities of a CBC
 study conducted in Sawtooth. All attributes were coded as
@@
 
-<li>`CBC_lin`: Example data set with raw utilities of a CBC
+<li><code>CBC_lin</code>: Example data set with raw utilities of a CBC
 study conducted in Sawtooth. One attribute was linear coded while the
@@
 
-<li>`MaxDiff`: Example data set with raw utilities of a
+<li><code>MaxDiff</code>: Example data set with raw utilities of a
 MaxDiff study conducted in Sawtooth.</li>

### 2023-10-22 README.Rmd
paper updated - 231023

@@
 > <b>Important</b>: For both <code>reach()</code> and <code>freqassort()</code>, <code>noen</code> does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.
+
+### Reestimating raw utilities
+
+<code>validateHOT</code> also provides 2 functions to better interpret the scores of both (A)CBC and MaxDiff. Currently, two functions are provided, namely:
+
+<ul>
+<li><code>att_imp()</code>: converts the raw utilities of either an ACBC or CBC into importance scores for each attribute (see, Orme, 2020, pp. 79-81)</li>
+
+<li><code>prob_scores()</code>converts the raw utilities of a MaxDiff to choice probabilities by applying the following procedures:
+<ul><li>For unanchored MaxDiff: First, the scores are zero-centered, afterwards they are transformed by the following formula $\frac{exp^{U_i}}{(exp^{U_i} + a - 1)}$ (Chrzan & Orme, 2019, p.
+56), where *$U_i$* is the raw utility of item *i* and <code>a</code> is the number of items shown simultaneously per MaxDiff task.
+Finally, the scores are normalized.</li>
+<li>For anchored MaxDiff: $\frac{exp^{U_i}}{(exp^{U_i} + a - 1)} * 100 * \frac{1}{a}$ (Chrzan & Orme, 2019, p. 59).</li>
+</ul>
+</li>
+</ul>
 
@@
 
-Orme, B. K. (2020). <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.
+Orme, B. K. 2020. <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.
 

### 2023-10-22 paper/paper.Rmd
paper updated - 231023

@@
   - R
+  - MaxDiff
+  - Conjoint Analysis
+  - Market Simulations
+  - Predictive Validity
 authors:
@@
     affiliation: 1
+  - name: Marcel Lichters
+    orcid: 0000-0002-3710-2292
+    corresponding: FALSE
+    affiliation: 1, 2    
 affiliations:
@@
    index: 1
-citation_author: Schramm, J.
-date: 10 October 2023
+ - name: Otto von Guericke University of Magdeburg, Germany
+   index: 1
+citation_author: Schramm & Lichters.
+date: 22 October 2023
 year: 2023
@@
 # Summary
-validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained a (adaptive) choice-based conjoint analysis and MaxDiff using [Sawtooth Software](https://sawtoothsoftware.com/).
-Having valid data is essential to predict future choice behavior.
 
-dfsdfdjf
+validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/).
+The ultimate goal of preference measurement techniques such as (A)CBC or MaxDiff is to predict future behavior [@green1990].
+Therefore, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks.
+The easiest way to test this is to include so-called holdout or validation task [@Orme2015].
+Despite the important role of validation tasks, most of the conjoint studies done in practice do not include them [@yang2018], which is unsatisfactory, given the fact that the model is used to estimate market shares which is the basis for relevant marketing decisions.
+
+validateHOT combines both validation and market simulation in one package.
+validateHOT's advantages are the following: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is open source tool for function that are usually implemented in Sawtooth Software and are ofen a black-box for researchers and practitioners.
 
@@
   data = MaxDiff, # data frame
-  id = 1, # column index of unique identifier
-  None = 19, # column index of none alternative
+  id = 1, # index unique identifier
+  none = 19, # index of none alternative
   prod = 7, # no of alternatives in HOT excluding none
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # column index of alternatives
+  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # index of alternatives
   method = "MaxDiff", # method applied
@@
 # Availability
+
 validateHOT is available on [Github](https://github.com/JoshSchramm94/validateHOT).

### 2023-10-22 R/att_imp.R

@@ -79,6 +79,14 @@ att_imp <- function(data, group = NULL, attrib, coding, interpolate.levels = NUL
     warning("Warning: 'group' contains NAs!")
   }
 
+  if (base::is.null(coding)){
+    base::stop("Error: 'coding' has to be specified!")
+  }
+
+  if (base::length(attrib) != base::length(coding)){
+    base::stop("Error: 'coding' and 'attrib' have to have the same length!")
+  }
+
 
   # test numeric input for coding
   if (!(base::is.null(coding))) {

### 2023-10-24 paper/paper.Rmd
updated paper - 231024

@@
  - name: Otto von Guericke University of Magdeburg, Germany
-   index: 1
+   index: 2
 citation_author: Schramm & Lichters.
@@
 ---
+
+\setlength{\headheight}{63.55022pt}
+\addtolength{\topmargin}{-0.95425pt}
+\newcommand{\colcod}[1]{\texttt{\color{purple}#1}}
 
@@
 validateHOT combines both validation and market simulation in one package.
-validateHOT's advantages are the following: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is open source tool for function that are usually implemented in Sawtooth Software and are ofen a black-box for researchers and practitioners.
+validateHOT's advantages are the following: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is open source tool for functions that are usually implemented in Sawtooth Software and are often a black-box for researchers and practitioners.
 
@@
 
-# Overview and features
+validateHOT is a practical tool for Sawtooth Software users in industry as well as academia.
+It provides an open source solution for a) validating a validation/holdout task and therefore ensuring that the model has predictive validity; b) running market simulations.
+Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix (see \autoref{tab:table1}).
+However, to put the Sawtooth export into the right format, the user needs some data wrangling which can be a barrier.
+Other packages mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
+To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations is still missing.
+The goal of validateHOT is still to fill this research gap.
+validateHOT creates market shares based on *share of preferences* or *first choice rule*, which can be helpful to report results for research articles according to open science standards.
+In addition, it also provides the function \colcod{turf}, which was offered formerly by the turfR package, which is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)).
+So, currently practitioners and academics mainly have to stick to paid solutions, for example, Sawtooth Software.
+
+# Key functions
+
+The main function that creates the validation/holdout task is the \texttt{\color{purple}createHOT} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
+82].
+The other functions in the package mainly focus on four different components which are outlined in \autoref{tab:table1}.
+
+| Validation metrics | Confusion matrix | Market Simulations | Rescaling scores |
+|:----------------:|:----------------:|:----------------:|:----------------:|
+|     hitrate()      |    accuracy()    |    freqassort()    |    att_imp()     |
+|        kl()        |       f1()       |     marksim()      |  prob_scores()   |
+|       mae()        |   precision()    |      reach()       |                  |
+|      medae()       |     recall()     |       turf()       |                  |
+|       mhp()        |  specificity()   |                    |                  |
+|       rmse()       |                  |                    |                  |
+
+: Overview of main four components of validateHOT and their corresponding functions \label{tab:table1}
+
+# Typical workflow
+
+After running the Hierarchical Bayes estimation in Sawtooth Software, the raw utility scores should be exported.
+Both the raw utilities and the actual choice in the validation/holdout task needs be read into *R* (please see the vignette for more advice).
+In the following, we provide the workflow for a MaxDiff study (the vignette also provides detailed examples for a CBC as well as an ACBC).
+
+We create the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}).
+Moreover, we also define the method, the actual choice in the validation/holdout task as well as the column indexes of the alternatives in the validation/holdout task.
+Finally, we define variables that we would like to keep in the data frame (\colcod{varskeep}).
+\texttt{\color{purple}createHOT} returns a data frame which we need for subsequent analyses.
 
 ```{r}
-data("MaxDiff")
+data("MaxDiff") # read in the data
 HOT <- createHOT(
@@
   method = "MaxDiff", # method applied
-  choice = 20 # column index of choice alternative
+  choice = 20, # column index of choice alternative
+  varskeep = 21
 )
 ```
+
+Next, to get the relevant validation metrics that are often reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wlömert2014], we only need to provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
+Everything can be implemented in the tidyverse [@tidyverse] logic.
+
+\pagebreak
 
@@
 
+Next, validateHOT also provides the five metrics for the confusion matrix.
+The underlying logic hereby is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
+validateHOT calculates, for example, how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (exemplary showed by applying the \texttt{\color{purple}accuracy} function and results split by \texttt{\color{purple}Group}).
+
+```{r}
+accuracy(
+  data = HOT, # data frame
+  group = Group, # optional grouping variable
+  opts = c(Option_1:None), # column names of alternatives
+  choice = choice, # column name of choice
+  none = None # column name 
+)
+```
+
+Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim} as well as \texttt{\color{purple}turf}.
+First, we calculate the market shares based on the multinomial logit model [@McFadden1974].
+Besides the aggregated shares, \texttt{\color{purple}marksim} also provides standard errors and the 95th confidence interval.
+
+```{r}
+marksim(
+  data = HOT,
+  opts = c(Option_1:None),
+  method = "shareofpref"
+)
+```
+
+\texttt{\color{purple}turf}, a "product line extension model" [@miaoulis1990, p.
+29] is a tool to find the perfect assortment that creates the highest reach and a powerful tool for MaxDiff studies [@chrzan2019, p.
+108].
+To optimize the search for the optimal bundle, we could include as well the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, as well as \texttt{\color{purple}prohib}, to define prohibitions of combinations of items that should not be part of the assortment (please see the vignette for more details and also to see how to apply \texttt{\color{purple}turf} with data obtained by a likert scale).
+
+For the following example, let us assume that you conducted an anchored MaxDiff analysis with 10 items (\colcod{opts}) and you want to find the best assortment with a size of 3 (\colcod{size = 3}).
+As a threshold (\colcod{none}) you use the anchor (no-buy alternative).
+Finally, you apply the threshold approach, that is that each alternative with a utility above the threshold (in our case \colcod{none}) is marked as purchase option.
+We reduce the output to the Top 5 combos based on the reach (a \colcod{1} indicates present in this assortment while \colcod{0} means not present).
+
 ```{r}
@@
   data = MaxDiff,
-  opts = c(Option_01:Option_16),
+  opts = c(Option_01:Option_10),
   none = none,
@@
   head(., n = 5) %>% 
-  mutate_if(is.numeric, round, 2)
+  mutate_if(is.numeric, round, 2) %>% 
+  t() %>% 
+  as.data.frame() %>% 
+  slice(-1) %>% 
+  rename_all(., ~ paste0("Combo ", c(1:5)))
 ```

### 2023-10-24 R/Precision.R

@@ -39,6 +39,16 @@
 #' \code{none} to specify column name of the \code{none} alternative in the
 #' validation/holdout task.
 #'
+#' Please be aware about the following 2x2 table regarding coding of buy and
+#' no-buy choice
+#'
+#'\tabular{crcc}{
+#'    \tab \tab  Predicted           \tab    \cr
+#' Observed \tab \tab  Buy \tab No-buy  \cr
+#'  \tab Buy \tab A \tab B  \cr
+#'  \tab No-Buy \tab C \tab D  \cr
+#' }
+#'
 #' @importFrom dplyr group_by summarise select pick
 #' @importFrom magrittr "%>%"
 #'

### 2023-10-24 tests/testthat/test-Precision.R

@@ -137,3 +137,16 @@ test_that("check whether examples are correct ", {
   expect_equal(base::round(base::as.numeric(precision(data = HOT, opts = c(Option_1:None), choice = choice, none = None)), 0), 71)
   expect_equal(base::round(base::as.numeric(precision(data = HOT, opts = c(Option_1:None), choice = choice, none = None, group = Group)[[2]]), 0), c(80, 67, 65))
 })
+
+test_that("Test whether results equals Metrics::precision ", {
+  metr <- HOT %>%
+    mutate(pred = max.col(.[c(2:9)]),
+           pred = ifelse(pred == 8, 0, 1),
+           choice = ifelse(choice == 8, 0, 1)) %>%
+    select(pred, choice)
+
+  actual <- c(unname(unlist(metr$choice)))
+  predicted <- c(unname(unlist(metr$pred)))
+
+  expect_equal(base::round(base::as.numeric(precision(data = HOT, opts = c(Option_1:None), choice = choice, none = None)), digits = 2), round(Metrics::precision(actual, predicted) * 100, digits = 2))
+})

### 2023-10-24 tests/testthat/test-RMSE.R

@@ -130,3 +130,16 @@ test_that("check whether examples are correct ", {
   expect_equal(base::round(base::as.numeric(rmse(data = HOT, opts = c(Option_1:None), choice = choice)), 2), 7.88)
   expect_equal(base::round(base::as.numeric(rmse(data = HOT, opts = c(Option_1:None), choice = choice, group = Group)[[2]]), 2), c(5.25, 9.98, 10.61))
 })
+
+
+test_that("Test whether results equals Metrics::rmse ", {
+  actual <- HOT %>%
+    dplyr::mutate(dplyr::across(Option_1:None, function(x) (base::exp(x)/base::rowSums(base::exp(.[c(2:9)]))))) %>%
+    dplyr::summarise(dplyr::across(Option_1:None, ~ mean(.x))) %>%
+    base::unlist() %>%
+    base::unname()
+
+  predicted <- base::unname(c(base::prop.table(base::table(HOT$choice))))
+
+  expect_equal(base::round(base::as.numeric(rmse(data = HOT, opts = c(Option_1:None), choice = choice)), digits = 2), round(Metrics::rmse(actual, predicted) * 100, digits = 2))
+})

### 2023-10-26 paper/paper.Rmd
updated paper - 231025

@@
    index: 2
-citation_author: Schramm & Lichters.
+citation_author: Schramm & Lichters
 date: 22 October 2023
@@
 
+```{=tex}
 \setlength{\headheight}{63.55022pt}
@@
 \newcommand{\colcod}[1]{\texttt{\color{purple}#1}}
-
+```
 ```{r include=FALSE}
@@
 validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/).
-The ultimate goal of preference measurement techniques such as (A)CBC or MaxDiff is to predict future behavior [@green1990].
-Therefore, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks.
+
+Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks.
 The easiest way to test this is to include so-called holdout or validation task [@Orme2015].
-Despite the important role of validation tasks, most of the conjoint studies done in practice do not include them [@yang2018], which is unsatisfactory, given the fact that the model is used to estimate market shares which is the basis for relevant marketing decisions.
+Despite the important role of validation tasks, practictioners often do not include them [@yang2018], which is unsatisfactory, given the fact that the model is used to estimate market shares which is the basis for relevant marketing decisions.
 
@@
 validateHOT creates market shares based on *share of preferences* or *first choice rule*, which can be helpful to report results for research articles according to open science standards.
-In addition, it also provides the function \colcod{turf}, which was offered formerly by the turfR package, which is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)).
+In addition, it also provides the function \texttt{\color{purple}turf}, which was offered formerly by the turfR package, which is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)).
 So, currently practitioners and academics mainly have to stick to paid solutions, for example, Sawtooth Software.
@@
 
-After running the Hierarchical Bayes estimation in Sawtooth Software, the raw utility scores should be exported.
-Both the raw utilities and the actual choice in the validation/holdout task needs be read into *R* (please see the vignette for more advice).
 In the following, we provide the workflow for a MaxDiff study (the vignette also provides detailed examples for a CBC as well as an ACBC).
 
-We create the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}).
-Moreover, we also define the method, the actual choice in the validation/holdout task as well as the column indexes of the alternatives in the validation/holdout task.
-Finally, we define variables that we would like to keep in the data frame (\colcod{varskeep}).
-\texttt{\color{purple}createHOT} returns a data frame which we need for subsequent analyses.
+After running the Hierarchical Bayes estimation in Sawtooth Software, the **raw** utility scores have to be exported and afterwards read into *R* including the actual choice in the validation/holdout task.
+
+To define the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}), we use the \texttt{\color{purple}createHOT} function.
+Here, the user can define the attributes as well as the method (in this case \texttt{\color{purple}MaxDiff}).
 
@@
 
-Next, validateHOT also provides the five metrics for the confusion matrix.
+validateHOT also provides the five metrics for the confusion matrix.
 The underlying logic hereby is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
@@
 
-For the following example, let us assume that you conducted an anchored MaxDiff analysis with 10 items (\colcod{opts}) and you want to find the best assortment with a size of 3 (\colcod{size = 3}).
-As a threshold (\colcod{none}) you use the anchor (no-buy alternative).
-Finally, you apply the threshold approach, that is that each alternative with a utility above the threshold (in our case \colcod{none}) is marked as purchase option.
-We reduce the output to the Top 5 combos based on the reach (a \colcod{1} indicates present in this assortment while \colcod{0} means not present).
+For the following example, let us assume that you conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and you want to find the best assortment with a size of 3 (\texttt{\color{purple}size = 3}).
+As a threshold (\texttt{\color{purple}none}) you use the anchor (no-buy alternative).
 
@@
 turf(
-  data = MaxDiff,
-  opts = c(Option_01:Option_10),
-  none = none,
-  size = 3,
-  approach = "thres"
+  data = MaxDiff, # define data
+  opts = c(Option_01:Option_10), # define items
+  none = none, # define threshold variable
+  size = 3, # define size of assortment
+  approach = "thres" # define approach
 ) %>%

### 2023-10-28 paper/paper.Rmd
paper update - 231028

@@
 
-validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/).
+validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/).[^1]
+
+[^1]: validateHOT also works with MaxDiff raw logit utilities, see, for example, @chapman2023.
+For CBC, it should also work with other sofware, as long as all attributes are part-worth coded.
+Linear and piecewise coding is implemented to work with Sawtooth Software.
 
 Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks.
-The easiest way to test this is to include so-called holdout or validation task [@Orme2015].
-Despite the important role of validation tasks, practictioners often do not include them [@yang2018], which is unsatisfactory, given the fact that the model is used to estimate market shares which is the basis for relevant marketing decisions.
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks (i.e., the model has external validity).
+In terms of external validity, we refer to the generalizations to different settings [see, @calder1982, p.240].
+The easiest way to test this is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Despite the important role of validation tasks, practitioners often do not include them [@yang2018].
+Given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions, the current approach is unsatisfactory.
 
-validateHOT combines both validation and market simulation in one package.
-validateHOT's advantages are the following: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is open source tool for functions that are usually implemented in Sawtooth Software and are often a black-box for researchers and practitioners.
+validateHOT combines both validation and market simulation in one package and has three key advantages: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is an open source tool including functions that are usually implemented in paid software, and therefore, remain a black-box for researchers and practitioners.
 
@@
 validateHOT is a practical tool for Sawtooth Software users in industry as well as academia.
-It provides an open source solution for a) validating a validation/holdout task and therefore ensuring that the model has predictive validity; b) running market simulations.
+It provides an open source solution for a) validating a validation/holdout task and therefore ensuring that the model has predictive validity; b) running market simulations (e.g., **T**otal **U**nduplicated **R**each and **F**requency, hereafter TURF).
 Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix (see \autoref{tab:table1}).
-However, to put the Sawtooth export into the right format, the user needs some data wrangling which can be a barrier.
-Other packages mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
-To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations is still missing.
-The goal of validateHOT is still to fill this research gap.
-validateHOT creates market shares based on *share of preferences* or *first choice rule*, which can be helpful to report results for research articles according to open science standards.
-In addition, it also provides the function \texttt{\color{purple}turf}, which was offered formerly by the turfR package, which is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)).
-So, currently practitioners and academics mainly have to stick to paid solutions, for example, Sawtooth Software.
+However, to put the Sawtooth export into the right format, the user needs some data wrangling which could pose a barrier.
+Moreover, packages mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
+To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is still missing.
+validateHOT is especially helpful for researchers who plan to report results for research articles according to open science standards.
+In addition, since the former package turfR is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)), academics and practitioners do not have an alternative function in *R* to run this method.
+Therefore, practitioners and academics mainly have to stick to paid solutions.
 
@@
 
-The main function that creates the validation/holdout task is the \texttt{\color{purple}createHOT} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
+validateHOT's functions can be categorized into four main components, see \autoref{tab:table1}.
+To bring the data into the right format, users can run the \texttt{\color{purple}createHOT} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
 82].
-The other functions in the package mainly focus on four different components which are outlined in \autoref{tab:table1}.
+\colcod{turf} as well as the 2 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT}, and can be run using the raw logit scores.
 
-| Validation metrics | Confusion matrix | Market Simulations | Rescaling scores |
+| Validation metrics | Confusion matrix | Market simulations | Rescaling scores |
 |:----------------:|:----------------:|:----------------:|:----------------:|
@@
 
-After running the Hierarchical Bayes estimation in Sawtooth Software, the **raw** utility scores have to be exported and afterwards read into *R* including the actual choice in the validation/holdout task.
+After running the Hierarchical Bayes estimation in, for example, Sawtooth Software, the **raw** utility scores have to be exported and afterwards read into *R* as a data frame.
+This data frame also has to include the actual choice in the validation/holdout task.
 
 To define the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}), we use the \texttt{\color{purple}createHOT} function.
-Here, the user can define the attributes as well as the method (in this case \texttt{\color{purple}MaxDiff}).
+Here, the user can define the attributes as well as the method (here \texttt{\color{purple}MaxDiff}).
 
@@
 
-Next, to get the relevant validation metrics that are often reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wlömert2014], we only need to provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
+Next, to get the relevant validation metrics that are often reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we only need to provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
 Everything can be implemented in the tidyverse [@tidyverse] logic.
-
-\pagebreak
 
@@
 First, we calculate the market shares based on the multinomial logit model [@McFadden1974].
-Besides the aggregated shares, \texttt{\color{purple}marksim} also provides standard errors and the 95th confidence interval.
+Besides the aggregated shares, \texttt{\color{purple}marksim} also provides standard errors and the 95% confidence interval.
 
@@
   opts = c(Option_1:None),
-  method = "shareofpref"
+  method = "sop"
 )
@@
 \texttt{\color{purple}turf}, a "product line extension model" [@miaoulis1990, p.
-29] is a tool to find the perfect assortment that creates the highest reach and a powerful tool for MaxDiff studies [@chrzan2019, p.
+29], is a tool to find the perfect assortment that creates the highest reach and especially powerful for MaxDiff studies [@chrzan2019, p.
 108].
-To optimize the search for the optimal bundle, we could include as well the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, as well as \texttt{\color{purple}prohib}, to define prohibitions of combinations of items that should not be part of the assortment (please see the vignette for more details and also to see how to apply \texttt{\color{purple}turf} with data obtained by a likert scale).
+To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, as well as \texttt{\color{purple}prohib}, to define prohibitions of combinations of items that should not be part of the assortment (please see the vignette for more details as well as how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
 
-For the following example, let us assume that you conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and you want to find the best assortment with a size of 3 (\texttt{\color{purple}size = 3}).
-As a threshold (\texttt{\color{purple}none}) you use the anchor (no-buy alternative).
+For the following example, let us assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3 (\texttt{\color{purple}size = 3}).
+As a threshold (\texttt{\color{purple}none}), the user uses the anchor (no-buy alternative).
 

### 2023-10-29 README.Rmd
updated createHOT - 231029

@@
   prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each attribute (for linear coded we specify value to be interpolated)
+  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
   interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
   lin.p = 14, # column index of the linear coded variable
-  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
   method = "CBC", # method

### 2023-10-29 R/createHOT.R

@@ -145,9 +145,9 @@
 #'   none = 15,
 #'   prod = 3,
 #'   prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)),
+#'   coding = c(0, 0, 1),
 #'   interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
 #'   lin.p = 14,
-#'   coding = c(0, 0, 1),
 #'   method = "CBC",
 #'   varskeep = 17,
 #'   choice = 16
@@ -167,12 +167,12 @@
 #'   none = 37,
 #'   prod = 6,
 #'   prod.levels = list(prod1, prod2, prod3, prod4, prod5, prod6),
+#'   coding = c(0, 0, 0, 0, 0, 0, 0, 0, 2),
 #'   interpolate.levels = list(c(2.093, 27.287)),
 #'   piece.p = list(
 #'     c(35, 36), c(35, 36), c(35, 36),
 #'     c(35, 36), c(35, 36), c(35, 36)
 #'   ),
-#'   coding = c(0, 0, 0, 0, 0, 0, 0, 0, 2),
 #'   method = "ACBC",
 #'   choice = 38
 #' )
@@ -190,24 +190,26 @@
 #'   none = 39,
 #'   prod = 6,
 #'   prod.levels = list(prod1, prod2, prod3, prod4, prod5, prod6),
-#'   interpolate.levels = list(
-#'     c(3, 5, 8, 10),
-#'     c(1.99, 6.99, 9.99, 10.99, 12.99, 17.99, 25.99)
-#'   ),
+#'   coding = c(0, 1, 0, 0, 0, 0, 0, 0, 2),
+#'   lin.p = 9,
 #'   piece.p = list(
 #'     c(36, 37), c(35, 36), c(35, 36),
 #'     c(33, 34), c(33, 34), c(33, 34)
 #'   ),
-#'   lin.p = 9,
-#'   coding = c(0, 1, 0, 0, 0, 0, 0, 0, 2),
+#'   interpolate.levels = list(
+#'     c(3, 5, 8, 10),
+#'     c(1.99, 6.99, 9.99, 10.99, 12.99, 17.99, 25.99)
+#'   ),
 #'   method = "ACBC",
 #'   choice = 40
 #' )
 #' }
 #' @export
 createHOT <- function(data, id, none = NULL, prod,
-                      prod.levels, interpolate.levels = NULL,
[…]

### 2023-10-29 paper/paper.Rmd
updated paper and vignette - 231029

@@
 [^1]: validateHOT also works with MaxDiff raw logit utilities, see, for example, @chapman2023.
-For CBC, it should also work with other sofware, as long as all attributes are part-worth coded.
+For CBC, it should work with other software, as long as all attributes are part-worth coded.
 Linear and piecewise coding is implemented to work with Sawtooth Software.
@@
 Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and can also predict outside tasks (i.e., the model has external validity).
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.
 In terms of external validity, we refer to the generalizations to different settings [see, @calder1982, p.240].
-The easiest way to test this is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
-Despite the important role of validation tasks, practitioners often do not include them [@yang2018].
-Given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions, the current approach is unsatisfactory.
+The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
 
-validateHOT combines both validation and market simulation in one package and has three key advantages: a) it helps you to decide which is the best model to proceed by validating it, b) it runs relevant market simulations that help to find the right product combinations, and finally, c) it is an open source tool including functions that are usually implemented in paid software, and therefore, remain a black-box for researchers and practitioners.
+validateHOT combines both validation and market simulation in one package and has three key advantages, it a) helps to opt for the best model, b) runs relevant market simulations that help to find the right product combinations, and finally, c) is an open source tool including functions that are usually implemented in paid software, and therefore, remain a black-box for researchers and practitioners.
 
@@
 validateHOT is a practical tool for Sawtooth Software users in industry as well as academia.
-It provides an open source solution for a) validating a validation/holdout task and therefore ensuring that the model has predictive validity; b) running market simulations (e.g., **T**otal **U**nduplicated **R**each and **F**requency, hereafter TURF).
-Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix (see \autoref{tab:table1}).
+It provides an open source solution for a) validating a validation/holdout task and ensuring that the model has predictive validity; b) running market simulations (e.g., **T**otal **U**nduplicated **R**each and **F**requency, hereafter TURF).
+Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
 However, to put the Sawtooth export into the right format, the user needs some data wrangling which could pose a barrier.
-Moreover, packages mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
-To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is still missing.
+Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
+To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
 validateHOT is especially helpful for researchers who plan to report results for research articles according to open science standards.
-In addition, since the former package turfR is no longer available on the Comprehensive R Archive Network (see [CRAN](https://cran.r-project.org/web/packages/turfR/index.html)), academics and practitioners do not have an alternative function in *R* to run this method.
-Therefore, practitioners and academics mainly have to stick to paid solutions.
 
@@
 
-After running the Hierarchical Bayes estimation in, for example, Sawtooth Software, the **raw** utility scores have to be exported and afterwards read into *R* as a data frame.
-This data frame also has to include the actual choice in the validation/holdout task.
+After running the Hierarchical Bayes estimation, the **raw** utility scores have to be exported and read into an *R* data frame.
+This data frame has to include the actual choice in the validation/holdout task.
 
 To define the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}), we use the \texttt{\color{purple}createHOT} function.
-Here, the user can define the attributes as well as the method (here \texttt{\color{purple}MaxDiff}).
 
 ```{r}
-data("MaxDiff") # read in the data
+# load data
+data("MaxDiff")
+
+# create holdout task and define relevant column indexes
 HOT <- createHOT(
-  data = MaxDiff, # data frame
-  id = 1, # index unique identifier
-  none = 19, # index of none alternative
+  data = MaxDiff, 
+  id = 1, 
+  none = 19, 
   prod = 7, # no of alternatives in HOT excluding none
   prod.levels = list(3, 10, 11, 15, 16, 17, 18), # index of alternatives
-  method = "MaxDiff", # method applied
-  choice = 20, # column index of choice alternative
+  method = "MaxDiff", 
+  choice = 20, 
   varskeep = 21
@@
 
-Next, to get the relevant validation metrics that are often reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we only need to provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
-Everything can be implemented in the tidyverse [@tidyverse] logic.
+To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}), which can be implemented using the tidyverse [@tidyverse] logic.
 
 ```{r}
+# test hit rate of holdout task
 hitrate(
-  data = HOT, # data frame
-  opts = c(Option_1:None), # column names of alternatives
-  choice = choice # column name of choice
+  data = HOT, 
+  opts = c(Option_1:None), 
+  choice = choice 
 ) %>%
@@
 
-validateHOT also provides the five metrics for the confusion matrix.
-The underlying logic hereby is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
-validateHOT calculates, for example, how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (exemplary showed by applying the \texttt{\color{purple}accuracy} function and results split by \texttt{\color{purple}Group}).
+The underlying logic of the confusion matrix is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
+validateHOT calculates how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (here by applying \texttt{\color{purple}accuracy}).
 
 ```{r}
+# test accuracy of holdout task
 accuracy(
-  data = HOT, # data frame
-  group = Group, # optional grouping variable
-  opts = c(Option_1:None), # column names of alternatives
-  choice = choice, # column name of choice
-  none = None # column name
+  data = HOT, 
+  group = Group, 
+  opts = c(Option_1:None), 
+  choice = choice, 
+  none = None 
 )
@@
 
-Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim} as well as \texttt{\color{purple}turf}.
-First, we calculate the market shares based on the multinomial logit model [@McFadden1974].
-Besides the aggregated shares, \texttt{\color{purple}marksim} also provides standard errors and the 95% confidence interval.
+Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim} and \texttt{\color{purple}turf}.
+In the following example, the market share is calculated accordning to the multinomial logit model [@McFadden1974].
 
 ```{r}
+# run market simulations (share of preference rule)
 marksim(
@@
 
-\texttt{\color{purple}turf}, a "product line extension model" [@miaoulis1990, p.
-29], is a tool to find the perfect assortment that creates the highest reach and especially powerful for MaxDiff studies [@chrzan2019, p.
+Finally, \texttt{\color{purple}turf}, a "product line extension model" [@miaoulis1990, p.
+29], is a tool to find the perfect assortment that creates the highest reach and is especially powerful for MaxDiff studies [@chrzan2019, p.
 108].
-To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, as well as \texttt{\color{purple}prohib}, to define prohibitions of combinations of items that should not be part of the assortment (please see the vignette for more details as well as how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
+To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibt certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
 
-For the following example, let us assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3 (\texttt{\color{purple}size = 3}).
+For the following example, we assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3.
 As a threshold (\texttt{\color{purple}none}), the user uses the anchor (no-buy alternative).
@@
 turf(
-  data = MaxDiff, # define data
-  opts = c(Option_01:Option_10), # define items
-  none = none, # define threshold variable
-  size = 3, # define size of assortment
-  approach = "thres" # define approach
+  data = MaxDiff, 
+  opts = c(Option_01:Option_10),
+  none = none, 
+  size = 3, 
+  approach = "thres" 
 ) %>%

### 2023-10-29 R/createHOT.R

@@ -276,6 +276,14 @@ createHOT <- function(data, id, none = NULL, prod,
     )
   }
 
+  if (!is.null(coding)){
+    for (i in 1:prod){
+      if (base::length(prod.levels[[i]]) != length(coding)) {
+        stop("Error: 'coding' and number of attributes must have the same length!")
+      }
+    }
+  }
+
   # test whether CBC is specified and no coding equal to 2
   if (method == "CBC" & base::any(coding == 2)) {
     base::stop("Error: Piecewise coding not possible for ", method, "!")

### 2023-11-10 R/zc_diffs.R
updated functions and also created zc diffs - 231110

@@ -1,4 +1,4 @@
-#' Attribute Importance for (A)CBC
+#' Zero-Centered Diffs for (A)CBC
 #'
 #' @param data A data frame with all relevant variables.
 #' @param group Optional column name(s) to specify grouping variable(s).
@@ -9,12 +9,14 @@
 #' be interpolated. These have to be the same as provided to Sawtooth Software.
 #' Please make sure to provide the whole list. Only has to be specified for the
 #' variables that are coded as '1' (linear).
-#' @param res A vector indicating whether individual shares (\code{ind}) or
-#' aggregated (\code{agg}) shares should be returned.
+#' @param res A vector indicating whether individual zero-centered diffs (\code{ind}) or
+#' aggregated (\code{agg}) zero-centered diffs should be returned.
+#' @param none A vector whether \code{none} option was included.
 #'
 #' @details
-#' \code{att_imp} converts raw utilities of a CBC or an ACBC to relative importance
-#' scores (see, Orme, 2020, p. 80, for more information).
+#' \code{zc_diffs} converts raw utilities of a CBC or an ACBC to
+#' zero-centered diffs (Orme, 2020, p. 78). This allows for comparison between
+#' the attributes.
 #'
 #' \code{data} has to be a data frame with the attributes. Attribute levels need
 #' to be the raw utilities.
@@ -39,11 +41,14 @@
 #' or across \code{group} (\code{res} needs to be set to {agg}) or if it scores
 #' should be converted for individuals only
 #'
+#' \code{none} specifies whether none option was included or not, if yes,
+#' column name or column index of \code{none} needs to be specified. If no
+#' \code{none} option was included, leave it empty.
 #'
 #'
 #' @seealso {
+#' \code{\link[=att_imp]{att_imp}} for attribute importance scores for (A)CBC
 #' \code{\link[=prob_scores]{prob_scores}} for probability scores for MaxDiff
-#' \code{\link[=zc_diffs]{zc_diffs}} for zero-center diff scores for (A)CBC
 #' }
 #'
 #' @references {
@@ -57,17 +62,18 @@
 #'
 #' @examples
 #' \dontrun{
-#' att_imp(
+#' zc_diffs(
 #'   data = CBC,
 #'   attrib = list(
[…]

### 2023-11-11 README.Rmd
updated package - 231111 including markdown

--- 2023-10-21 README.Rmd
@@
 [![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
+
 <!-- badges: end -->
@@
 The goal of `validateHOT` is to validate the results of your validation
-task (also known as holdout task) as well as a tool for simulating markets with
-the results of your MaxDiff, CBC, and ACBC. 
-This package is especially relevant for the [Sawtooth Software](https://sawtoothsoftware.com/) community who would like to report their analysis in *R* for open science purposes. Of course,
-this package is also useful for practitioners, who would like to run the analyses
-in an open source software.
-The ultimate goal of these preference measurement techniques is to predict 
-future behavior (Green & Srinivasan, 1990). Therefore, it is essential for 
-both academics and practitioners to ensure that the collected data is valid 
-and can also predict outside tasks that were not included in the estimation of 
-the utility scores.
+task (also known as holdout task) as well as a tool for simulating
+markets with the results of your MaxDiff, CBC, and ACBC. This package is
+especially relevant for the [Sawtooth
+Software](https://sawtoothsoftware.com/) community who would like to
+report their analysis in *R* for open science purposes. However, it also
+works perfectly with the great package `ChoiceModelR`(Sermas, 2022). Of
+course, this package is also useful for practitioners, who would like to
+run the analyses in an open source software. The ultimate goal of these
+preference measurement techniques is to predict future behavior (Green &
+Srinivasan, 1990). Therefore, it is essential for both academics and
+practitioners to ensure that the collected data is valid and can also
+predict outside tasks that were not included in the estimation of the
+utility scores.
 
-Although commercial studies often do not include a validation/holdout task (Yang et al., 2018), it is highly recommended to do so
-(Orme, 2015; Rao, 2014). This validation/holdout task does not only
-help to check whether everything went right during data collection but
-also to determine the final model. `validatHOT` provides
-some of the relevant metrics to test the performance of the data in
-predicting a validation/holdout task.
+Although commercial studies often do not include a validation/holdout
+task (Yang et al., 2018), it is highly recommended to do so (Orme, 2015;
+Rao, 2014). This validation/holdout task does not only help to check
+whether everything went right during data collection but also to
+determine the final model. `validatHOT` provides some of the relevant
+metrics to test the performance of the data in predicting a
+validation/holdout task.
 
-Moreover, another key goal of preference measurement techniques is to simulate 
-or predict markets (Gilbride, Lenk, & Brazell, 2008). `validateHOT` provides key functions for an easy implementation to simulate markets for both (A)CBC and MaxDiff.
+Moreover, another key goal of preference measurement techniques is to
+simulate or predict markets (Gilbride, Lenk, & Brazell, 2008).
+`validateHOT` provides key functions for an easy implementation to
+simulate markets for both (A)CBC and MaxDiff.
 
-> `validateHOT` was developed to work with Sawtooth Software. Please be cautious about using it with different platforms (especially for linear and piecewise-coded variables).
+> `validateHOT` was developed to work with Sawtooth Software and
+> `ChoiceModelR`. Please be cautious about using it with different
+> platforms (especially for linear and piecewise-coded variables).
 
@@
 and running your initial Hierarchical Bayes models, you can turn to
-`validateHOT` and test how good your model predicts choices
-in the validation/holdout task. Therefore, you only have to read in your
-raw utility scores as well as the actual choice of your validation/
-holdout task. You can use the `merge()` function provided by the *R* base package to do so (R Core Team, 2023). Afterward, you can read in your data
-file and enjoy `validateHOT`. We provide a short tutorial in the markdown, for a more detailed tutorial, please see the vignette that comes along with `validateHOT`.
+`validateHOT` and test how good your model predicts choices in the
+validation/holdout task. Therefore, you only have to read in your raw
+utility scores as well as the actual choice of your validation/ holdout
+task. You can use the `merge()` function provided by the *R* base
+package to do so (R Core Team, 2023). Afterward, you can read in your
+data file and enjoy `validateHOT`. We provide a short tutorial in the
+markdown, for a more detailed tutorial, please see the vignette that
+comes along with `validateHOT`.
 
-👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT`
-provides functions for 3 key areas:
+👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT` provides
+functions for 4 key areas:
 
@@
 
+<li>converting raw logit utilities in scores that are easier to
+interpret</li>
+
 </ul>
 
-For all 3 key areas, the `createHOT()` function is essential.
-This function creates the total utilities for each alternative in the
+For all 4 key areas, the `createHOT()` function is essential. This
+function creates the total utilities for each alternative in the
 validation/holdout task and also in the simulation method, respectively.
@@
 total utility of a profile or conjoint model is the sum of its attribute
-levels. `createHOT()` will calculate the total utility of each alternative you specify.
-
-> We are planning to expand the functions of the package by also providing functions to convert the raw utilities into scores that are easier to interpretate, for example, `prob_scores()` to calculate choice probabilities of both unanchored and anchored MaxDiff or `att_imp()` to calculate the importance of the attributes included in an ACBC or CBC.
+levels. `createHOT()` will calculate the total utility of each
+alternative you specify.
 
@@
 <li><code>hitrate()</code>: creates the Hit Rate (correctly predicted
-choices) of your validation/holdout task. The output will contain 
-the percentage of how many choices were correctly predicted, 
-the chance level in your validation task ($\frac{1}{alternatives}$) in percentage,
-the number of correctly predicted participants' choices as well as the number of observations. 
-</li>
+choices) of your validation/holdout task. The output will contain the
+percentage of how many choices were correctly predicted, the chance
+level in your validation task ($\frac{1}{alternatives}$) in percentage,
+the number of correctly predicted participants' choices as well as the
+number of observations.</li>
 
@@
 divergence between the actual choice distribution and the predicted
-choice distribution (Ding et al., 2011; Drost, 2018). Output provides both
-divergence between predicted from observed and observed from predicted
-due to the asymmetry of the Kullback-Leibler divergence. If you specify
-an optional <code>group</code> argument the output is split by
-groups. Currently, you can choose between \eqn{log} and \eqn{log{_2}} as logarithm base.
-The default is set to \eqn{log}.</li>
+choice distribution (Ding et al., 2011; Drost, 2018). Output provides
+both divergence between predicted from observed and observed from
+predicted due to the asymmetry of the Kullback-Leibler divergence. If
+you specify an optional <code>group</code> argument the output is split
+by groups. Currently, you can choose between \eqn{log} and \eqn{log{_2}}
+as logarithm base. The default is set to \eqn{log}.</li>
 
-<li><code>mae()</code>: calculates the mean absolute error, i.e., deviation between
-predicted and stated choice share. </li>
+<li><code>mae()</code>: calculates the mean absolute error, i.e.,
+deviation between predicted and stated choice share.</li>
 
-<li><code>medae()</code>: calculates the median absolute error, which is less affected
-by outliers compared to the mean absolute error.</li>
+<li><code>medae()</code>: calculates the median absolute error, which is
+less affected by outliers compared to the mean absolute error.</li>
 
-<li><code>mhp()</code>: calculates the averaged hit probability of participant's actual
-choice in the validation/holdout task.</li>
+<li><code>mhp()</code>: calculates the averaged hit probability of
+participant's actual choice in the validation/holdout task.</li>
 
-<li><code>rmse()</code>: provides the root-mean-squared error of deviation
-between predicted and stated choice share.</li>
+<li><code>rmse()</code>: provides the root-mean-squared error of
+deviation between predicted and stated choice share.</li>
 
@@
 
-All functions can be extended with the `group` argument to get 
-output split by group(s).
+All functions can be extended with the `group` argument to get output
+split by group(s).
 
@@
 matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
-currently have to include a **none** alternative in your validation/holdout 
-task. We currently predict, e.g., whether a buy or no-buy was correctly 
-predicted. Information could be used for overestimating and underestimating,
-respectively, of product purchases. In the following <code>TP</code>
-stands for true positives, <code>FP</code> for false positives,
-<code>TN</code> for true negatives, and <code>FN</code> for false
-negatives (Burger, 2018). 
-To translate this to the `validateHOT` logic, imagine you have a 
-validation/holdout task with 5 alternatives plus the alternative not to buy 
-any of those chosen. `validateHOT` now measures whether or not a buy 
-(participant opts for one of the 5 alternatives) or a no-buy (participant opts
-for the no-buy alternative), respectively, is correctly predicted.
+currently have to include a **none** alternative in your
+validation/holdout task. We currently predict, e.g., whether a buy or
+no-buy was correctly predicted. Information could be used for
+overestimating and underestimating, respectively, of product purchases.
+In the following <code>TP</code> stands for true positives,
+<code>FP</code> for false positives, <code>TN</code> for true negatives,
+and <code>FN</code> for false negatives (Burger, 2018). To translate
+this to the `validateHOT` logic, imagine you have a validation/holdout
+task with 5 alternatives plus the alternative not to buy any of those
+chosen. `validateHOT` now measures whether or not a buy (participant
+opts for one of the 5 alternatives) or a no-buy (participant opts for
+the no-buy alternative), respectively, is correctly predicted.
+
+Please be aware that for coding, `validateHOT` applies the following
+coding of the *buy* and *no-buy* alternatives. Rows refer to the
+observed decisions while columns refer to the predicted ones.
+
+|        |     |        |
+|--------|:---:|:------:|
+|        | Buy | No-buy |
+| Buy    | TP  |   FN   |
+| No-buy | FP  |   TN   |
 
@@
 
-<li><code>accuracy()</code>: calculates the number of correctly predicted choices (buy or no-buy);
-$\frac{TP + TN}{TP + TN + FP + FN}$ (Burger, 2018). 
-</li>
+<li><code>accuracy()</code>: calculates the number of correctly
+predicted choices (buy or no-buy); $\frac{TP + TN}{TP + TN + FP + FN}$
+(Burger, 2018).</li>
 
@@
 
-<li><code>precision()</code>: defined as $\frac{TP}{TP + FP}$ (Burger, 2018).</li>
+<li><code>precision()</code>: defined as $\frac{TP}{TP + FP}$ (Burger,
+2018).</li>
 
-<li><code>recall()</code>: defined as $\frac{TP}{TP + FN}$ (Burger, 2018).</li>
+<li><code>recall()</code>: defined as $\frac{TP}{TP + FN}$ (Burger,
+2018).</li>
 
-<li><code>specificity()</code>: defined as $\frac{TN}{TN + FP}$ (Burger, 2018).</li>
+<li><code>specificity()</code>: defined as $\frac{TN}{TN + FP}$ (Burger,
+2018).</li>
 
@@
 
-Again, all functions can be extended with the `group` argument to get output 
-split by group(s).
+Again, all functions can be extended with the `group` argument to get
+output split by group(s).
 
@@
 
-<li><code>turf()</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p.
-29) that helps to find the perfect product bundle based on the reach (e.g., how many participants consider buying at least one product of that assortment) and the frequency (how many products are on average a purchase option).
-<code>turf()</code> currently provides both the *threshold*  approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p.
-112) and the *first choice* approach (<code>approach = 'thres'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p.
-111).</li>
+<li><code>turf()</code>: <b>T</b>(otal) <b>U</b>(nduplicated)
+<b>R</b>(each) and <b>F</b>(requency) is a "product line extension
+model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect
+product bundle based on the reach (e.g., how many participants consider
+buying at least one product of that assortment) and the frequency (how
+many products are on average a purchase option). <code>turf()</code>
+currently provides both the *threshold* approach (<code>approach =
+'thres'</code>; all products that exceed a threshold are considered,
+e.g., as purchase option; Chrzan & Orme, 2019, p. 112) and the *first
+choice* approach (<code>approach = 'thres'</code>; only product with
+highest utility is considered as purchase option; Chrzan & Orme, 2019,
+p. 111).</li>
 
-<li><code>freqassort()</code>: Similar to <code>turf()</code>, <code>freqassort()</code>
-will give you the averaged frequency, how many products the participants
-will choose from your in the function determined potential assortment. 
-Again, you have to define a <code>none</code> alternative, because <code>freqassort()</code> uses 
-the <i>threshold</i> approach, meaning if the utility of one product is above 
-the utility of <code>none</code>, it is marked as potential purchase option. 
-While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, 
-you specify the combination you are interested in <code>freqassort()</code>.</li>
+<li><code>freqassort()</code>: Similar to <code>turf()</code>,
+<code>freqassort()</code> will give you the averaged frequency, how many
+products the participants will choose from your in the function
+determined potential assortment. Again, you have to define a
+<code>none</code> alternative, because <code>freqassort()</code> uses
+the <i>threshold</i> approach, meaning if the utility of one product is
+above the utility of <code>none</code>, it is marked as potential
+purchase option. While <code>turf()</code> calculates the reach and
+frequency for <b>all</b> combinations, you specify the combination you
+are interested in <code>freqassort()</code>.</li>
 
-<li><code>reach()</code>: Similar to <code>turf()</code>, <code>reach()</code> will
-give you the averaged percentage of how many participants you can reach
-(at least one of the products resemble a purchase option) with your in the function determined
-potential assortment.
-<code>reach()</code> also uses the <i>threshold</i> approach (see above).
-While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach()</code>.</li>
+<li><code>reach()</code>: Similar to <code>turf()</code>,
+<code>reach()</code> will give you the averaged percentage of how many
+participants you can reach (at least one of the products resemble a
+purchase option) with your in the function determined potential
+assortment. <code>reach()</code> also uses the <i>threshold</i> approach
+(see above). While <code>turf()</code> calculates the reach and
+frequency for <b>all</b> combinations, you specify the combination you
+are interested in <code>reach()</code>.</li>
 
-<li><code>marksim()</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
-calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>
+<li><code>marksim()</code>: runs market simulations (either share of
+preference or first choice rule), including the standard error, as well
+as the lower and upper confidence interval, which is calculated
+according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p.
+94).</li>
 
@@
 
-> <b>Important</b>: For both <code>reach()</code> and <code>freqassort()</code>, <code>noen</code> does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.
+> <b>Important</b>: For both <code>reach()</code> and
+> <code>freqassort()</code>, <code>none</code> does not necessarily have
+> to be the no-buy alternative but can be another alternative that
+> should be exceeded.
+
+### Reestimating raw utilities
+
+<code>validateHOT</code> also provides 3 functions to better interpret
+the scores of both (A)CBC and MaxDiff. Currently, 3 functions are
+provided, namely:
+
+<ul>
+
+<li><code>att_imp()</code>: converts the raw utilities of either an ACBC
+or CBC into importance scores for each attribute (see, Orme, 2020, pp.
+79-81)</li>
+
+<li>
+
+<code>prob_scores()</code>converts the raw utilities of a MaxDiff to
+choice probabilities by applying the following procedures:
+
+<ul>
+
+<li>For unanchored MaxDiff: First, the scores are zero-centered,
+afterwards they are transformed by the following formula
+$\frac{exp^{U_i}}{(exp^{U_i} + a - 1)}$ (Chrzan & Orme, 2019, p. 56),
+where $U_i$ is the raw utility of item *i* and <code>a</code> is the
+number of items shown simultaneously per MaxDiff task. Finally, the
+scores are normalized.</li>
+
+<li>For anchored MaxDiff:
+$\frac{exp^{U_i}}{(exp^{U_i} + a - 1)} * 100 * \frac{1}{a}$ (Chrzan &
+Orme, 2019, p. 59).</li>
+
+</ul>
+
+</li>
+
+<li><code>zc_diffs()</code>: rescales the raw logit utilities to make
+them comparable across participants (Sawtooth Software Inc, 2023, p.
+343).</li>
+
+</ul>
 
@@
 
-`validaeHOT` provides 5 data sets that come with the package. These datasets 
-should help to better understand the way the data needs to be defined, 
-especially for the `createHOT()` function.
+`validaeHOT` provides 5 data sets that come with the package. These data
+sets should help to better understand the way the data needs to be
+defined, especially for the `createHOT()` function.
 
@@
 
-<li><code>CBC</code>: Example data set with raw utilities of a CBC
-study conducted in Sawtooth. All attributes were coded as
-part-worth.</li>
+<li><code>CBC</code>: Example data set with raw utilities of a CBC study
+conducted in Sawtooth. All attributes were coded as part-worth.</li>
 
@@
 We are teaching a preference measurement seminar for students. Often
-these students did not have any prior experience (or only sparsely) with *R*.
-One of the chapters in this class is about model validating the results obtained and we teach this,
-of course, in *R*. We want to put a strong emphasis on open science and providing tools to run the analyses and provide the code afterwards is essential.
+these students did not have any prior experience (or only sparsely) with
+*R*. One of the chapters in this class is about model validating the
+results obtained and we teach this, of course, in *R*. We want to put a
+strong emphasis on open science and providing tools to run the analyses
+and provide the code afterwards is essential.
 
-Of course, there are other great packages which are faster in running (i.e., `Metrics` by Hamner & Frasco, 2018), however, these packages need some more data wrangling in order to use the
-appropriate functions with the raw utilities, which might be a burden or barrier for one or
-the other.
+Of course, there are other great packages which are faster in running
+(i.e., `Metrics` by Hamner & Frasco, 2018), however, these packages need
+some more data wrangling in order to use the appropriate functions with
+the raw utilities, which might be a burden or barrier for one or the
+other.
 
-Moreover, as Yang et al. (2018) report, commercial studies often do not use
-any validation task. Again, the missing experience in *R* could be one explanation. 
-Since these functions are not always implemented in other software, this might be one reason why
-they do not include one simply because they do not know how to use it
-correctly. Having a package to evaluate the validation/holdout task can
-also be beneficial from this perspective.
+Moreover, as Yang et al. (2018) report, commercial studies often do not
+use any validation task. Again, the missing experience in *R* could be
+one explanation. Since these functions are not always implemented in
+other software, this might be one reason why they do not include one
+simply because they do not know how to use it correctly. Having a
+package to evaluate the validation/holdout task can also be beneficial
+from this perspective.
 
@@
 *CBC* where all of the attributes are part-worth coded, so we need no
-interpolation. Let us load the `CBC` data frame for this
-example.
+interpolation. Let us load the `CBC` data frame for this example.
 
@@
 
-The data frame has a total of `r nrow(CBC)` participants and `r ncol(CBC)` columns.
+The data frame has a total of `r nrow(CBC)` participants and
+`r ncol(CBC)` columns.
 
-Now imagine you included a validation/holdout task with three
-alternatives plus a no-buy alternative.
-We specify the `data` argument and the column index of `id`.
-Since we also have a *no-buy* alternative in our validation task, we next specify the `none` argument, otherwise we would have left it empty.
-Afterwards, we specify the number of alternatives (`prod`) in our validation/holdout task (excluding the *no-buy* alternative).
-Next, we define each alternative with the argument `prod.levels`.
-If we look back at the data frame, we can see that the first alternative in the holdout task (`c(4, 9, 19)`) is composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and `Att3_Lev5`.
+Now imagine you included a validation/holdout task with 3 alternatives
+plus a no-buy alternative. We specify the `data` argument and as well as
+the `id`. Since we also have a *no-buy* alternative in our validation
+task, we next specify the `none` argument, otherwise we would have left
+it empty. Afterwards, we define each alternative with the argument
+`prod.levels`. If we look back at the data frame, we can see that the
+first alternative in the holdout task (`c(4, 9, 19)`) is composed of the
+following attribute levels `Att1_Lev1`, `Att2_Lev1`, and `Att3_Lev5`.
 
-As mentioned above, all the attributes are part-worth coded, therefore, we set `coding = c(0, 0, 0)`.
-Finally, we specify the method, which is `method = "CBC"` in our case, and define the column index of the actual participant's choice (`choice`).
-If you run the code, a data frame called `HOT` (short form of **H**old**o**ut **t**ask) will be returned to the global environment.
+As mentioned above, all the attributes are part-worth coded, therefore,
+we set `coding = c(0, 0, 0)`. Finally, we specify the method, which is
+`method = "CBC"` in our case, and define the column index of the actual
+participant's choice (`choice`). If you run the code, a data frame
+called `HOT` (short form of **H**old**o**ut **t**ask) will be returned
+to the global environment.
 
-> &#10071; `createHOT()` is currently just taking indexes instead of column names, please be aware of this.
-However, you can easily find out the index by either using the `names()` function to see all names of the dataframe, or if you already know the name of the variable, you can use `which()` and `colnames()`, both functions are provided by the base package (R Core Team, 2023).
-For example, if you want to find out the column index of `ID`, you could run `which(colnames(CBC) == "ID")` to determine the column index of `ID`.
+> ❗ `createHOT()` takes both column names and column indexes. However,
+> please be aware, if you include linear coding or piecewise coding, you
+> **have** to provide the column indexes for the input in prod.levels.,
+> please be aware of this. However, you can easily find out the index by
+> either using the `names()` function to see all names of the data
+> frame, or if you already know the name of the variable, you can use
+> `which()` and `colnames()`, both functions are provided by the base
+> package (R Core Team, 2023). For example, if you want to find out the
+> column index of `ID`, you could run `which(colnames(CBC) == "ID")` to
+> determine the column index of `ID`.
 
@@
 HOT <- createHOT(
-  data = CBC, # data frame
-  id = 1, # column index of the id
-  none = 21, # column index of none alternative
-  prod = 3, # number of alternatives in validation task (excluding none)
-  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)), # column index of the attribute levels for each attribute
-  coding = c(0, 0, 0), # how the attributes were coded
-  method = "CBC", # method
-  choice = 22 # column index of choice
+  data = CBC,
+  id = "ID",
+  none = 21,
+  prod.levels = list(c("Att1_Lev1", "Att2_Lev1", "Att3_Lev5"), c(8, 12, 17), c(5, 10, 17)),
+  coding = c(0, 0, 0),
+  method = "CBC",
+  choice = "HOT"
 )
@@
 
-Let us take a glimpse at the output, which shows the participants' total raw utilities for each of the 3 alternatives that were included in the validation/holdout task.
+Let us take a glimpse at the output, which shows the participants' total
+raw utilities for each of the 3 alternatives that were included in the
+validation/holdout task.
 
@@
 
-In the next step, we would like to see how well our model (from which we took the raw utilities) predicts 
-the actual choices in the validation/holdout task. First, we will run the `hitrate()` function. 
-We specify the `data`, the column names of the alternatives (`opts`; remember 
-there are three alternatives + the *no-buy* alternative), and finally the actual choice (`choice`).
+In the next step, we would like to see how well our model (from which we
+took the raw utilities) predicts the actual choices in the
+validation/holdout task. First, we will run the `hitrate()` function. We
+specify the `data`, the column names of the alternatives (`opts`;
+remember there are 3 alternatives + the *no-buy* alternative), and
+finally the actual choice (`choice`).
 
@@
 
-Next, we look at the magnitude of the mean absolute error by running the `mae()` function. The arguments are the same as for the `hitrate()` function.
+Next, we look at the magnitude of the mean absolute error by running the
+`mae()` function. The arguments are the same as for the `hitrate()`
+function.
 
@@
 
-To cover also one example on how to use the metrics of the confusion matrix, we could test whether our model overestimates the purchase behavior (our model predicts a *buy* although participant opts for a *no-buy*) or underestimates it (i.e., model predicts *no-buy* but participant opts for a *buy*).
-We will test the accuracy of the model by running the `accuracy()` function.
+To cover also one example on how to use the metrics of the confusion
+matrix, we could test whether our model overestimates the purchase
+behavior (our model predicts a *buy* although participant opts for a
+*no-buy*) or underestimates it (i.e., model predicts *no-buy* but
+participant opts for a *buy*). We will test the accuracy of the model by
+running the `accuracy()` function.
 
@@
 
-Finally, let us test, how many participants would at least buy one of the 3 products, assuming that this is one potential assortment we would like to offer to our consumers.
-We will use the `reach()` function.
-To specify the bundles we are offering we use the `opts` argument in our function.
+Finally, let us test, how many participants would at least buy one of
+the 3 products, assuming that this is one potential assortment we would
+like to offer to our consumers. We will use the `reach()` function. To
+specify the bundles we are offering we use the `opts` argument in our
+function.
 
@@
 
-In a second example, we again use a *CBC*, however, this time we show how to use `validateHOT` if one of the variables are linear coded. All other examples are provided in the accompanied vignette.
+In a second example, we again use a *CBC*, however, this time we show
+how to use `validateHOT` if one of the variables are linear coded. All
+other examples are provided in the accompanied vignette.
 
-We are using the data frame `CBC_lin`. Again, we first load the data frame.
+We are using the data frame `CBC_lin`. Again, we first load the data
+frame.
 
@@
 
-Next, we create the validation/holdout task to evaluate it in the next step.
-We use a validation/holdout task with three alternatives plus the *no-buy* alternative, just as we did in the previous example.
-The only difference to the previous example is that for our model estimation, the third attribute (`Att3_Lin`) was coded as linear.
+Next, we create the validation/holdout task to evaluate it in the next
+step. We use a validation/holdout task with 3 alternatives plus the
+*no-buy* alternative, just as we did in the previous example. The only
+difference to the previous example is that for our model estimation, the
+third attribute (`Att3_Lin`) was coded as linear.
 
-Again, we first define data.
-The `id` is saved in the first column.
-The utilities for the `none` parameter are stored in the 15th column, and we again set `prod` to 3 (**excluding** the *no-buy* alternative).
-Next, we define the `prod.levels` for each alternative.
-For example, we can see that the second alternative is composed of `Att1_Lev5`, `Att2_Lev4`, and `60` which is the value that should be interpolated.
-We tell `createHOT()` that this value needs to be interpolated by specifying the `coding` argument.
-This tells us that the first two attributes (`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are part-worth coded (`0`) while the third attribute is linear coded (`1`).
+Again, we first define data, namely the `id` as well as the `none`
+alternative. Next, we define the `prod.levels` for each alternative.
+Since we have one linear coded attribute, we have to specify the column
+indexes instead of the column names. For example, for the second
+alternative which is composed of `Att1_Lev5`, `Att2_Lev4`, and `60`
+which is the value that should be interpolated. We tell `createHOT()`
+that this value needs to be interpolated by specifying the `coding`
+argument. This tells us that the first two attributes (`Att1_Lev5`,
+`Att2_Lev4` in the case of alternative 2) are part-worth coded (`0`)
+while the third attribute is linear coded (`1`).
 
-To interpolate the value, we have to provide `createHOT()` the `interpolate.levels`.
-These **need** to be the same as provided to Sawtooth as levels.
-Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of `interpolate.levels`.
-In our case, we had 7 levels that range from 10 to 70.
+To interpolate the value, we have to provide `createHOT()` the
+`interpolate.levels`. These **need** to be the same as provided to
+Sawtooth or `ChoiceModelR` as levels. Moreover, it is important that the
+value that should be interpolated needs to lie within the lower and
+upper bound of `interpolate.levels`. In our case, we had 7 levels that
+range from 10 to 70.
 
-Next, we define the column index of the linear coded variable (`lin.p`) and specify the `coding` we talked about above.
-Again, we are running a *CBC* specified by the `method` argument.
-This time, we would like to keep some of the variables in the data frame, which we specify in `varskeep`.
-We only keep one further variable, however, you can specify as many as you want.
-This could be relevant if you would like to display results per group.
-Finally, we just tell `createHOT()` the column index of the final choice (`choice`) and we are all set.
+Next, we define the column index of the linear coded variable (`lin.p`)
+and specify the `coding` we talked about above. Again, we are running a
+*CBC* specified by the `method` argument. This time, we would like to
+keep some of the variables in the data frame, which we specify in
+`varskeep`. We only keep one further variable, however, you can specify
+as many as you want. This could be relevant if you would like to display
+results per group. Finally, we define the actual choice (`choice`) in
+the holdout/validation task and we are all set.
 
@@
   data = CBC_lin, # data frame
-  id = 1, # column index of the id
-  none = 15, # column index of none alternative
-  prod = 3, # number of alternatives in validation task (excluding none)
-  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each attribute (for linear coded we specify value to be interpolated)
-  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
-  lin.p = 14, # column index of the linear coded variable
-  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
-  method = "CBC", # method
-  varskeep = 17, # column index of variables that should be kept in the dataframe
-  choice = 16 # column index of choice
+  id = 1,
+  none = 15,
+  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)),
+  coding = c(0, 0, 1),
+  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
+  lin.p = 14,
+  method = "CBC",
+  varskeep = "Group",
+  choice = "HOT"
 )
@@
 
-The next steps are the same as above.
-However, let us take a look at some examples in which we display the results per group.
-Let us again begin with the `hitrate()` function.
-To do so, we specify the column name of the grouping variable in the `group` argument.
+The next steps are the same as above. However, let us take a look at
+some examples in which we display the results per group. Let us again
+begin with the `hitrate()` function. To do so, we specify the column
+name of the grouping variable in the `group` argument.
 
@@
 In this case, the group assignment is stored in form of integers.
-However, the output is the same if it is a factor or if it is labelled data.
-To proof this we just quickly change `group` into a factor by using the `factor()` function provided by the *R*  Core Team (2023).
+However, the output is the same if it is a factor or if it is labelled
+data. To proof this we just quickly change `group` into a factor by
+using the `factor()` function provided by the *R* Core Team (2023).
 
@@
 
-Afterward, we display the *mean hit probability* by running the `mhp()` function.
+Afterward, we display the *mean hit probability* by running the `mhp()`
+function.
 
@@
 
-Burger, Scott V. 2018. <em>Introduction to Machine Learning with R: Rigorous Mathematical Analysis</em>. O'Reilly.
+Burger, Scott V. 2018. <em>Introduction to Machine Learning with R:
+Rigorous Mathematical Analysis</em>. O'Reilly.
 
-Chrzan, K., & Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
+Chrzan, K., & Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner's
+Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
 
-Ding, Min, John R.
-Hauser, Songting Dong, Daria Dzyabura, Zhilin Yang, SU Chenting, and Steven P.
-Gaskin.
-2011.
-“Unstructured Direct Elicitation of Decision Rules.” <em>Journal of Marketing Research 48</em>(1): 116-27.
-[https://doi.org/10.1509/jmkr.48.1.116](https://doi.org/10.1509/jmkr.48.1.116)
+Ding, Min, John R. Hauser, Songting Dong, Daria Dzyabura, Zhilin Yang,
+SU Chenting, and Steven P. Gaskin. 2011. "Unstructured Direct
+Elicitation of Decision Rules." <em>Journal of Marketing Research
+48</em>(1): 116-27. <https://doi.org/10.1509/jmkr.48.1.116>
 
-Drost, Hajk-Georg.
-2018.
-“Philentropy: Information Theory and Distance Quantification with R” <em>Journal of Open Source Software 3</em>(26), 765, [https://joss.theoj.org/papers/10.21105/joss.00765](https://joss.theoj.org/papers/10.21105/joss.00765).
+Drost, Hajk-Georg. 2018. "Philentropy: Information Theory and Distance
+Quantification with R" <em>Journal of Open Source Software 3</em>(26),
+765, <https://joss.theoj.org/papers/10.21105/joss.00765>.
 
-Gilbride, Timothy J., Lenk, Peter J., and Brazell, Jeff D.
-2008.
-"Market Share Constraints and the Loss Function in Choice-Based Conjoint Analysis." <em>Marketing Science 27</em>(6):995-1011.[https://doi.org/10.1287/mksc.1080.0369](https://doi.org/10.1287/mksc.1080.0369)
+Gilbride, Timothy J., Lenk, Peter J., and Brazell, Jeff D. 2008. "Market
+Share Constraints and the Loss Function in Choice-Based Conjoint
+Analysis." <em>Marketing Science
+27</em>(6):995-1011.<https://doi.org/10.1287/mksc.1080.0369>
 
-Green, Paul E.,  and Srinivasan, V.
-1990.
-"Conjoint Analysis in Marketing: New Developments with Implications for Research and Practice." <em>Journal of Marketing 54</em>(4): 3-19.[https://doi.org/10.1177/002224299005400402](https://doi.org/10.1177/002224299005400402).
+Green, Paul E., and Srinivasan, V. 1990. "Conjoint Analysis in
+Marketing: New Developments with Implications for Research and
+Practice." <em>Journal of Marketing 54</em>(4):
+3-19.<https://doi.org/10.1177/002224299005400402>.
 
-Hamner, Ben, and Michael Frasco. 2018. “Metrics: Evaluation Metrics for Machine Learning.” [https://CRAN.R-project.org/package=Metrics](https://CRAN.R-project.org/package=Metrics).
+Sawtooth Software Inc. 2023. <em>Lighthouse Studio 9. Version
+9.15.2.</em> Sequim, WA.: Sawtooth Software Inc.
 
-Miaoulis, G., Parsons, H., & Free, V. 1990. Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
+Hamner, Ben, and Michael Frasco. 2018. "Metrics: Evaluation Metrics for
+Machine Learning." <https://CRAN.R-project.org/package=Metrics>.
 
-Orme, Bryan K.
-2015.
-“Including Holdout Choice Tasks in Conjoint Studies.” [https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies](https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies).
+Miaoulis, G., Parsons, H., & Free, V. 1990. Turf: A New Planning
+Approach for Product Line Extensions. <em>Marketing Research 2</em> (1):
+28-40.
 
-Orme, B. K. (2020). <em>Getting Started with Conjoint Analysis: Strategies for Product Design and Pricing Research</em>. 4th edition. Manhattan Beach, CA: Research Publishers LLC.
+Orme, Bryan K. 2015. "Including Holdout Choice Tasks in Conjoint
+Studies."
+<https://sawtoothsoftware.com/resources/technical-papers/including-holdout-choice-tasks-in-conjoint-studies>.
 
-R Core Team. 2023. “R: A Language and Environment for Statistical Computing.” [https://www.R-project.org/](https://www.R-project.org/).
+Orme, B. K. 2020. <em>Getting Started with Conjoint Analysis: Strategies
+for Product Design and Pricing Research</em>. 4th edition. Manhattan
+Beach, CA: Research Publishers LLC.
 
-Rao, Vithala R. 2014. <em>Applied Conjoint Analysis.</em> Springer Berlin Heidelberg. [https://doi.org/10.1007/978-3-540-87753-0](https://doi.org/10.1007/978-3-540-87753-0).
+R Core Team. 2023. "R: A Language and Environment for Statistical
+Computing." <https://www.R-project.org/>.
 
-Yang, Liu (Cathy), Olivier Toubia, and Martijn G.
-de Jong.
-2018.
-“Attention, Information Processing, and Choice in Incentive-Aligned Choice Experiments.” <em>Journal of Marketing Research 55</em>(6): 783–800.
-[https://doi.org/10.1177/0022243718817004](https://doi.org/10.1177/0022243718817004).
+Rao, Vithala R. 2014. <em>Applied Conjoint Analysis.</em> Springer
+Berlin Heidelberg. <https://doi.org/10.1007/978-3-540-87753-0>.
+
+Sermas R (2022). *ChoiceModelR: Choice Modeling in R*. R package version
+1.3.0, <https://CRAN.R-project.org/package=ChoiceModelR>.
+
+Yang, Liu (Cathy), Olivier Toubia, and Martijn G. de Jong. 2018.
+"Attention, Information Processing, and Choice in Incentive-Aligned
+Choice Experiments." <em>Journal of Marketing Research 55</em>(6):
+783--800. <https://doi.org/10.1177/0022243718817004>.

### 2023-11-11 paper/paper.Rmd
updated package - 231111 including markdown

@@
 
-validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using [Sawtooth Software](https://sawtoothsoftware.com/).[^1]
-
-[^1]: validateHOT also works with MaxDiff raw logit utilities, see, for example, @chapman2023.
-For CBC, it should work with other software, as long as all attributes are part-worth coded.
-Linear and piecewise coding is implemented to work with Sawtooth Software.
+validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using `ChoiceModelR` [@ChoiceModelR] or [Sawtooth Software](https://sawtoothsoftware.com/).
 
 Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.
-In terms of external validity, we refer to the generalizations to different settings [see, @calder1982, p.240].
-The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
 Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
+
+[^1]: In terms of external validity, we refer to the generalizations to different settings [see, @calder1982, p.240].
 
@@
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
-validateHOT is especially helpful for researchers who plan to report results for research articles according to open science standards.
 
@@
 82].
-\colcod{turf} as well as the 2 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT}, and can be run using the raw logit scores.
+\colcod{turf} as well as the 3 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT}, and can be run using the raw logit scores.
 
@@
 |        kl()        |       f1()       |     marksim()      |  prob_scores()   |
-|       mae()        |   precision()    |      reach()       |                  |
+|       mae()        |   precision()    |      reach()       |    zc-diffs()    |
 |      medae()       |     recall()     |       turf()       |                  |
@@
 
-To define the validation/holdout task, which has a total of 7 items (\texttt{\color{purple}prod}) plus the no-buy alternative (\texttt{\color{purple}none}), we use the \texttt{\color{purple}createHOT} function.
+Assuming you included a validation/holdout task with a total of 7 alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
+To create this validation task in *R*, we use the \texttt{\color{purple}createHOT} function.
 
 ```{r}
-# load data
-data("MaxDiff")
-
 # create holdout task and define relevant column indexes
@@
   data = MaxDiff, 
-  id = 1, 
-  none = 19, 
-  prod = 7, # no of alternatives in HOT excluding none
-  prod.levels = list(3, 10, 11, 15, 16, 17, 18), # index of alternatives
+  id = "ID", 
+  none = "none", 
+  prod.levels = list(3, 10, 11, 15, 16, 17, 18), 
   method = "MaxDiff", 
-  choice = 20, 
-  varskeep = 21
+  choice = "HOT", 
+  varskeep = "Group"
 )
@@
 ```{r}
-# test hit rate of holdout task
 hitrate(
@@
 ```{r}
-# test accuracy of holdout task
 accuracy(
@@
 Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim} and \texttt{\color{purple}turf}.
-In the following example, the market share is calculated accordning to the multinomial logit model [@McFadden1974].
+In the following example, the market share is calculated according to the multinomial logit model [@McFadden1974].
 
 ```{r}
-# run market simulations (share of preference rule)
 marksim(
@@
 108].
-To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibt certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
+To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
 

### 2023-11-11 R/MAE.R

@@ -45,7 +45,6 @@
 #'   data = MaxDiff,
 #'   id = 1,
 #'   none = 19,
-#'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",
 #'   choice = 20,

### 2023-11-11 R/MarkSim.R

@@ -58,7 +58,6 @@
 #'   data = MaxDiff,
 #'   id = 1,
 #'   none = 19,
-#'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",
 #'   choice = 20,

### 2023-11-11 R/Precision.R

@@ -42,9 +42,9 @@
 #' Please be aware about the following 2x2 table regarding coding of buy and
 #' no-buy choice
 #'
-#'\tabular{crcc}{
+#' \tabular{crcc}{
 #'    \tab \tab  Predicted           \tab    \cr
-#' Observed \tab \tab  Buy \tab No-buy  \cr
+#' Observed \tab \tab  Buy \tab No-Buy  \cr
 #'  \tab Buy \tab A \tab B  \cr
 #'  \tab No-Buy \tab C \tab D  \cr
 #' }
@@ -77,7 +77,6 @@
 #'   data = MaxDiff,
 #'   id = 1,
 #'   none = 19,
-#'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",
 #'   choice = 20, varskeep = 21

### 2023-11-11 R/Recall.R

@@ -44,9 +44,9 @@
 #' Please be aware about the following 2x2 table regarding coding of buy and
 #' no-buy choice
 #'
-#'\tabular{crcc}{
+#' \tabular{crcc}{
 #'    \tab \tab  Predicted           \tab    \cr
-#' Observed \tab \tab  Buy \tab No-buy  \cr
+#' Observed \tab \tab  Buy \tab No-Buy  \cr
 #'  \tab Buy \tab A \tab B  \cr
 #'  \tab No-Buy \tab C \tab D  \cr
 #' }
@@ -76,7 +76,6 @@
 #'   data = MaxDiff,
 #'   id = 1,
 #'   none = 19,
-#'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",
 #'   varskeep = 21,

### 2023-11-11 R/Specificity.R

@@ -43,9 +43,9 @@
 #' Please be aware about the following 2x2 table regarding coding of buy and
 #' no-buy choice
 #'
-#'\tabular{crcc}{
+#' \tabular{crcc}{
 #'    \tab \tab  Predicted           \tab    \cr
-#' Observed \tab \tab  Buy \tab No-buy  \cr
+#' Observed \tab \tab  Buy \tab No-Buy  \cr
 #'  \tab Buy \tab A \tab B  \cr
 #'  \tab No-Buy \tab C \tab D  \cr
 #' }
@@ -75,7 +75,6 @@
 #'   data = MaxDiff,
 #'   id = 1,
 #'   none = 19,
-#'   prod = 7,
 #'   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
 #'   method = "MaxDiff",
 #'   varskeep = 21,

### 2023-11-11 R/prob_scores.R

@@ -37,7 +37,6 @@
 #' should be converted for individuals only
 #'
 #' \code{anchor} only needs to be specified if anchored MaxDiff is applied. Input
-#' needs to be variable name or column index of anchor variable.
 #'
 #'
 #'
@@ -50,7 +49,7 @@
 #' Chrzan, K., & Orme, B. K. (2019). \emph{Applied MaxDiff: A Practitioner’s
 #' Guide to Best-Worst Scaling} Provo, UT: Sawtooth Software.
 #'
-#'}
+#' }
 #'
 #' @examples
 #' \dontrun{
@@ -152,7 +151,7 @@ prob_scores <- function(data, group = NULL, items, set.size,
   }
 
   # can not specify res to 'ind' and specify group
-  if ((res == "ind") & !base::missing(group)){
+  if ((res == "ind") & !base::missing(group)) {
     stop("Error: Can not speficy 'group' if 'res' is set to 'ind'!")
   }
 
@@ -160,61 +159,57 @@ prob_scores <- function(data, group = NULL, items, set.size,
 
   #######################################################
   if (base::is.null(anchor)) {
-    if (res == "agg"){
-    return(data %>%
-      dplyr::mutate(dplyr::across({{ items }}, ~ (base::exp(.x) / (base::exp(.x) + (set.size - 1))))) %>%
-      dplyr::rowwise() %>%
-      dplyr::mutate(Summe = base::sum(dplyr::pick({{ items }}))) %>% # sum up
-      dplyr::ungroup() %>%
-      dplyr::mutate(dplyr::across({{ items }}, ~ .x / Summe * 100)) %>%
-      dplyr::group_by(dplyr::pick({{ group }})) %>%
-      dplyr::summarise(dplyr::across({{ items }},
-        c(mw = base::mean, std = stats::sd),
-        .names = "{.col}.{.fn}"
-      )) %>%
-      tidyr::pivot_longer(.,
-        cols = tidyselect::ends_with(c(".mw", ".std")),
-        names_to = c("Option", ".value"), names_sep = "\\."
-      ))
-    }
-
-
-    if (res == "ind"){
+    if (res == "agg") {
       return(data %>%
-               dplyr::mutate(dplyr::across({{ items }}, ~ (base::exp(.x) / (base::exp(.x) + (set.size - 1))))) %>%
-               dplyr::rowwise() %>%
[…]

### 2023-11-11 R/zc_diffs.R

@@ -95,11 +95,11 @@ zc_diffs <- function(data, group = NULL, attrib, coding, interpolate.levels = NU
     warning("Warning: 'group' contains NAs!")
   }
 
-  if (base::is.null(coding)){
+  if (base::is.null(coding)) {
     base::stop("Error: 'coding' has to be specified!")
   }
 
-  if (base::length(attrib) != base::length(coding)){
+  if (base::length(attrib) != base::length(coding)) {
     base::stop("Error: 'coding' and 'attrib' have to have the same length!")
   }
 
@@ -123,7 +123,7 @@ zc_diffs <- function(data, group = NULL, attrib, coding, interpolate.levels = NU
 
   # test input of interpolate levels
   if (!(base::is.list(interpolate.levels)) &
-      !(base::is.null(interpolate.levels))) {
+    !(base::is.null(interpolate.levels))) {
     base::stop("Error: Input of 'interpolate.levels' has to be a list!")
   }
 
@@ -145,7 +145,7 @@ zc_diffs <- function(data, group = NULL, attrib, coding, interpolate.levels = NU
 
   # interpolate.levels can not be larger than number of attributes
   if (!base::is.null(interpolate.levels) &
-      (base::length(interpolate.levels) > base::length(attrib))) {
+    (base::length(interpolate.levels) > base::length(attrib))) {
     base::stop(
       "Error: List of 'interpolate.levels' can not be larger than list of 'attrib'!"
     )
@@ -204,7 +204,7 @@ zc_diffs <- function(data, group = NULL, attrib, coding, interpolate.levels = NU
   }
 
   # can not specify res to 'ind' and specify group
-  if ((res == "ind") & !base::missing(group)){
+  if ((res == "ind") & !base::missing(group)) {
     stop("Error: Can not speficy 'group' if 'res' is set to 'ind'!")
   }
 
@@ -213,8 +213,8 @@ zc_diffs <- function(data, group = NULL, attrib, coding, interpolate.levels = NU
   att <- base::length(attrib)
 
   attrib_all <- c()
-  for (i in 1:base::length(attrib)){
-    attrib_all <- c(attrib_all, base::colnames(data[ , attrib[[i]]]))
+  for (i in 1:base::length(attrib)) {
+    attrib_all <- c(attrib_all, base::colnames(data[, attrib[[i]]]))
   }
 
   new <- c()
[…]

### 2023-11-11 tests/testthat/test-MedAE.R

@@ -1,6 +1,6 @@
 HOT <- createHOT(
   data = MaxDiff, none = 19,
-  id = 1, prod = 7,
+  id = 1,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
   choice = 20, method = "MaxDiff", varskeep = 21
 )
@@ -133,7 +133,7 @@ test_that("check whether examples are correct ", {
 
 test_that("Test whether results equals Metrics::mdae ", {
   actual <- HOT %>%
-    dplyr::mutate(dplyr::across(Option_1:None, function(x) (base::exp(x)/base::rowSums(base::exp(.[c(2:9)]))))) %>%
+    dplyr::mutate(dplyr::across(Option_1:None, function(x) (base::exp(x) / base::rowSums(base::exp(.[c(2:9)]))))) %>%
     dplyr::summarise(dplyr::across(Option_1:None, ~ mean(.x))) %>%
     base::unlist() %>%
     base::unname()

### 2023-11-11 tests/testthat/test-Precision.R

@@ -1,6 +1,6 @@
 HOT <- createHOT(
   data = MaxDiff, none = 19,
-  id = 1, prod = 7,
+  id = 1,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
   choice = 20, method = "MaxDiff", varskeep = 21
 )
@@ -140,9 +140,11 @@ test_that("check whether examples are correct ", {
 
 test_that("Test whether results equals Metrics::precision ", {
   metr <- HOT %>%
-    mutate(pred = max.col(.[c(2:9)]),
-           pred = ifelse(pred == 8, 0, 1),
-           choice = ifelse(choice == 8, 0, 1)) %>%
+    mutate(
+      pred = max.col(.[c(2:9)]),
+      pred = ifelse(pred == 8, 0, 1),
+      choice = ifelse(choice == 8, 0, 1)
+    ) %>%
     select(pred, choice)
 
   actual <- c(unname(unlist(metr$choice)))

### 2023-11-11 tests/testthat/test-Recall.R

@@ -1,6 +1,6 @@
 HOT <- createHOT(
   data = MaxDiff, none = 19,
-  id = 1, prod = 7,
+  id = 1,
   prod.levels = list(3, 10, 11, 15, 16, 17, 18),
   choice = 20, method = "MaxDiff", varskeep = 21
 )
@@ -140,9 +140,11 @@ test_that("check whether examples are correct ", {
 
 test_that("Test whether results equals Metrics::recall ", {
   metr <- HOT %>%
-    mutate(pred = max.col(.[c(2:9)]),
-           pred = ifelse(pred == 8, 0, 1),
-           choice = ifelse(choice == 8, 0, 1)) %>%
+    mutate(
+      pred = max.col(.[c(2:9)]),
+      pred = ifelse(pred == 8, 0, 1),
+      choice = ifelse(choice == 8, 0, 1)
+    ) %>%
     select(pred, choice)
 
   actual <- c(unname(unlist(metr$choice)))

### 2023-11-11 tests/testthat/test-createHOT.R

@@ -1,32 +1,8 @@
-test_that("wrong input", {
-  expect_error(createHOT(
-    data = MaxDiff,
-    id = "id",
-    prod = 7,
-    prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-    choice = 20,
-    method = "MaxDiff"
-  ))
-})
-
-test_that("wrong input", {
-  expect_error(createHOT(
-    data = MaxDiff,
-    id = 1,
-    none = "none",
-    prod = 7,
-    prod.levels = list(3, 10, 11, 15, 16, 17, 18),
-    choice = 20,
-    method = "MaxDiff"
-  ))
-})
-
-test_that("With none one column more", {
+test_that("With none one column more ", {
   expect_equal((base::length(createHOT(
     data = MaxDiff,
     id = 1,
     none = 19,
-    prod = 7,
     prod.levels = list(3, 10, 11, 15, 16, 17, 18),
     choice = 20,
     method = "MaxDiff"
@@ -34,7 +10,6 @@ test_that("With none one column more", {
     base::length(createHOT(
       data = MaxDiff,
       id = 1,
-      prod = 7,
       prod.levels = list(3, 10, 11, 15, 16, 17, 18),
       choice = 20,
       method = "MaxDiff"
@@ -42,12 +17,11 @@ test_that("With none one column more", {
   ), 1)
 })
 
-test_that("Coding not needed for MaxDiff", {
+test_that("Coding not needed for MaxDiff ", {
   expect_error(createHOT(
     data = MaxDiff,
     id = 1,
     none = 19,
-    prod = 7,
     prod.levels = list(3, 10, 11, 15, 16, 17, 18),
     choice = 20,
     coding = rep(0, 7),
@@ -55,12 +29,11 @@ test_that("Coding not needed for MaxDiff", {
   ))
 })
 
-test_that("interpolate.leves not needed for MaxDiff", {
+test_that("interpolate.leves not needed for MaxDiff ", {
   expect_error(createHOT(
     data = MaxDiff,
     id = 1,
     none = 19,
-    prod = 7,
     prod.levels = list(3, 10, 11, 15, 16, 17, 18),
     choice = 20,
     interpolate.levels = list(c(20:30)),
[…]

### 2023-11-11 paper/paper.Rmd
updated paper - 231111

@@
 |        kl()        |       f1()       |     marksim()      |  prob_scores()   |
-|       mae()        |   precision()    |      reach()       |    zc-diffs()    |
+|       mae()        |   precision()    |      reach()       |    zc_diffs()    |
 |      medae()       |     recall()     |       turf()       |                  |
@@
 ```{r}
-# create holdout task and define relevant column indexes
 HOT <- createHOT(

### 2023-11-11 paper/paper.Rmd
updated paper typos - 231111

@@
     corresponding: True
-    affiliation: 1
+    affiliation: 1, 2
   - name: Marcel Lichters
@@
 Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participant) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
 Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.

### 2023-11-13 paper/paper.Rmd
added github actions - 231113

@@
 
-validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using `ChoiceModelR` [@ChoiceModelR] or [Sawtooth Software](https://sawtoothsoftware.com/).
+validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using, for example, `ChoiceModelR` [@ChoiceModelR] or Sawtooth's Lighthouse Studio.
 
-Preference measurement techniques', such as (A)CBC or MaxDiff, ultimate goal is to predict future behavior [@green1990].
+Preference measurement techniques', such as (A)CBC or MaxDiff, aim is to predict behavior [@green1990].
 Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
@@
 
-validateHOT combines both validation and market simulation in one package and has three key advantages, it a) helps to opt for the best model, b) runs relevant market simulations that help to find the right product combinations, and finally, c) is an open source tool including functions that are usually implemented in paid software, and therefore, remain a black-box for researchers and practitioners.
+validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps to opt for the best model, (2) runs relevant market simulations that help to find the right product combinations or assortments, and finally, (3) is an open source tool including functions that are usually implemented in property commercial, and therefore, remain a black-box for researchers and practitioners.
 
@@
 validateHOT is a practical tool for Sawtooth Software users in industry as well as academia.
-It provides an open source solution for a) validating a validation/holdout task and ensuring that the model has predictive validity; b) running market simulations (e.g., **T**otal **U**nduplicated **R**each and **F**requency, hereafter TURF).
+It provides an open source solution for a) validating a validation/holdout task and ensuring that the model has predictive validity; b) running market simulations (e.g., Total Unduplicated Reach and Frequency, hereafter TURF).
 Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
 However, to put the Sawtooth export into the right format, the user needs some data wrangling which could pose a barrier.
-Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR [@ChoiceModelR], choicetools [@choicetools], logitR [@logitr], bayesm [@bayesm] etc.).
+Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR, @ChoiceModelR, choicetools, @choicetools, logitR, @logitr, bayesm, @bayesm], etc.).
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
@@
 
-validateHOT's functions can be categorized into four main components, see \autoref{tab:table1}.
-To bring the data into the right format, users can run the \texttt{\color{purple}createHOT} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
+validateHOT's functions can be categorized into four main areas, see \autoref{tab:table1}.
+To bring the data into the right format, users can run the \texttt{\color{purple}createHOT()} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
 82].
-\colcod{turf} as well as the 3 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT}, and can be run using the raw logit scores.
+\colcod{turf()} as well as the 3 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()}, and can be run using the raw logit scores.
 
@@
 
-: Overview of main four components of validateHOT and their corresponding functions \label{tab:table1}
+: Overview of main four areas of validateHOT and their corresponding functions \label{tab:table1}
 
@@
 
-After running the Hierarchical Bayes estimation, the **raw** utility scores have to be exported and read into an *R* data frame.
+After running the hierarchical Bayes estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame.
 This data frame has to include the actual choice in the validation/holdout task.
@@
 Assuming you included a validation/holdout task with a total of 7 alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
-To create this validation task in *R*, we use the \texttt{\color{purple}createHOT} function.
+To create this validation task in *R*, we use the \texttt{\color{purple}createHOT()} function.
 
@@
 The underlying logic of the confusion matrix is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
-validateHOT calculates how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (here by applying \texttt{\color{purple}accuracy}).
+validateHOT calculates how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (here by applying \texttt{\color{purple}accuracy()}).
 
@@
 
-Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim} and \texttt{\color{purple}turf}.
+Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
 In the following example, the market share is calculated according to the multinomial logit model [@McFadden1974].
@@
 
-Finally, \texttt{\color{purple}turf}, a "product line extension model" [@miaoulis1990, p.
+Finally, \texttt{\color{purple}turf()}, a "product line extension model" [@miaoulis1990, p.
 29], is a tool to find the perfect assortment that creates the highest reach and is especially powerful for MaxDiff studies [@chrzan2019, p.
 108].
-To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf} with data obtained using a likert scale).
+To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf()} with data obtained using a likert scale).
 

### 2023-12-08 R/Recall.R
added zero_anchored + updated functions - 231209

@@ -160,6 +160,14 @@ recall <- function(data, group, opts, choice, none) {
     stop("Error: 'choice' has to be numeric!")
   }
 
+  # test length of none
+  if (!base::missing(none)) {
+    anc <- data %>% dplyr::select(., {{ none }}) %>% base::colnames(.)
+    if (length(anc) > 1)
+      base::stop("Error: 'none' can only be one variable!")
+  }
+
+
   return(data %>%
     dplyr::mutate(
       # store column index with highest utility

### 2023-12-21 README.Rmd
proof reading of manuals, markdown, and vignette - 231221

@@
 
-The goal of `validateHOT` is to validate the results of your validation
-task (also known as holdout task) as well as a tool for simulating
-markets with the results of your MaxDiff, CBC, and ACBC. This package is
+The goal of `validateHOT` is to provide a tool to validate the results
+of your validation task (also known as holdout task; short form
+**HOT**), simulating markets with the results of your MaxDiff, CBC, and
+ACBC, and lastly to convert the raw logit scores of your MaxDiff, CBC,
+and ACBC into scores that are easier to communicate. This package is
 especially relevant for the [Sawtooth
@@
 report their analysis in *R* for open science purposes. However, it also
-works perfectly with the great package `ChoiceModelR`(Sermas, 2022). Of
-course, this package is also useful for practitioners, who would like to
+works perfectly with the great package `ChoiceModelR`(Sermas, 2022).
+This package is extremely useful for practitioners, who would like to
 run the analyses in an open source software. The ultimate goal of these
@@
 task (Yang et al., 2018), it is highly recommended to do so (Orme, 2015;
-Rao, 2014). This validation/holdout task does not only help to check
-whether everything went right during data collection but also to
-determine the final model. `validatHOT` provides some of the relevant
-metrics to test the performance of the data in predicting a
-validation/holdout task.
+Rao, 2014). Validation/holdout tasks do not only check whether your data
+is valid but can also help to test different models. `validatHOT`
+provides some of the relevant metrics to test the performance of the
+data in predicting a validation/holdout task.
 
@@
 
-👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data,
+👉🏾 <u>**What you need to provide**</u>: <br> After collecting your data
 and running your initial Hierarchical Bayes models, you can turn to
@@
 validation/holdout task. Therefore, you only have to read in your raw
-utility scores as well as the actual choice of your validation/ holdout
+utility scores as well as the actual choice of your validation/holdout
 task. You can use the `merge()` function provided by the *R* base
@@
 
-<li>validation metrics mainly reported in preference measurement
-studies</li>
+<li>validation metrics</li>
 
@@
 choices) of your validation/holdout task. The output will contain the
-percentage of how many choices were correctly predicted, the chance
-level in your validation task ($\frac{1}{alternatives}$) in percentage,
-the number of correctly predicted participants' choices as well as the
-number of observations.</li>
+percentage of how many choices were correctly predicted including the
+standard error, the chance level in your validation task
+($\frac{1}{alternatives}$) in percentage, the number of correctly
+predicted participants' choices as well as the number of
+observations.</li>
 
@@
 both divergence between predicted from observed and observed from
-predicted due to the asymmetry of the Kullback-Leibler divergence. If
-you specify an optional <code>group</code> argument the output is split
-by groups. Currently, you can choose between \eqn{log} and \eqn{log{_2}}
-as logarithm base. The default is set to \eqn{log}.</li>
+predicted due to the asymmetry of the Kullback-Leibler divergence.
+`validateHOT` currently provides two logarithm bases: \eqn{log} and
+\eqn{log{_2}}. The default is set to \eqn{log}.</li>
 
@@
 
-<li><code>medae()</code>: calculates the median absolute error, which is
-less affected by outliers compared to the mean absolute error.</li>
+<li><code>medae()</code>: calculates the median absolute error, which
+is, compared to the mean absolute error, less affected by outliers.</li>
 
@@
 
-<li><code>rmse()</code>: provides the root-mean-squared error of
+<li><code>rmse()</code>: provides the root-mean-square error of
 deviation between predicted and stated choice share.</li>
@@
 We also include metrics from machine learning, i.e., the confusion
-matrix (e.g., Burger, 2018). For all of the 5 provided functions, you
-currently have to include a **none** alternative in your
-validation/holdout task. We currently predict, e.g., whether a buy or
-no-buy was correctly predicted. Information could be used for
-overestimating and underestimating, respectively, of product purchases.
-In the following <code>TP</code> stands for true positives,
-<code>FP</code> for false positives, <code>TN</code> for true negatives,
-and <code>FN</code> for false negatives (Burger, 2018). To translate
-this to the `validateHOT` logic, imagine you have a validation/holdout
-task with 5 alternatives plus the alternative not to buy any of those
-chosen. `validateHOT` now measures whether or not a buy (participant
-opts for one of the 5 alternatives) or a no-buy (participant opts for
-the no-buy alternative), respectively, is correctly predicted.
+matrix (e.g., Burger, 2018). For all of the five provided functions, a
+**none** alternative has to be included in the validation/holdout task.
+The logic of the implemented confusion matrix is to test, for example,
+whether a buy or no-buy was correctly predicted. Information could be
+used to get a sense of overestimation and underestimation, respectively,
+of product demand. In the table below <code>TP</code> stands for true
+positives, <code>FP</code> for false positives, <code>TN</code> for true
+negatives, and <code>FN</code> for false negatives (Burger, 2018; Kuhn,
+2008). To translate this to the `validateHOT` logic, imagine you have a
+validation/holdout task with five alternatives plus the alternative not
+to buy any of those chosen. `validateHOT` now measures whether or not a
+buy (participant opts for one of the five alternatives) or a no-buy
+(participant opts for the none alternative), respectively, is correctly
+predicted.
 
-Please be aware that for coding, `validateHOT` applies the following
-coding of the *buy* and *no-buy* alternatives. Rows refer to the
-observed decisions while columns refer to the predicted ones.
+Please be aware that `validateHOT` applies the following coding of the
+*buy* and *no-buy* alternatives. Rows refer to the observed decisions
+while columns refer to the predicted ones.
 
-|        |     |        |
+|        | Buy | No-buy |
 |--------|:---:|:------:|
-|        | Buy | No-buy |
 | Buy    | TP  |   FN   |
@@
 buying at least one product of that assortment) and the frequency (how
-many products are on average a purchase option). <code>turf()</code>
+many products on average are a purchase option). <code>turf()</code>
 currently provides both the *threshold* approach (<code>approach =
@@
 <code>freqassort()</code> will give you the averaged frequency, how many
-products the participants will choose from your in the function
-determined potential assortment. Again, you have to define a
-<code>none</code> alternative, because <code>freqassort()</code> uses
-the <i>threshold</i> approach, meaning if the utility of one product is
-above the utility of <code>none</code>, it is marked as potential
-purchase option. While <code>turf()</code> calculates the reach and
-frequency for <b>all</b> combinations, you specify the combination you
-are interested in <code>freqassort()</code>.</li>
+products the participants will choose from a potential assortment.
+Again, you have to define a <code>none</code> alternative, because
+<code>freqassort()</code> uses the <i>threshold</i> approach, meaning if
+the utility of one product is above the utility of <code>none</code>, it
+is marked as potential purchase option. While <code>turf()</code>
+calculates the reach and frequency for <b>all</b> combinations, you
+specify the combination you are interested in
+<code>freqassort()</code>.</li>
 
@@
 
-<li><code>marksim()</code>: runs market simulations (either share of
+<li><code>marksim()</code>: Runs market simulations (either share of
 preference or first choice rule), including the standard error, as well
 as the lower and upper confidence interval, which is calculated
-according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p.
-94).</li>
+according to the following formula $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$
+(Orme, 2020, p. 94).</li>
 
@@
 
-### Reestimating raw utilities
+### Converting raw utilities
 
-<code>validateHOT</code> also provides 3 functions to better interpret
-the scores of both (A)CBC and MaxDiff. Currently, 3 functions are
-provided, namely:
+<code>validateHOT</code> also provides four functions to better
+interpret the scores of both (A)CBC and MaxDiff, namely:
 
@@
 
-<li><code>att_imp()</code>: converts the raw utilities of either an ACBC
+<li><code>att_imp()</code>: Converts the raw utilities of either an ACBC
 or CBC into importance scores for each attribute (see, Orme, 2020, pp.
@@
 
-<li>
-
-<code>prob_scores()</code>converts the raw utilities of a MaxDiff to
-choice probabilities by applying the following procedures:
+<li><code>prob_scores()</code>: Converts the raw utilities of a MaxDiff
+to choice probabilities by applying the following procedures:
 
@@
 
-<li>For anchored MaxDiff:
+<li>For anchored MaxDiff a slightly different formula is applied:
 $\frac{exp^{U_i}}{(exp^{U_i} + a - 1)} * 100 * \frac{1}{a}$ (Chrzan &
@@
 
-<li><code>zc_diffs()</code>: rescales the raw logit utilities to make
+<li><code>zc_diffs()</code>: Rescales the raw logit utilities to make
 them comparable across participants (Sawtooth Software Inc, 2023, p.
 343).</li>
+
+<li><code>zero_anchored()</code></li>: Rescales the raw logits of a
+MaxDiff to zero-centered diffs (Chrzan & Orme, 2019, p. 64).
 
@@
 
-`validaeHOT` provides 5 data sets that come with the package. These data
-sets should help to better understand the way the data needs to be
-defined, especially for the `createHOT()` function.
+`validateHOT` provides five data sets that help to better explain the
+functions as well as the structure of the input, especially for the
+`createHOT()` function.
 
@@
 <li><code>CBC_lin</code>: Example data set with raw utilities of a CBC
-study conducted in Sawtooth. One attribute was linear coded while the
+study conducted in Sawtooth. One attribute was linear-coded while the
 other attributes are part-worth coded.</li>
@@
 
-## Why `validateHOT`
+## The story behind `validateHOT`
 
@@
 these students did not have any prior experience (or only sparsely) with
-*R*. One of the chapters in this class is about model validating the
-results obtained and we teach this, of course, in *R*. We want to put a
-strong emphasis on open science and providing tools to run the analyses
-and provide the code afterwards is essential.
+*R*. One of the chapters in this class is about model validation by
+checking holdout task and we teach this, of course, in *R* 😍. We want
+to put a strong emphasis on open science and providing tools to run the
+analyses and provide the code afterwards is essential. `validateHOT`
+makes this process look easy.
 
-Of course, there are other great packages which are faster in running
-(i.e., `Metrics` by Hamner & Frasco, 2018), however, these packages need
-some more data wrangling in order to use the appropriate functions with
-the raw utilities, which might be a burden or barrier for one or the
-other.
+Of course, there are other great packages which are faster in terms of
+running time (i.e., `Metrics` by Hamner & Frasco, 2018), however, these
+packages need some more data wrangling in order to use the appropriate
+functions with the raw utilities, which might be a burden or barrier for
+the one or the other.
 
@@
 simply because they do not know how to use it correctly. Having a
-package to evaluate the validation/holdout task can also be beneficial
+package to evaluate the validation/holdout task can be very beneficial
 from this perspective.
@@
 
-First, we load the package.
+First, we load the package:
 
@@
 
-Now imagine you included a validation/holdout task with 3 alternatives
-plus a no-buy alternative. We specify the `data` argument and as well as
-the `id`. Since we also have a *no-buy* alternative in our validation
-task, we next specify the `none` argument, otherwise we would have left
-it empty. Afterwards, we define each alternative with the argument
-`prod.levels`. If we look back at the data frame, we can see that the
-first alternative in the holdout task (`c(4, 9, 19)`) is composed of the
-following attribute levels `Att1_Lev1`, `Att2_Lev1`, and `Att3_Lev5`.
+Now imagine you included a validation/holdout task with three
+alternatives plus a no-buy alternative. We specify the `data` argument
+and as well as the `id`. Since we also have a *no-buy* alternative in
+our validation task, we next specify the `none` argument, otherwise we
+would have left it empty. Afterwards, we define each alternative with
+the argument `prod.levels`. If we look back at the data frame, we can
+see that the first alternative in the holdout task (`c(4, 9, 19)`) is
+composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and
+`Att3_Lev5`.
 
@@
 > ❗ `createHOT()` takes both column names and column indexes. However,
-> please be aware, if you include linear coding or piecewise coding, you
-> **have** to provide the column indexes for the input in prod.levels.,
-> please be aware of this. However, you can easily find out the index by
-> either using the `names()` function to see all names of the data
-> frame, or if you already know the name of the variable, you can use
-> `which()` and `colnames()`, both functions are provided by the base
-> package (R Core Team, 2023). For example, if you want to find out the
-> column index of `ID`, you could run `which(colnames(CBC) == "ID")` to
-> determine the column index of `ID`.
+> please be aware, if you include linear-coded or piecewise-coded, you
+> **have** to provide the column indexes for the input in `prod.levels`.
+> However, you can easily find out the index by either using the
+> `names()` function to see all names of the data frame, or if you
+> already know the name of the variable, you can use `which()` and
+> `colnames()`, both functions are provided by the base package (R Core
+> Team, 2023). For example, if you want to find out the column index of
+> `ID`, you could run `which(colnames(CBC) == "ID")` to determine the
+> column index of `ID`.
 
@@
 Let us take a glimpse at the output, which shows the participants' total
-raw utilities for each of the 3 alternatives that were included in the
-validation/holdout task.
+raw utilities for each of the three alternatives that were included in
+the validation/holdout task.
 
@@
 specify the `data`, the column names of the alternatives (`opts`;
-remember there are 3 alternatives + the *no-buy* alternative), and
+remember there are three alternatives + the *no-buy* alternative), and
 finally the actual choice (`choice`).
@@
 Finally, let us test, how many participants would at least buy one of
-the 3 products, assuming that this is one potential assortment we would
-like to offer to our consumers. We will use the `reach()` function. To
-specify the bundles we are offering we use the `opts` argument in our
-function.
+the three products, assuming that this is one potential assortment we
+would like to offer to our consumers. We will use the `reach()`
+function. To specify the bundles we are offering we use the `opts`
+argument in our function.
 
@@
 
-### Example II - CBC with linear coding
+### Example II - CBC with linear-coded attribute(s)
 
 In a second example, we again use a *CBC*, however, this time we show
-how to use `validateHOT` if one of the variables are linear coded. All
+how to use `validateHOT` if one of the variables is linear-coded. All
 other examples are provided in the accompanied vignette.
@@
 *no-buy* alternative, just as we did in the previous example. The only
-difference to the previous example is that for our model estimation, the
-third attribute (`Att3_Lin`) was coded as linear.
+difference to the previous example is that the third attribute
+(`Att3_Lin`) was linear-coded.
 
@@
 that this value needs to be interpolated by specifying the `coding`
-argument. This tells us that the first two attributes (`Att1_Lev5`,
-`Att2_Lev4` in the case of alternative 2) are part-worth coded (`0`)
-while the third attribute is linear coded (`1`).
+argument accordingly. This tells us that the first two attributes
+(`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are part-worth
+coded (`0`) while the third attribute is linear-coded (`1`).
 
 To interpolate the value, we have to provide `createHOT()` the
-`interpolate.levels`. These **need** to be the same as provided to
-Sawtooth or `ChoiceModelR` as levels. Moreover, it is important that the
-value that should be interpolated needs to lie within the lower and
-upper bound of `interpolate.levels`. In our case, we had 7 levels that
-range from 10 to 70.
+`interpolate.levels`. These **need** to be the same levels as provided
+to Sawtooth or `ChoiceModelR`. Moreover, it is important that the value
+that should be interpolated needs to lie within the lower and upper
+bound of `interpolate.levels`. In our case, we had 7 levels that range
+from 10 to 70.
 
@@
 In this case, the group assignment is stored in form of integers.
-However, the output is the same if it is a factor or if it is labelled
-data. To proof this we just quickly change `group` into a factor by
-using the `factor()` function provided by the *R* Core Team (2023).
+However, the output is the same if it is a factor or labelled data. To
+proof this we just quickly change `group` into a factor by using the
+`factor()` function provided by the *R* Core Team (2023).
 
@@
 
-Chrzan, K., & Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner's
+Chrzan, K., and Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner's
 Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.
@@
 Share Constraints and the Loss Function in Choice-Based Conjoint
-Analysis." <em>Marketing Science
-27</em>(6):995-1011.<https://doi.org/10.1287/mksc.1080.0369>
+Analysis." <em>Marketing Science 27</em>(6):
+995-1011.<https://doi.org/10.1287/mksc.1080.0369>
 
@@
 3-19.<https://doi.org/10.1177/002224299005400402>.
+
+Kuhn, Max. 2008. "Building Predictive Models in R Using the caret
+Package." <em>Journal of Statistical Software 28</em>(5), 1-26.
+<https://doi.org/10.18637/jss.v028.i05>.
 
@@
 
-Miaoulis, G., Parsons, H., & Free, V. 1990. Turf: A New Planning
-Approach for Product Line Extensions. <em>Marketing Research 2</em> (1):
+Miaoulis, G., Parsons, H., and Free, V. 1990. Turf: A New Planning
+Approach for Product Line Extensions. <em>Marketing Research 2</em>(1):
 28-40.
@@
 
-Sermas R (2022). *ChoiceModelR: Choice Modeling in R*. R package version
+Sermas, R. 2022. *ChoiceModelR: Choice Modeling in R*. R package version
 1.3.0, <https://CRAN.R-project.org/package=ChoiceModelR>.

### 2023-12-21 paper/paper.Rmd
proof reading of manuals, markdown, and vignette - 231221

@@
 authors:
-  - name: Joshua Schramm
+  - name: Joshua Benjamin Schramm
     orcid: 0000-0001-5602-4632
@@
 However, to put the Sawtooth export into the right format, the user needs some data wrangling which could pose a barrier.
-Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR, @ChoiceModelR, choicetools, @choicetools, logitR, @logitr, bayesm, @bayesm], etc.).
+Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR, @ChoiceModelR, choicetools, @choicetools, logitR, @logitr, bayesm, @bayesm, etc.).
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
@@
 82].
-\colcod{turf()} as well as the 3 rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()}, and can be run using the raw logit scores.
+\colcod{turf()} as well as the four rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()}, and can be run using the raw logit scores.
 
@@
 |       mae()        |   precision()    |      reach()       |    zc_diffs()    |
-|      medae()       |     recall()     |       turf()       |                  |
+|      medae()       |     recall()     |       turf()       | zero_anchored()  |
 |       mhp()        |  specificity()   |                    |                  |

### 2023-12-21 R/MAE.R

@@ -1,14 +1,14 @@
 #' Mean Absolute Error
 #'
-#' @description Function to measure the mean absolute error of a
-#' validation/holdout task.Calculates the averaged absolute error, i.e.,
+#' @description \code{mae} measures the mean absolute error of a
+#' validation/holdout task. Calculates the averaged absolute error, i.e.,
 #' deviation between predicted and stated share of alternatives in the
 #' validation/holdout task.
 #'
 #'
 #' @param data A data frame with all relevant variables.
 #' @param group Optional column name(s) to specify grouping variable(s)
-#' to get \code{"mae"} by group(s).
+#' to get \code{mae} by group(s).
 #' @param opts Column names of the alternatives included in the
 #' validation/holdout task.
 #' @param choice Column name of the actual choice.

### 2023-12-21 R/Precision.R

@@ -1,24 +1,24 @@
 #' Precision
 #'
-#' @description precision is one of the 5 metrics of the confusion matrix
+#' @description \code{precision} is one of the 5 metrics of the confusion matrix
 #' and is defined as \eqn{\frac{TP}{TP + FP}}, where TP =
 #' True Positives, FP = False Positives (see, e.g., Burger, 2018).
 #'
 #' @param data A data frame with all relevant variables.
 #' @param group Optional column name(s) to specify grouping variable(s)
-#' to get \code{"precision"} by group(s).
+#' to get \code{precision} by group(s).
 #' @param opts Column names of the alternatives included in the
 #' validation/holdout task.
 #' @param choice Column name of the actual choice.
 #' @param none Column name of none alternative.
 #'
 #' @details
-#' The current logic of \code{"precision"} is to determine whether a binary
+#' The current logic of \code{precision} is to determine whether a binary
 #' coded is correctly predicted by the model.
-#' To use the function a \code{"none"} alternative has to be included in the
+#' To use the function a \code{none} alternative has to be included in the
 #' validation/holdout task. One potential usage is, for example, whether a
 #' buy or a no-buy condition was predicted correctly. For example,
-#' you have three alternatives plus a \code{"none"} alternative and you
+#' you have three alternatives plus a \code{none} alternative and you
 #' want to check whether a buy or no-buy was correctly predicted. This function
 #' can be helpful when you test, for example, if your model significantly
 #' overestimates or underestimates, for example, a purchase likelihood.
@@ -40,7 +40,7 @@
 #' validation/holdout task.
 #'
 #' Please be aware about the following 2x2 table regarding coding of buy and
-#' no-buy choice
+#' no-buy choice:
 #'
 #' \tabular{crcc}{
 #'    \tab \tab  Predicted           \tab    \cr

### 2023-12-21 R/createHOT.R

@@ -1,17 +1,17 @@
 #' @title  Preparing holdout/validation task and creating utilities
 #'
 #' @description Function used to create utilities for validation task.
-#' Currently not working with alternative-specific designs.
 #'
 #' @param data A data frame with all relevant variables.
 #' @param id A vector of unique identifier in \code{data}.
-#' @param none An optionalvector to specify \code{none}
+#' @param none An optional vector to specify \code{none}
 #' alternative in \code{data}.
 #' @param prod.levels A list to define the attribute levels of the
-#' alternatives (\code{prod}).
+#' alternatives (\code{prod}). If include linear-coded or piecewise-coded
+#' attributes are included, column indexes are needed for the input.
 #' @param interpolate.levels A list of the levels of the variables that should
-#' be interpolated. These have to be the same as provided to Sawtooth Software
-#' or ChoiceModelR (Sermas, 2022).
+#' be interpolated. These have to be the same as specified in model estimation
+#' (e.g., if you center attribute levels before estimation, insert the centered levels).
 #' Please make sure to provide the whole list. Only has to be specified for the
 #' variables that are coded as '1' (linear) or '2' (piecewise).
 #' @param piece.p A list of the lower level and the upper
@@ -33,27 +33,24 @@
 #' Make sure to upload the raw utilities of your study (either from Sawtooth Software
 #' or ChoiceModelR, Sermas, 2022).
 #' Afterwards, the function will create the utilities based on the additive
-#' utility model (Rao, 2014, p. 82).
+#' utility model (Rao, 2014, p. 82). If working with alternative specific-designs,
+#' insert \code{NA} if attribute is not specified.
 #'
-#' \code{data} has to be a data frame with **raw** scores of the attribute
+#' \code{data} has to be a data frame with raw scores of the attribute
 #' levels.
 #'
 #' \code{id} has to be the column index or column name of the id (unique for each participant)
 #' in data frame.
 #'
 #' \code{none} has to be specified in case a \code{none} alternative is
-#' included in holdout/validation task, please specify this by specifying the
+#' included in holdout/validation task, specify
 #' column index or column name of \code{none} alternative, otherwise leave it empty.
 #'
 #'
 #' \code{prod.levels} specifies the attribute levels for each alternative.
 #' Input for \code{prod.levels} has to be a list. In case
-#' \code{method = "MaxDiff"} this will only be a list of the column indexes or
[…]

### 2023-12-21 R/hitrate.R

@@ -5,7 +5,7 @@
 #'
 #' @param data A data frame with all relevant variables.
 #' @param group Optional column name(s) to specify grouping variable(s)
-#' to get \code{"hitrate"} by group(s).
+#' to get \code{hitrate} by group(s).
 #' @param opts Column names of the alternatives included in the
 #' validation/holdout task.
 #' @param choice Column name of the actual choice.
@@ -15,13 +15,13 @@
 #' predicted by the model.
 #' Output contains the following 4 metrics:
 #' \itemize{
-#' \item \code{"HR"} hit rate (number of correctly predicted
+#' \item \code{HR} hit rate (number of correctly predicted
 #' choices) in percentages
-#' \item \code{"se"} standard error in percentages
-#' \item \code{"chance"} chance level of correctly predicted choices by simply
+#' \item \code{se} standard error in percentages
+#' \item \code{chance} chance level of correctly predicted choices by simply
 #' guessing
-#' \item \code{"cor"} absolute number of correctly predicted choices
-#' \item \code{"n"} total number of choices
+#' \item \code{cor} absolute number of correctly predicted choices
+#' \item \code{n} total number of choices
 #' }
 #'
 #' \code{data} has to be a data frame including the alternatives shown in
@@ -32,7 +32,7 @@
 #' different groups. Has to be column name of variables in \code{data}.
 #'
 #' \code{opts} is needed to specify the different alternatives in the
-#' validation/holdout task (also includes the \code{none} alternative).
+#' validation/holdout task.
 #' Input of \code{opts} has to be column names of variables in \code{data}.
 #'
 #' \code{choice} to specify column of actual choice.

### 2023-12-21 R/prob_scores.R

@@ -20,7 +20,7 @@
 #' For anchored MaxDiff the following formula is applied \eqn{\frac{e^U}{(e^U + (a - 1)} * 100 / (1 / a)}
 #' (Chrzan & Orme, 2019, pp. 59-60).
 #'
-#' \code{data} has to be a data frame with the attributes. Items need
+#' \code{data} has to be a data frame with the attributes. Items have
 #' to be the raw utilities.
 #'
 #' \code{group} optional grouping variable, if results should be displayed by

### 2023-12-21 R/zc_diffs.R

@@ -6,7 +6,8 @@
 #' @param coding A vector of the coding of each attribute, '0' = part-worth
 #' coding, '1' = linear coding.
 #' @param interpolate.levels A list of the attribute levels that should
-#' be interpolated. These have to be the same as provided to Sawtooth Software.
+#' be interpolated. These have to be the same as specified in model estimation 
+#' (e.g., if you center attribute levels before estimation, insert the centered levels).
 #' Please make sure to provide the whole list. Only has to be specified for the
 #' variables that are coded as '1' (linear).
 #' @param res A vector indicating whether individual zero-centered diffs (\code{ind}) or
@@ -18,7 +19,7 @@
 #' zero-centered diffs (Orme, 2020, p. 78). This allows for comparison between
 #' the attributes.
 #'
-#' \code{data} has to be a data frame with the attributes. Attribute levels need
+#' \code{data} has to be a data frame with the attributes. Attribute levels have
 #' to be the raw utilities.
 #'
 #' \code{group} optional grouping variable, if results should be displayed by
@@ -28,18 +29,18 @@
 #' Input for \code{attrib} has to be a list. Needs to specify the column names or
 #' column indexes of the attribute levels.
 #'
-#' \code{coding} has to be specified  to indicate the attribute coding. \code{0}
+#' \code{coding} has to be specified to indicate the attribute coding. \code{0}
 #' to indicated part-worth coding, \code{1} for linear coding.
 #'
-#' \code{interpolate.levels} has to be specified for linear coded variables.
+#' \code{interpolate.levels} has to be specified for linear-coded variables.
 #' If scaled or centered values were used for hierarchical bayes (HB)
 #' estimation, these have to be specified in this case.
-#' All values have to be specified. For example, if one linear coded attribute
-#' had 5 levels, all 5 levels have to be inserted.
+#' All values have to be specified. For example, if one linear-coded attribute
+#' has 5 levels, all 5 levels have to be inserted.
 #'
 #' \code{res} specifies whether results should be aggregated across all participants
-#' or across \code{group} (\code{res} needs to be set to \code{agg}) or if it scores
-#' should be converted for individuals only
+#' or across \code{group} (\code{res} needs to be set to \code{agg}) or if scores
+#' should be converted for individuals only.
 #'
 #' \code{none} specifies whether none option was included or not, if yes,
 #' column name or column index of \code{none} needs to be specified. If no

### 2023-12-25 README.Rmd
correct zc_diffs() for ACBC - 231225

@@
 
-<li><code>prob_scores()</code>: Converts the raw utilities of a MaxDiff
-to choice probabilities by applying the following procedures:
+<li>
+
+<code>prob_scores()</code>: Converts the raw utilities of a MaxDiff to
+choice probabilities by applying the following procedures:
 
@@
 
-<li><code>zero_anchored()</code></li>: Rescales the raw logits of a
-MaxDiff to zero-centered diffs (Chrzan & Orme, 2019, p. 64).
+<li><code>zero_anchored()</code></li>
+
+: Rescales the raw logits of a MaxDiff to zero-centered diffs (Chrzan &
+Orme, 2019, p. 64).
 

### 2023-12-25 R/RMSE.R

@@ -39,7 +39,7 @@
 #' summarise
 #' @importFrom magrittr %>%
 #' @importFrom tidyr pivot_longer
-#' @importFrom tidyselect ends_with#'
+#' @importFrom tidyselect ends_with
 #'
 #'
 #' @examples

### 2023-12-25 R/Recall.R

@@ -162,9 +162,12 @@ recall <- function(data, group, opts, choice, none) {
 
   # test length of none
   if (!base::missing(none)) {
-    anc <- data %>% dplyr::select(., {{ none }}) %>% base::colnames(.)
-    if (length(anc) > 1)
+    anc <- data %>%
+      dplyr::select(., {{ none }}) %>%
+      base::colnames(.)
+    if (length(anc) > 1) {
       base::stop("Error: 'none' can only be one variable!")
+    }
   }
 
 

### 2023-12-25 R/att_imp.R

@@ -6,7 +6,7 @@
 #' @param coding A vector of the coding of each attribute, '0' = part-worth
 #' coding, '1' = linear coding.
 #' @param interpolate.levels A list of the attribute levels that should
-#' be interpolated. These have to be the same as specified in model estimation 
+#' be interpolated. These have to be the same as specified in model estimation
 #' (e.g., if you center attribute levels before estimation, insert the centered levels).
 #' Please make sure to provide the whole list. Only has to be specified for the
 #' variables that are coded as '1' (linear).
@@ -214,19 +214,19 @@ att_imp <- function(data, group = NULL, attrib, coding,
   for (i in 1:att) {
     helper <- 1
 
-    data[[base::paste0("att_imp", i)]] <- 0
+    data[[base::paste0("att_imp_", i)]] <- 0
 
     vars <- attrib[[i]]
 
-    new <- c(new, base::paste0("att_imp", i))
+    new <- c(new, base::paste0("att_imp_", i))
 
     for (j in 1:base::nrow(data)) {
       if (coding[i] == 0) {
-        data[j, base::paste0("att_imp", i)] <- base::abs(base::diff(base::range(data[j, vars])))
+        data[j, base::paste0("att_imp_", i)] <- base::abs(base::diff(base::range(data[j, vars])))
       }
 
       if (coding[i] == 1) {
-        data[j, base::paste0("att_imp", i)] <- base::abs(data[j, vars] * base::abs(base::diff(base::range(interpolate.levels[[helper]]))))
+        data[j, base::paste0("att_imp_", i)] <- base::abs(data[j, vars] * base::abs(base::diff(base::range(interpolate.levels[[helper]]))))
 
         helper
       }
@@ -242,11 +242,11 @@ att_imp <- function(data, group = NULL, attrib, coding,
       dplyr::mutate(dplyr::across(tidyselect::all_of(new), ~ .x / base::rowSums(data[new]))) %>%
       dplyr::group_by(dplyr::pick({{ group }})) %>%
       dplyr::summarise(dplyr::across(tidyselect::all_of(new), c(mw = base::mean, std = stats::sd),
-        .names = "{.col}.{.fn}"
+        .names = "{.col}...{.fn}"
       )) %>%
       tidyr::pivot_longer(.,
         cols = tidyselect::ends_with(c(".mw", ".std")),
-        names_to = c("Option", ".value"), names_sep = "\\."
[…]

### 2023-12-25 R/zero_anchored.R

@@ -96,7 +96,7 @@ zero_anchored <- function(data, group = NULL, items,
     stop("Error: 'items' is missing!")
   }
 
-  if (isTRUE(tibble::is_tibble(data))){
+  if (isTRUE(tibble::is_tibble(data))) {
     stop("Error: 'data' has to be a data frame!")
   }
 
@@ -174,10 +174,9 @@ zero_anchored <- function(data, group = NULL, items,
 
 
   for (i in 1:base::nrow(data)) {
-
     vec <- base::unname(base::unlist(c(data[i, var_items])))
 
-    #data[i, var_items] <- NA
+    # data[i, var_items] <- NA
 
     vec <- scales::rescale(vec, to = c(0, 100)) - base::mean(scales::rescale(vec, to = c(0, 100)))
 
@@ -189,30 +188,29 @@ zero_anchored <- function(data, group = NULL, items,
     }
 
     data[i, var_items] <- vec
-
   }
 
   if (res == "agg") {
     if (base::missing(group)) {
       return(data %>%
         dplyr::summarise(dplyr::across(tidyselect::all_of(var_items), c(mw = base::mean, std = stats::sd),
-          .names = "{.col}.{.fn}"
+          .names = "{.col}...{.fn}"
         )) %>%
         tidyr::pivot_longer(.,
           cols = tidyselect::ends_with(c(".mw", ".std")),
-          names_to = c("Option", ".value"), names_sep = "\\."
+          names_to = c("Option", ".value"), names_sep = "\\.\\.\\."
         ))
     }
 
     if (!(base::missing(group))) {
       return(data %>%
-        dplyr::group_by(dplyr::pick ({{group}})) %>%
+        dplyr::group_by(dplyr::pick({{ group }})) %>%
         dplyr::summarise(dplyr::across(tidyselect::all_of(var_items), c(mw = base::mean, std = stats::sd),
-          .names = "{.col}.{.fn}"
+          .names = "{.col}...{.fn}"
         )) %>%
         tidyr::pivot_longer(.,
           cols = tidyselect::ends_with(c(".mw", ".std")),
-          names_to = c("Option", ".value"), names_sep = "\\."
+          names_to = c("Option", ".value"), names_sep = "\\.\\.\\."
         ))
     }
   }
@@ -221,4 +219,3 @@ zero_anchored <- function(data, group = NULL, items,
     return(data)
   }
 }
-

### 2023-12-25 tests/testthat/test-zc_diffs.R

@@ -10,7 +10,7 @@ test_that("Coding missing ", {
   ))
 })
 
-test_that("Coding not 1 or 0 ", {
+test_that("Coding not 0, 1, or 2 ", {
   expect_error(zc_diffs(
     data = CBC,
     attrib = list(
@@ -18,12 +18,12 @@ test_that("Coding not 1 or 0 ", {
       c("Att2_Lev1", "Att2_Lev2", "Att2_Lev3", "Att2_Lev4", "Att2_Lev5"),
       c("Att3_Lev1", "Att3_Lev2", "Att3_Lev3", "Att3_Lev4", "Att3_Lev5", "Att3_Lev6", "Att3_Lev7")
     ),
-    coding = c(0, 0, 2),
+    coding = c(0, 0, 3),
     res = "agg"
   ))
 })
 
-test_that("Coding not 1 or 0 ", {
+test_that("Coding not 0, 1, or 2 ", {
   expect_error(zc_diffs(
     data = CBC,
     attrib = list(
@@ -59,6 +59,19 @@ test_that("Linear coded variables not equal to length of interpolate.levels ", {
     ),
     coding = c(0, 1, 1),
     interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
+    res = "agg"
+  ))
+})
+
+test_that("More than 1 variables code 2 ", {
+  expect_error(zc_diffs(
+    data = CBC,
+    attrib = list(
+      c("Att1_Lev1", "Att1_Lev2", "Att1_Lev3", "Att1_Lev4", "Att1_Lev5"),
+      c("Att2_Lev1", "Att2_Lev2", "Att2_Lev3", "Att2_Lev4", "Att2_Lev5"),
+      c("Att3_Lev1", "Att3_Lev2")
+    ),
+    coding = c(0, 2, 2),
     res = "agg"
   ))
 })
@@ -389,4 +402,3 @@ test_that("length of input equals length of output ", {
     sum(1, length(c("Att1_Lev1", "Att1_Lev2", "Att1_Lev3", "Att1_Lev4", "Att1_Lev5")), length(c("Att2_Lev1", "Att2_Lev2", "Att2_Lev3", "Att2_Lev4", "Att2_Lev5")), length(c("Att3_Lev1", "Att3_Lev2", "Att3_Lev3", "Att3_Lev4", "Att3_Lev5", "Att3_Lev6", "Att3_Lev7")))
   )
 })
-

### 2024-01-03 paper/paper.Rmd
updated paper - 240103

@@
 ---
-title: 'validateHOT - Validate your Holdout Task'
+title: 'validateHOT - an R package for holdout task validation and market simulation'
 tags:
@@
     corresponding: FALSE
-    affiliation: 1, 2    
+    affiliation: 2    
 affiliations:
@@
 citation_author: Schramm & Lichters
-date: 22 October 2023
-year: 2023
+date: 02 January
+year: 2024
 bibliography: paper.bib
@@
 journal: JOSS
+header-includes: 
+ - \usepackage{float}
 ---
@@
 ```{=tex}
-\setlength{\headheight}{63.55022pt}
-\addtolength{\topmargin}{-0.95425pt}
 \newcommand{\colcod}[1]{\texttt{\color{purple}#1}}
@@
 
+# Statement of need
+
 Preference measurement techniques', such as (A)CBC or MaxDiff, aim is to predict behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way to test it is to include so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
 Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
@@
 
-# Statement of need
+# State of the field in R
 
-validateHOT is a practical tool for Sawtooth Software users in industry as well as academia.
-It provides an open source solution for a) validating a validation/holdout task and ensuring that the model has predictive validity; b) running market simulations (e.g., Total Unduplicated Reach and Frequency, hereafter TURF).
-Other packages, for example, Metrics [@Metrics] provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
-However, to put the Sawtooth export into the right format, the user needs some data wrangling which could pose a barrier.
-Moreover, there are also packages that however mainly focus on the analysis of conjoint analysis (e.g., ChoiceModelR, @ChoiceModelR, choicetools, @choicetools, logitR, @logitr, bayesm, @bayesm, etc.).
+Other packages provide functions to calculate validation metrics, however, these are not specified for individual raw logit coefficients which are usually the output when running random parameter logit / hierarchical Bayes models.
+Metrics [@Metrics], for example, provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
+However, to get the output of, for example, Sawtooth Software or ChoiceModelR [@ChoiceModelR] into the right format, the user needs some data wrangling.
+The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones.
+However, no functions for validation are included and moreover, conjoint [@conjoint] mainly focuses on classical conjoint analysis.
+support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as Maximum Difference Scaling) and only provides market simulations based on conditional logit rule.
+logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
+Lastly, conjoint [@conjoint] also provides functions for both market simulations, A comparison of validateHOT's functions with current R packages is provided in \autoref{comparison}.
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
 
+validateHOT is introduced with data estimated with Lighthouse Studio using effects-coded data for the design matrix, however, can easily be used with data estimated with ChoiceModelR [@ChoiceModelR], bayesm [@bayesm], or STAN [@rstan], if used with similar settings (ChoiceModelR, for example, automatically implements effects-coding).
+
+```{=tex}
+\begin{figure}[h]
+  \includegraphics{figures/FunctionComparison.png}
+  \caption{Comparison of validateHOT's function to existing R packages}
+  \label{comparison}
+\end{figure}
+```
 # Key functions
@@
 
-In the following, we provide the workflow for a MaxDiff study (the vignette also provides detailed examples for a CBC as well as an ACBC).
+In the following, we provide the workflow for a MaxDiff study and a CBC study with only part-worth coded attributes (the vignette also provides detailed examples for a CBC including linear-coded attributes as well as an ACBC).
+
+## MaxDiff
 
@@
 ) %>%
-  round(3)
+  round(2)
 ```
@@
   none = None 
-)
+) %>% 
+  round(2)
 ```
@@
   method = "sop"
-)
+) %>% 
+  mutate_if(is.numeric, round, 2)
 ```
@@
 
+## CBC
+
+Again, we start by creating the validation scenario.
+
+```{r}
+HOT_CBC <- createHOT(
+  data = CBC,
+  id = "ID",
+  none = "none",
+  prod.levels = list(c(4, 9, 19), c(8, 12, 17), c(5, 10, 17)),
+  coding = c(0, 0, 0),
+  method = "CBC",
+  choice = "HOT"
+)
+```
+
+This time we calculate the mean hit probability.
+
+```{r}
+HOT_CBC %>% 
+  mhp(
+  data = ., 
+  opts = c(Option_1:None), 
+  choice = choice 
+) %>% 
+  round(2)
+```
+
+Finally, we can also display the attribute importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
+
+```{r}
+att_imp(
+  data = CBC,
+  attrib = list(
+    c(4:8),
+    c(9:13),
+    c(14:20)
+  ),
+  coding = c(rep(0, 3)),
+  res = "agg"
+) %>% 
+  mutate_if(is.numeric, round, 2)
+```
+
 # Availability

### 2024-01-04 paper/paper.Rmd
updated paper - 240104

@@
  - \usepackage{float}
+ - \usepackage{fancyhdr}
 ---
@@
 ```{=tex}
+\setlength{\headheight}{63.55022pt}
+\addtolength{\topmargin}{-0.95425pt}
 \newcommand{\colcod}[1]{\texttt{\color{purple}#1}}
 ```
+
 ```{r include=FALSE}
@@
 
-validateHOT is a package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using, for example, `ChoiceModelR` [@ChoiceModelR] or Sawtooth's Lighthouse Studio.
+validateHOT is an R package that provides functions to both validate a validation/holdout task and run market simulations for results obtained in a (adaptive) choice-based conjoint analysis (hereafter ACBC and CBC, respectively) and maximum difference scaling (hereafter MaxDiff) using, for example, ChoiceModelR [@ChoiceModelR] or Sawtooth's Lighthouse Studio.
 
@@
 
-Preference measurement techniques', such as (A)CBC or MaxDiff, aim is to predict behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [@Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
+Preference measurement techniques' (e.g., (A)CBC or MaxDiff) aim is to predict behavior [@green1990].
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
 Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
@@
 The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones.
-However, no functions for validation are included and moreover, conjoint [@conjoint] mainly focuses on classical conjoint analysis.
-support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as Maximum Difference Scaling) and only provides market simulations based on conditional logit rule.
+However, no functions for validation are included and moreover, conjoint [@conjoint] focuses on classical conjoint analysis, and thus is limited when applying more common CBC methods, for example, (A)CBC.
+support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as MaxDiff) and only provides market simulations based on conditional logit rule.
 logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
-Lastly, conjoint [@conjoint] also provides functions for both market simulations, A comparison of validateHOT's functions with current R packages is provided in \autoref{comparison}.
+A comparison of validateHOT's functions with current R packages is provided in \autoref{comparison}.
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
-
-validateHOT is introduced with data estimated with Lighthouse Studio using effects-coded data for the design matrix, however, can easily be used with data estimated with ChoiceModelR [@ChoiceModelR], bayesm [@bayesm], or STAN [@rstan], if used with similar settings (ChoiceModelR, for example, automatically implements effects-coding).
 
@@
 ```
+
+validateHOT is introduced with data estimated with Lighthouse Studio using effects-coding for creating the design matrix.
+It, however, can easily be used with data estimated with ChoiceModelR [@ChoiceModelR], bayesm [@bayesm], or STAN [@rstan], if used with similar settings (ChoiceModelR, for example, automatically implements effects-coding).
+
 # Key functions
 
-validateHOT's functions can be categorized into four main areas, see \autoref{tab:table1}.
+validateHOT's functions can be categorized into four main components, see \autoref{tab:table1}.
 To bring the data into the right format, users can run the \texttt{\color{purple}createHOT()} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
@@
 
-: Overview of main four areas of validateHOT and their corresponding functions \label{tab:table1}
+: Overview of validateHOT's main four components and their corresponding functions \label{tab:table1}
 
@@
 
+### Creating Holdout Task / Market Scenario
+
 After running the hierarchical Bayes estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame.
-This data frame has to include the actual choice in the validation/holdout task.
+This data frame has to include the actual choice in the validation/holdout task (if only a market scenario is created, the \texttt{\color{purple}choice} argument in \texttt{\color{purple}createHOT()} can be left empty)..
 
@@
 ```
+
+### Validating Holdout Task
 
@@
 
-Finally, we show two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
+### Market Simulations
+
+Lastly, we introduce two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
 In the following example, the market share is calculated according to the multinomial logit model [@McFadden1974].
@@
 
-Finally, \texttt{\color{purple}turf()}, a "product line extension model" [@miaoulis1990, p.
+Next, \texttt{\color{purple}turf()}, a "product line extension model" [@miaoulis1990, p.
 29], is a tool to find the perfect assortment that creates the highest reach and is especially powerful for MaxDiff studies [@chrzan2019, p.
@@
 
-Again, we start by creating the validation scenario.
+### Creating Holdout Task / Market Scenario
+
+The setup is almost the same, only the arguments \texttt{\color{purple}prod.levels}, \texttt{\color{purple}coding}, and \texttt{\color{purple}method} are different or new, respectively.
+\newpage
 
@@
 
-This time we calculate the mean hit probability.
+### Validating Holdout Task
+
+This time we calculate the mean hit probability (i.e., MHP).
 
@@
 
-Finally, we can also display the attribute importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
+### Rescaling Scores
+
+Finally, we can also display the attributes importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
 

### 2024-01-04 README.Rmd
updated createHOT - 240201
updated vignette and markdown - 240104

@@
 **HOT**), simulating markets with the results of your MaxDiff, CBC, and
-ACBC, and lastly to convert the raw logit scores of your MaxDiff, CBC,
+ACBC, and lastly converting the raw logit scores of your MaxDiff, CBC,
 and ACBC into scores that are easier to communicate. This package is
@@
 report their analysis in *R* for open science purposes. However, it also
-works perfectly with the great package `ChoiceModelR`(Sermas, 2022).
-This package is extremely useful for practitioners, who would like to
-run the analyses in an open source software. The ultimate goal of these
+works perfectly with the package `ChoiceModelR`(Sermas, 2022). This
+package is extremely useful for practitioners, who would like to run the
+analyses in an open source software. The ultimate goal of these
 preference measurement techniques is to predict future behavior (Green &
@@
 `validateHOT` and test how good your model predicts choices in the
-validation/holdout task. Therefore, you only have to read in your raw
-utility scores as well as the actual choice of your validation/holdout
-task. You can use the `merge()` function provided by the *R* base
-package to do so (R Core Team, 2023). Afterward, you can read in your
-data file and enjoy `validateHOT`. We provide a short tutorial in the
-markdown, for a more detailed tutorial, please see the vignette that
-comes along with `validateHOT`.
+validation/holdout task, run market simulations, or convert your data
+into scores which are easier to interpret. To enjoy `validateHOT` you
+only have to read in your raw utility scores. If you plan to validate
+your validation/holdout tasks you also need to provide the actual choice
+of your validation/holdout task. You can use the `merge()` function
+provided by the *R* base package to do so (R Core Team, 2023). We
+provide a short tutorial in the markdown, for a more detailed tutorial,
+please see the vignette that comes along with `validateHOT`.
 
 👈🏾 <u>**What you get**</u>:<br> At the moment, `validateHOT` provides
-functions for 4 key areas:
+functions for 4 key components:
 
@@
 
-For all 4 key areas, the `createHOT()` function is essential. This
-function creates the total utilities for each alternative in the
+For the first 3 components, the `createHOT()` function is essential.
+This function creates the total utilities for each alternative in the
 validation/holdout task and also in the simulation method, respectively.
@@
 used to get a sense of overestimation and underestimation, respectively,
-of product demand. In the table below <code>TP</code> stands for true
-positives, <code>FP</code> for false positives, <code>TN</code> for true
-negatives, and <code>FN</code> for false negatives (Burger, 2018; Kuhn,
-2008). To translate this to the `validateHOT` logic, imagine you have a
-validation/holdout task with five alternatives plus the alternative not
-to buy any of those chosen. `validateHOT` now measures whether or not a
-buy (participant opts for one of the five alternatives) or a no-buy
-(participant opts for the none alternative), respectively, is correctly
-predicted.
+of general product demand. In the table below <code>TP</code> stands for
+true positives, <code>FP</code> for false positives, <code>TN</code> for
+true negatives, and <code>FN</code> for false negatives (Burger, 2018;
+Kuhn, 2008). To translate this to the `validateHOT` logic, imagine you
+have a validation/holdout task with five alternatives plus the
+alternative not to buy any of those alternatives. `validateHOT` now
+measures whether or not a buy (participant opts for one of the five
+alternatives) or a no-buy (participant opts for the none alternative),
+respectively, is correctly predicted.
 
@@
 Again, all functions can be extended with the `group` argument to get
-output split by group(s).
+the output split by group(s).
 
@@
 
-<li><code>zero_anchored()</code></li>
-
-: Rescales the raw logits of a MaxDiff to zero-centered diffs (Chrzan &
-Orme, 2019, p. 64).
+<li><code>zero_anchored()</code>: Rescales the raw logits of a MaxDiff
+to zero-centered diffs (Chrzan & Orme, 2019, p. 64).</li>
 
@@
 analyses and provide the code afterwards is essential. `validateHOT`
-makes this process look easy.
-
-Of course, there are other great packages which are faster in terms of
-running time (i.e., `Metrics` by Hamner & Frasco, 2018), however, these
-packages need some more data wrangling in order to use the appropriate
-functions with the raw utilities, which might be a burden or barrier for
-the one or the other.
+makes this process look easy 🤹‍♀️. Of course, there are other great
+packages which are faster in terms of running time (i.e., `Metrics` by
+Hamner & Frasco, 2018), however, these packages need some more data
+wrangling in order to use the appropriate functions with the raw
+utilities, which might be a burden or barrier for the one or the other.
 
@@
 and as well as the `id`. Since we also have a *no-buy* alternative in
-our validation task, we next specify the `none` argument, otherwise we
-would have left it empty. Afterwards, we define each alternative with
-the argument `prod.levels`. If we look back at the data frame, we can
-see that the first alternative in the holdout task (`c(4, 9, 19)`) is
+our validation task, we specify the `none` argument, otherwise we would
+have left it empty. Afterwards, we define each alternative with the
+argument `prod.levels`. If we look back at the data frame, we can see
+that the first alternative in the holdout task (`c(4, 9, 19)`) is
 composed of the following attribute levels `Att1_Lev1`, `Att2_Lev1`, and
@@
 > Team, 2023). For example, if you want to find out the column index of
-> `ID`, you could run `which(colnames(CBC) == "ID")` to determine the
-> column index of `ID`.
+> `ID`, you could run `which(colnames(CBC) == "ID")`.
 
@@
 ```
+
+> In case you just need to create a market scenario, you can also leave
+> the `choice` argument empty.
 
@@
 matrix, we could test whether our model overestimates the purchase
-behavior (our model predicts a *buy* although participant opts for a
+behavior (our model predicts *buy* although participant opts for
 *no-buy*) or underestimates it (i.e., model predicts *no-buy* but
-participant opts for a *buy*). We will test the accuracy of the model by
+participant opts for *buy*). We will test the accuracy of the model by
 running the `accuracy()` function.
@@
 Since we have one linear coded attribute, we have to specify the column
-indexes instead of the column names. For example, for the second
-alternative which is composed of `Att1_Lev5`, `Att2_Lev4`, and `60`
-which is the value that should be interpolated. We tell `createHOT()`
-that this value needs to be interpolated by specifying the `coding`
-argument accordingly. This tells us that the first two attributes
-(`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are part-worth
-coded (`0`) while the third attribute is linear-coded (`1`).
+indexes instead of the column names in `prod.levels`. For example, for
+the second alternative which is composed of `Att1_Lev5`, `Att2_Lev4`,
+and `60` which is the value that should be interpolated. We tell
+`createHOT()` that this value needs to be interpolated by specifying the
+`coding` argument accordingly. This tells us that the first two
+attributes (`Att1_Lev5`, `Att2_Lev4` in the case of alternative 2) are
+part-worth coded (`0`) while the third attribute is linear-coded (`1`).
 
@@
 
-Next, we define the column index of the linear coded variable (`lin.p`)
-and specify the `coding` we talked about above. Again, we are running a
-*CBC* specified by the `method` argument. This time, we would like to
-keep some of the variables in the data frame, which we specify in
-`varskeep`. We only keep one further variable, however, you can specify
-as many as you want. This could be relevant if you would like to display
-results per group. Finally, we define the actual choice (`choice`) in
-the holdout/validation task and we are all set.
+Next, we define the column index of the linear coded variable (`lin.p`).
+Again, we are running a *CBC* specified by the `method` argument. This
+time, we would like to keep some of the variables in the data frame,
+which we specify by using the `varskeep` argument. We only keep one
+further variable, however, you can specify as many as you want. This
+could be relevant if you would like to display results per group.
+Finally, we define the actual choice (`choice`) in the
+holdout/validation task and we are all set.
 
@@
   group = Group # column name of Grouping variable
+)
+```
+
+Lastly, this time we also want to use a rescaling function, namely
+`att_imp()` which basically tells us the importance of each attribute
+included (Orme, 2020). We need the data set with the raw logit
+coefficients (`CBC_lin`). Next, we define the `attrib` argument. Here,
+we need to specify each attribute level for the corresponding level.
+Afterwards, we specify the coding again, and since we have one linear
+coded attribute, we need to define the `interpolate.levels` argument
+again, as we did for the `createHOT()` function above. Finally, we set
+`res` to `agg`, which tells `att_imp()` to display the aggregated
+results (for individuals results set `agg` to `ind`).
+
+```{r}
+att_imp(
+  data = CBC_lin,
+  attrib = list(
+    c("Att1_Lev1", "Att1_Lev2", "Att1_Lev3", "Att1_Lev4", "Att1_Lev5"),
+    c("Att2_Lev1", "Att2_Lev2", "Att2_Lev3", "Att2_Lev4", "Att2_Lev5"),
+    c("Att3_Lin")
+  ),
+  coding = c(0, 0, 1),
+  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
+  res = "agg"
 )

### 2024-01-12 paper/paper.Rmd
try compiling - 240104
updated figure and turf() manual - 240105
updated intro of paper - 240112

@@
 ---
-title: 'validateHOT - an R package for holdout task validation and market simulation'
+title: 'validateHOT - an R package for holdout task validation and market simulations'
 tags:
@@
 ```
-
 ```{r include=FALSE}
@@
 Preference measurement techniques' (e.g., (A)CBC or MaxDiff) aim is to predict behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities in hierarchical Bayes estimation.
-Practitioners often do not include them [@yang2018], which is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
+Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes estimation.
+Despite the importance of validation/holdout tasks, practitioners do not always include them [@yang2018].
+This is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
 
@@
 
-validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps to opt for the best model, (2) runs relevant market simulations that help to find the right product combinations or assortments, and finally, (3) is an open source tool including functions that are usually implemented in property commercial, and therefore, remain a black-box for researchers and practitioners.
+validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps to opt for the best model and (2) runs relevant market simulations that help to find the right product combinations or assortments, and finally, (3) is an open source tool which helps especially researchers to report accompanied scripts for their research papers.
 
@@
 The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones.
-However, no functions for validation are included and moreover, conjoint [@conjoint] focuses on classical conjoint analysis, and thus is limited when applying more common CBC methods, for example, (A)CBC.
+However, no functions for validation are included and moreover, conjoint [@conjoint] focuses on classical conjoint analysis, and thus is limited when applying more common conjoint methods, for example, (A)CBC.
 support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as MaxDiff) and only provides market simulations based on conditional logit rule.
@@
 ```
-
 validateHOT is introduced with data estimated with Lighthouse Studio using effects-coding for creating the design matrix.
@@
 To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}), which can be implemented using the tidyverse [@tidyverse] logic.
+
+\newpage
 
@@
 
-The setup is almost the same, only the arguments \texttt{\color{purple}prod.levels}, \texttt{\color{purple}coding}, and \texttt{\color{purple}method} are different or new, respectively.
-\newpage
+The setup is almost the same, only the arguments \texttt{\color{purple}prod.levels}, \texttt{\color{purple}coding}, and \texttt{\color{purple}method} are different or new, respectively. \newpage
 
@@
 
+# Acknowledgments
+
+We would like to thank [Sawtooth Software](https://sawtoothsoftware.com/) for their great transparent documentation.
+
 # References

### 2024-01-15 README.Rmd
upated RMD - 240110
new laptop push

@@
 The goal of `validateHOT` is to provide a tool to validate the results
-of your validation task (also known as holdout task; short form
+of a validation task (also known as holdout task; short form
 **HOT**), simulating markets with the results of your MaxDiff, CBC, and
@@
 predicted due to the asymmetry of the Kullback-Leibler divergence.
-`validateHOT` currently provides two logarithm bases: \eqn{log} and
-\eqn{log{_2}}. The default is set to \eqn{log}.</li>
+<code>validateHOT</code> currently provides two logarithm bases: $log$
+and $log_2$. The default is set to $log$.</li>
 

### 2024-01-22 paper/paper.Rmd
prepared paper for submission - 240122

@@
 
-Preference measurement techniques' (e.g., (A)CBC or MaxDiff) aim is to predict behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes estimation.
+The aim of preference measurement techniques' (e.g., (A)CBC or MaxDiff) is to predict behavior [@green1990].
+Hence, it is essential for both researchers and practitioners to ensure that the data collected is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The simplest way for testing validity is to include so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are typically not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes estimation.
 Despite the importance of validation/holdout tasks, practitioners do not always include them [@yang2018].
@@
 
-validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps to opt for the best model and (2) runs relevant market simulations that help to find the right product combinations or assortments, and finally, (3) is an open source tool which helps especially researchers to report accompanied scripts for their research papers.
+validateHOT combines both validation and market simulation in one package and has three main advantages, it (1) helps to opt for the best model and (2) performs relevant market simulations that help, for example, to find the right product combination or assortment, and (3) is an open source tool that helps especially researchers to report accompanied scripts for their research.
 
@@
 Other packages provide functions to calculate validation metrics, however, these are not specified for individual raw logit coefficients which are usually the output when running random parameter logit / hierarchical Bayes models.
-Metrics [@Metrics], for example, provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
+Metrics [@Metrics], for example, provides functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
 However, to get the output of, for example, Sawtooth Software or ChoiceModelR [@ChoiceModelR] into the right format, the user needs some data wrangling.
-The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones.
-However, no functions for validation are included and moreover, conjoint [@conjoint] focuses on classical conjoint analysis, and thus is limited when applying more common conjoint methods, for example, (A)CBC.
-support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as MaxDiff) and only provides market simulations based on conditional logit rule.
-logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
-A comparison of validateHOT's functions with current R packages is provided in \autoref{comparison}.
+The conjoint [@conjoint] package provides functions that are most similar to those of validateHOT.
+However, it does not include any functions for validation and moreover, conjoint [@conjoint] focuses on classical conjoint analysis and is therefore limited when using more common conjoint methods, for example, (A)CBC.
+support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as MaxDiff) and provides market simulations based on conditional logit rule.
+logitr [@logitr], besides running multinomial and mixed logit models, also offers functions to run market simulations tools.
+However, it currently does not provide validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
+
+A comparison of validateHOT's functions with current R packages is shown in \autoref{comparison}.
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
@@
 ```
-validateHOT is introduced with data estimated with Lighthouse Studio using effects-coding for creating the design matrix.
-It, however, can easily be used with data estimated with ChoiceModelR [@ChoiceModelR], bayesm [@bayesm], or STAN [@rstan], if used with similar settings (ChoiceModelR, for example, automatically implements effects-coding).
+validateHOT is introduced with data estimated using Lighthouse Studio. It, however, can easily be used with data estimated with ChoiceModelR [@ChoiceModelR], bayesm [@bayesm], or STAN [@rstan].
 
@@
 82].
-\colcod{turf()} as well as the four rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()}, and can be run using the raw logit scores.
+\colcod{turf()} as well as the four rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()} and can be run using the raw logit scores.
 
@@
 
-After running the hierarchical Bayes estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame.
-This data frame has to include the actual choice in the validation/holdout task (if only a market scenario is created, the \texttt{\color{purple}choice} argument in \texttt{\color{purple}createHOT()} can be left empty)..
+After running the hierarchical Bayes estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an R data frame.
+This data frame must contain the actual choice in the validation/holdout task (if only a market scenario is created, the \texttt{\color{purple}choice} argument can be left empty).
 
-Assuming you included a validation/holdout task with a total of 7 alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
-To create this validation task in *R*, we use the \texttt{\color{purple}createHOT()} function.
+Suppose you have a validation/holdout task with a total of 7 alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
+To create this validation task in R, we use the \texttt{\color{purple}createHOT()} function.
 
@@
 
-To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}), which can be implemented using the tidyverse [@tidyverse] logic.
+In the following, we provide the hitrate, a metric that is often reported as validation metric (see, e.g., @ding2005; @sablotny-wackershauser2024).
+\texttt{\color{purple}hitrate()} requires the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
+The input can be implemented using the tidyverse [@tidyverse] logic.
+The setup is the same for other metrics that are often reported, for example, mean hit probability [mhp, @voleti2017] or mean absolute error [mae, @wloemert2014].
 
@@
 
-The underlying logic of the confusion matrix is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
-validateHOT calculates how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (here by applying \texttt{\color{purple}accuracy()}).
+validateHOT also includes the Confusion Matrix.
+The underlying logic in validateHOT is that the user must provide a no-buy alternative (\texttt{\color{purple}none}).
+validateHOT calculates how often a buy or no-buy was correctly predicted and, therefore, tests whether the model correctly predicts the general demand (here by applying \texttt{\color{purple}accuracy()}).
 
@@
 
-Lastly, we introduce two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
+Lastly, two functions for market simulations are introduced, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
 In the following example, the market share is calculated according to the multinomial logit model [@McFadden1974].
@@
 Next, \texttt{\color{purple}turf()}, a "product line extension model" [@miaoulis1990, p.
-29], is a tool to find the perfect assortment that creates the highest reach and is especially powerful for MaxDiff studies [@chrzan2019, p.
+29], is a tool to find the perfect assortment that creates the highest reach and is particularly powerful for MaxDiff studies [@chrzan2019, p.
 108].
-To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf()} with data obtained using a likert scale).
+To optimize the search for the optimal bundle, we also add the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and the application of \texttt{\color{purple}turf()} with data obtained using a Likert scale).
 
-For the following example, we assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3.
-As a threshold (\texttt{\color{purple}none}), the user uses the anchor (no-buy alternative).
+For the following example, let's assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3 items.
+The user uses the anchor (no-buy alternative) as a threshold.
 

### 2024-03-03 paper/paper.Rmd
updated paper - 240303

--- 2024-01-12 paper/paper.Rmd
@@
 Preference measurement techniques' (e.g., (A)CBC or MaxDiff) aim is to predict behavior [@green1990].
-Hence, it is essential for both academics and practitioners to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.[^1] The easiest way for testing validity is by including so-called validation or holdout tasks [e.g., @rao2014; @Orme2015], which are tasks that are fixed (i.e., same across participants) and are usually not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes estimation.
-Despite the importance of validation/holdout tasks, practitioners do not always include them [@yang2018].
+Hence, it is essential to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.
+The easiest way for testing validity is by including validation tasks [e.g., @rao2014; @Orme2015], which are fixed tasks (i.e., same across participants) and not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes (HB) estimation.
+Despite their importance, practitioners don't always include them [@yang2018].
 This is unsatisfactory given the fact that the model is used to estimate market shares which poses the basis for relevant marketing decisions.
 
-[^1]: In terms of external validity, we refer to the generalizations to different settings [see, @calder1982, p.240].
-
-validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps to opt for the best model and (2) runs relevant market simulations that help to find the right product combinations or assortments, and finally, (3) is an open source tool which helps especially researchers to report accompanied scripts for their research papers.
+validateHOT combines both validation and market simulation in one package and has three key advantages, it (1) helps opting for the best model and (2) runs relevant market simulations that help finding the right product combinations or assortments, and (3) is an open source tool which helps especially researchers reporting accompanied scripts for their research papers.
 
@@
 
-Other packages provide functions to calculate validation metrics, however, these are not specified for individual raw logit coefficients which are usually the output when running random parameter logit / hierarchical Bayes models.
+Other packages provide functions to calculate validation metrics, however, these are not always specified for individual part-worth utilities.
 Metrics [@Metrics], for example, provide functions to run validation metrics such as *mean absolute error*, *root mean squared error*, or the five metrics of the confusion matrix.
 However, to get the output of, for example, Sawtooth Software or ChoiceModelR [@ChoiceModelR] into the right format, the user needs some data wrangling.
-The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones.
-However, no functions for validation are included and moreover, conjoint [@conjoint] focuses on classical conjoint analysis, and thus is limited when applying more common conjoint methods, for example, (A)CBC.
-support.BWS [@support.BWS] only covers best-worst scaling case 1 (also known as MaxDiff) and only provides market simulations based on conditional logit rule.
+The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones, but no validation functions are included and the package focuses on classical conjoint analysis, thus it is limited when applying more common conjoint methods.
+support.BWS [@support.BWS] only covers best-worst scaling case 1 (i.e., MaxDiff).
 logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
-A comparison of validateHOT's functions with current R packages is provided in \autoref{comparison}.
+\autoref{comparison} shows a comparison of validateHOT's functions with current R packages.
 To the best of our knowledge, a package that converts raw utility scores into validation metrics or running a variety of marketing simulations (especially TURF) is missing.
@@
 ```
+
 validateHOT is introduced with data estimated with Lighthouse Studio using effects-coding for creating the design matrix.
@@
 validateHOT's functions can be categorized into four main components, see \autoref{tab:table1}.
-To bring the data into the right format, users can run the \texttt{\color{purple}createHOT()} function, which creates the total utility of each alternative by applying the additive utility model [@rao2014, p.
+To bring the data into the right format for some functions, the \texttt{\color{purple}createHOT()} function can be applied, which creates each alternatives' total utility by applying the additive utility model [@rao2014, p.
 82].
-\colcod{turf()} as well as the four rescaling functions, however, are not dependent on \texttt{\color{purple}createHOT()}, and can be run using the raw logit scores.
 
@@
 
-: Overview of validateHOT's main four components and their corresponding functions \label{tab:table1}
+: Overview of validateHOT's main components and their corresponding functions \label{tab:table1}
 
@@
 
-In the following, we provide the workflow for a MaxDiff study and a CBC study with only part-worth coded attributes (the vignette also provides detailed examples for a CBC including linear-coded attributes as well as an ACBC).
+We provide the workflow for a MaxDiff study and a CBC study with only part-worth coded attributes (the vignette provides detailed examples for other CBCs and an ACBC).
 
@@
 
-After running the hierarchical Bayes estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame.
-This data frame has to include the actual choice in the validation/holdout task (if only a market scenario is created, the \texttt{\color{purple}choice} argument in \texttt{\color{purple}createHOT()} can be left empty)..
-
-Assuming you included a validation/holdout task with a total of 7 alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
+After running the HB estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame. 
+Assuming you included a validation task with seven alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
 To create this validation task in *R*, we use the \texttt{\color{purple}createHOT()} function.
@@
 
-To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005], mean hit probability [mhp, @voleti2017], or mean absolute error [mae, @wloemert2014], we provide the data, the alternatives in the validation/holdout task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}), which can be implemented using the tidyverse [@tidyverse] logic.
-
-\newpage
+To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005] or mean hit probability [mhp, @voleti2017], we provide the data, the alternatives in the validation task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
+The function can be implemented using the tidyverse [@tidyverse] logic.
 
@@
 
-The underlying logic of the confusion matrix is that the user has to provide a no-buy alternative (\texttt{\color{purple}none}).
-validateHOT calculates how often a buy or no-buy was correctly predicted, therefore, it is testing whether the model correctly predicts general demand (here by applying \texttt{\color{purple}accuracy()}).
-
-```{r}
-accuracy(
-  data = HOT, 
-  group = Group, 
-  opts = c(Option_1:None), 
-  choice = choice, 
-  none = None 
-) %>% 
-  round(2)
-```
-
 ### Market Simulations
 
-Lastly, we introduce two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
+We also introduce two functions for market simulations, namely \texttt{\color{purple}marksim()} and \texttt{\color{purple}turf()}.
 In the following example, the market share is calculated according to the multinomial logit model [@McFadden1974].
@@
 108].
-To optimize the search for the optimal bundle, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations of being part of the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf()} with data obtained using a likert scale).
+To optimize the search for the optimal assortment, we also include the arguments \texttt{\color{purple}fixed}, to define alternatives that have to be part of the assortment, and \texttt{\color{purple}prohib}, to prohibit certain item combinations in the assortment (see the vignette for more details and how to apply \texttt{\color{purple}turf()} with data obtained using a likert scale).
 
@@
 
-The setup is almost the same, only the arguments \texttt{\color{purple}prod.levels}, \texttt{\color{purple}coding}, and \texttt{\color{purple}method} are different or new, respectively. \newpage
+The setup is almost the same, only the arguments \texttt{\color{purple}prod.levels}, \texttt{\color{purple}coding}, and \texttt{\color{purple}method} are different or new, respectively.
 
@@
 )
-```
-
-### Validating Holdout Task
-
-This time we calculate the mean hit probability (i.e., MHP).
-
-```{r}
-HOT_CBC %>% 
-  mhp(
-  data = ., 
-  opts = c(Option_1:None), 
-  choice = choice 
-) %>% 
-  round(2)
 ```

### 2024-03-03 paper/paper.Rmd
shortening paper - 240303

@@
 
-For the following example, we assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3.
-As a threshold (\texttt{\color{purple}none}), the user uses the anchor (no-buy alternative).
+For the following example, let's assume that the user conducted an anchored MaxDiff analysis with 10 items (\texttt{\color{purple}opts}) and now wants to find the best assortment with a size of 3 items.
+The user uses the anchor (no-buy alternative) as a threshold.
 
@@
 
-Finally, we can also display the attributes importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
+We can also display the attributes importance scores. Therefore, we need to define the attribute levels as well as the coding of the attributes.
 

### 2024-03-04 paper/paper.Rmd
deleted references and also changed affiliation - 240304

@@
     corresponding: True
-    affiliation: 1, 2
+    affiliation: 1
   - name: Marcel Lichters
@@
     corresponding: FALSE
-    affiliation: 2    
+    affiliation: 1    
 affiliations:
- - name: Chemnitz University of Technology, Germany
+ - name: Otto von Guericke University of Magdeburg, Germany
    index: 1
- - name: Otto von Guericke University of Magdeburg, Germany
-   index: 2
 citation_author: Schramm & Lichters
-date: 02 January
+date: 04 March
 year: 2024
@@
 Hence, it is essential to ensure that the collected data is valid and predicts outside tasks (i.e., the model has external validity) well.
-The easiest way for testing validity is by including validation tasks [e.g., @rao2014; @Orme2015], which are fixed tasks (i.e., same across participants) and not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes (HB) estimation.
+The easiest way for testing validity is by including validation tasks [e.g., @Orme2015], which are fixed tasks (i.e., same across participants) and not used for estimating the part-worth utilities (raw logit utilities) in hierarchical Bayes (HB) estimation.
 Despite their importance, practitioners don't always include them [@yang2018].
@@
 The package conjoint [@conjoint] provides functions that are most similar to validateHOT's ones, but no validation functions are included and the package focuses on classical conjoint analysis, thus it is limited when applying more common conjoint methods.
-support.BWS [@support.BWS] only covers best-worst scaling case 1 (i.e., MaxDiff).
-logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability [@voleti2017] or hit rate [@netzer2011].
+logitr [@logitr] provides market simulations tools, however, no validation metrics such as mean hit probability or hit rate.
 \autoref{comparison} shows a comparison of validateHOT's functions with current R packages.
@@
 validateHOT's functions can be categorized into four main components, see \autoref{tab:table1}.
-To bring the data into the right format for some functions, the \texttt{\color{purple}createHOT()} function can be applied, which creates each alternatives' total utility by applying the additive utility model [@rao2014, p.
-82].
+To bring the data into the right format for some functions, the \texttt{\color{purple}createHOT()} function can be applied, which creates each alternatives' total utility by applying the additive utility model.
 
@@
 
-After running the HB estimation [@allenby1995; @lenk1996], the **raw** utility scores have to be exported and read into an *R* data frame. 
+After running the HB estimation [@allenby1995], the **raw** utility scores have to be exported and read into an *R* data frame. 
 Assuming you included a validation task with seven alternatives plus the no-buy alternative (\texttt{\color{purple}none}).
@@
 
-To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate [e.g., @ding2005] or mean hit probability [mhp, @voleti2017], we provide the data, the alternatives in the validation task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
+To get the relevant validation metrics that are reported in conjoint studies, for example, hit rate or mean hit probability, we provide the data, the alternatives in the validation task (\texttt{\color{purple}opts}), and the actual choice (\texttt{\color{purple}choice}).
 The function can be implemented using the tidyverse [@tidyverse] logic.
